### 2024-02-25 paper.tex
Update on Overleaf.

% !TeX spellcheck = en_GB
% !TeX program = lualatex

\documentclass[a4paper,
               %boxit,        % check whether paper is inside correct margins
               %titlepage,    % separate title page
               %refpage       % separate references
               %biblatex,     % biblatex is used
               keeplastbox,   % flushend option: not to un-indent last line in References
               %nospread,     % flushend option: do not fill with whitespace to balance columns
               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
               %xetex,        % use XeLaTeX to process the file
               %luatex,       % use LuaLaTeX to process the file
               ]{jacow}
%
% ONLY FOR \footnote in table/tabular
%
\usepackage{pdfpages,multirow,ragged2e} %
%
% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
% ----------------------------------------------------
% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
%    might generates errors, therefore PNG and JPG first
%
\makeatletter%
	\ifboolexpr{bool{xetex}}
	 {\renewcommand{\Gin@extensions}{.pdf,%
	                    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
	                    .eps,.ps,%
	                    }}{}
\makeatother

% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
% --------------------------------------------------------
%   utf8  is default for XeTeX/LuaTeX
%   utf8  in LaTeX only realises a small portion of codes
%
\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
 {}                                      % input encoding is utf8 by default
 {\usepackage[utf8]{inputenc}}           % switch to utf8

\usepackage[USenglish]{babel}

%
% if BibLaTeX is used
%
\ifboolexpr{bool{jacowbiblatex}}%
 {%
  \addbibresource{jacow-test.bib}
  \addbibresource{biblatex-examples.bib}
 }{}
\listfiles

%%
%%   Lengths for the spaces in the title
%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em

\begin{document}

\title{preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}}

\author{A. N. Author\thanks{email address}, H. Coauthor, Name of Institute or Affiliation, City, Country \\
		P. Contributor\textsuperscript{1}, Name of Institute or Affiliation, City, Country \\
		\textsuperscript{1}also at Name of Secondary Institute or Affiliation, City, Country}

\maketitle

%
\begin{abstract}
   Many conference series have adopted the same standards
   for electronic publication and have joined the Joint
   Accelerator Conferences Website (JACoW) collaboration
   for the publication of their proceedings. This document
   describes the common requirements for the submission of
   papers to these conferences. Please consult individual
   conference information for page limits, method of electronic
   submission, etc. It is not intended that this should
   be a tutorial in word processing; the aim is to explain the
   particular requirements for electronic publication at
   www.JACoW.org. The abstract itself is to act as a stand-alone
   entity and, as such, should not include citations. Any acronyms 
   should be expanded on their first occurrence, both in the 
   abstract and in the rest of the paper. 
   The abstract itself is to act as a stand-alone entity and, 
   as such, should not include citations. Any acronyms should 
   be expanded on their first occurrence, both in the abstract 
   and in the rest of the paper.
\end{abstract}

\section{SUBMISSION OF PAPERS}
Each author should submit the PDF file and all source
files (text and figures) to enable the paper to be
reconstructed if there are processing difficulties.

\section{MANUSCRIPTS}
Templates are provided for recommended software and
authors are advised to use them. Please consult the
individual conference help pages if questions arise.

\subsection{General Layout}

These instructions are a typical implementation of the
requirements. Manuscripts should have:
\begin{Itemize}
    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
           authors must change this to 1 line.
    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
\end{Itemize}
\begin{table}[!hbt]
   \centering
   \caption{Margin Specifications}
   \begin{tabular}{lcc}
       \toprule
       \textbf{Margin} & \textbf{A4 Paper}                      & \textbf{US Letter Paper} \\
       \midrule
           Top         & \SI{37}{mm} (\SI{1.46}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
          Bottom       & \SI{19}{mm} (\SI{0.75}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
           Left        & \SI{20}{mm} (\SI{0.79}{in})            & \SI{0.79}{in} (\SI{20}{mm})        \\ %[3pt]
           Right       & \SI{20}{mm} (\SI{0.79}{in})            & \SI{1.02}{in} (\SI{26}{mm})        \\
       \bottomrule
   \end{tabular}
   \label{tab:margins}
\end{table}

\subsection{Fonts}

In order to produce good Adobe Acrobat PDF files, authors
using the `jacow' \LaTeX{} template are asked to use only the fonts
defined in the ‘jacow’ class file (v2.3 of 2019/01/15) in standard, 
bold (i.\,e., \verb|\textbf|) or italic (i.\,e., \verb|\textit|) form and
symbols from the standard set of fonts. In Word use only
Symbol and, depending on your platform, Times or Times New Roman
fonts in standard, bold or italic form.

The layout of the text on the page is illustrated in
Fig.~\ref{fig:paper_layout}. Note that the paper’s title and the author list should
be the width of the full page. Tables and figures may span
the whole \SI{170}{mm} page width, if desired (see Fig.~\ref{fig:jacow_team}), but
if they span both columns, they should be placed at either
the top or bottom of a page to ensure proper flow of the
text (which should flow from top to bottom in each column).

\begin{figure}[!htb]
   \centering
   \includegraphics*[width=.7\columnwidth]{JACpic_mc}
   \caption{Layout of papers.}
   \label{fig:paper_layout}
\end{figure}

\begin{figure*}[!tbh]
    \centering
    \includegraphics*[width=\textwidth]{JACpic2}

    \caption{Example of a full-width figure showing the JACoW Team at their annual
    	     meeting in December 2018. This figure has a multi-line caption that has to be
    	     justified rather than centred.}
    \label{fig:jacow_team}
\end{figure*}

\subsection{Title and Author List}

The title should use \SI{14}{pt} bold uppercase letters and be centred on the page.
Individual letters may be lowercased to avoid misinterpretation (e.\,g., mW, GeV, 
SPring-8, SwissFEL).
To include a funding support statement, put an asterisk after the title and
the support text at the bottom of the first column on page~1---in Word,
use a text box; in \LaTeX, use $\backslash$\texttt{thanks}. See also the
subsection on footnotes.

The names of authors, their organizations/affiliations and
postal addresses should be grouped by affiliation and
listed in \SI{12}{pt} upper- and lowercase letters. The name of
the submitting or primary author should be first, followed
by the coauthors, alphabetically by affiliation. Where
authors have multiple affiliations, the secondary affiliation
may be indicated with a superscript, as shown in the
author listing of this paper. See \textbf{ANNEX~A} for further examples.

\subsection{Section Headings}

Section headings should not be numbered. They should
use  \SI{12}{pt}  bold  uppercase  letters  and  be  centred  in  the
column. All section headings should appear directly above
the text---there should never be a column break between a heading and the
following paragraph.

\subsection{Subsection Headings}

Subsection  headings  should  not  be  numbered.
They should use \SI{12}{pt} italic letters and be left aligned in the column.
Subsection headings use Title Case (or Initial Caps)
and should appear directly above the text---there should never be a column break
between a subheading and the following paragraph.

\subsubsection{Third-level Headings} These should use \SI{10}{pt} bold
letters and be run into the paragraph text. In \LaTeX{} these headings are
created with \LaTeX's \verb|\subsubsection| command.
In the Word templates authors must bold the heading text themselves.
This heading should be used sparingly. See Table~\ref{tab:styles}
for its style details.

\subsection{Paragraph Text}

Paragraphs should use \SI{10}{pt} font and be justified (touch each side) in
the column. The beginning of each paragraph should be indented
approximately \SI{0.33}{cm} (\SI{0.13}{in}). The last line of a paragraph should not be
printed by itself at the beginning of a column nor should the first line of
a paragraph be printed by itself at the end of a column.

\subsection{Figures, Tables and Equations}

Place figures and tables as close to their place of mention as
possible. Lettering in figures and tables should be large enough to
reproduce clearly. Use of non-approved fonts in figures can lead to
problems when the files are processed. \LaTeX{} users should be sure to use
non-bitmapped versions of Computer Modern fonts in equations (Type\,1 PostScript
or OpenType fonts are required. Their use is described in the help 
pages of the JACoW website\cite{jacow-help}).

Each figure and table must be numbered in ascending
order (1, 2, 3, etc.) throughout the paper. 
Figure captions are placed below figures, and table
captions are placed above tables.

Figure captions are formatted as shown in Figs.~\ref{fig:paper_layout} and \ref{fig:jacow_team},
while table captions take the form of a heading,
with initial letters of principle words, capitalized, and
without a period at the end (see Tables~\ref{tab:margins} and~\ref{tab:styles}).
Any reference to the contents of the table should be made from
the body of the paper rather than from within the table
caption itself.

Single-line captions are centred in the column, while captions
that span more than one line should be justified.
The \LaTeX{} template uses the ‘booktabs’ package to
format tables.

When referring to a figure from within the text, the
convention is to use the abbreviated form [e.\,g., Fig.~1]
\emph{unless} the reference is at the start of the sentence, in
which case “Figure” is written in full. Reference to a
table, however, is never abbreviated [e.\,g., Table~1].

If a displayed equation needs a number (i.\,e., it will be
referenced), place it in parentheses, and flush with the
right margin of the column. The equation itself should be
indented and centred, as far as is possible:
\begin{equation}\label{eq:label}
    C_B=\frac{q^3}{3\epsilon_{0} mc}=\SI{3.54}{\micro eV/T}
\end{equation}

When referencing a numbered equation, use the word
“Equation” at the start of a sentence, and the abbreviated
form, “Eq.”, if in the text. The equation number is placed
in parentheses [e.\,g., Eq.~\eqref{eq:label}], which can be 
achieved in \LaTeX{} using \verb|\eqref{eq:label}|.

\subsection{Units}

Units should be written using the standard, roman font,
not the italic font, as shown in Eq.~\eqref{eq:label}.
An unbreakable space should precede a unit (in \LaTeX{} use a “\verb|\,|”,
the template uses the ‘siunitx’ package to format units).
Some examples are: \SI{3}{keV},
\SI{100}{kW}, \SI{7}{µm}. When a unit appears in a hyphenated,
compound adjective that precedes a noun, it takes on the
singular form, e.\,g., the 3.8-metre long undulator.

\subsection{References}
%
% References examples given here are not formatted using \cite as there
%			 are only reference numbers [1] and [2] in the template
%
All bibliographical and web references should be numbered and listed at the
end of the paper in a section called \textbf{REFERENCES}. When citing a
reference in the text, place the corresponding reference number in square
brackets~[1]. The reference citations in the text should be numbered
in ascending order. Multiple citations should appear in
the same bracket~[3, 4] and
with ranges where appropriate~[1--4, 10].

A URL or DOI may be included as part of a reference, but its
hyperlink should NOT be added. The usual practice is to
use a monospaced font for the URL so as to help distinguish
it from normal text. In \LaTeX{} the ‘url’ package is used with its 
default font now being switched to ``newtxtt'' which offers
a better distinction between ``\texttt{O}'' and ``\texttt{0}''.

For authors to properly cite the resources used when researching
their papers is an obligation. In the interest of
promoting uniformity and complete citations, the IEEE
Editorial Style for Transactions and Journals, which itself 
adheres to the Chicago Manual of Style, has been adopted~\cite{IEEE}. 
When citing a periodical, the official abbreviation of the journal 
should be used\cite{journal-abbreviations}.
Please consult the appended material, \textbf{ANNEX~B},
for details. The onus is on authors to pay attention to
the details of the said style to ensure complete, accurate
and properly formatted references.

  \begin{table}[h!b]
	\setlength\tabcolsep{3.5pt}
	\centering
	\caption{Summary of Styles}
	\label{tab:styles}
	\begin{tabular}{llcc}
		\toprule
		\textbf{Style} & \textbf{Font}               & \textbf{Space}  & \textbf{Space} \\
		&                             & \textbf{Before} & \textbf{After} \\
		\midrule
		\textbf{PAPER}  & \SI{14}{pt}                 & \SI{0}{pt}      & \SI{3}{pt}  \\
		\textbf{TITLE}  & \textbf{UPPERCASE}          &                 &      \\
		& \textbf{EXCEPT FOR}         &                 &      \\
		& \textbf{REQUIRED lowercase} &                 &      \\
		& \textbf{letters}            &                 &      \\
		& \textbf{Bold}               &                 &      \\[5pt]
		%\midrule
		Author list  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{12}{pt} \\
		& UPPER- and lowercase        &                 &      \\[5pt]
		%\midrule
		\textit{Abstract} & \SI{12}{pt}                 & \SI{0}{pt}      & \SI{3}{pt} \\
		\textit{Title}  & \textit{Initial Caps}       &                 &      \\
		& \textit{Italic}             &                 &      \\[5pt]
		%\midrule
		\textbf{Section}  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{3}{pt}  \\
		\textbf{Heading}  & \textbf{UPPERCASE}          &                 &      \\
		& \textbf{bold}               &                 &      \\[5pt]
		%\midrule
		\textit{Subsection} & \SI{12}{pt}                 & \SI{6}{pt}      & \SI{3}{pt}  \\
		\textit{Heading}
                             & \textit{Initial Caps}       &                 &      \\
		& \textit{Italic}             &                 &      \\[5pt]
		%\midrule
		\textbf{Third-level} & \SI{10}{pt}                 & \SI{6}{pt}      & \SI{0}{pt}  \\
		\textbf{Heading}     
                            & \textbf{Initial Caps}       &                 &      \\
		& \textbf{Bold}               &                 &      \\[5pt]
		%\midrule
		Figure        & \SI{10}{pt}                 & \SI{3}{pt}      & $\ge$\SI{3}{pt}  \\
		Captions      &                             &                 &      \\[5pt]
		%\midrule
		Table         & \SI{10}{pt}                 & $\ge$\SI{3}{pt} & \SI{3}{pt}  \\
		Captions      &                             &                 &      \\[5pt]
		%\midrule
		Equations     & \SI{10}{pt} base font       & $\ge$\SI{6}{pt}     & $\ge$\SI{6}{pt} \\[5pt]
		%\midrule
		References      & \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt} \\
        when $\le9$ 	& \verb|\bibliography{9}|	&                 &  \\[5pt]
        Refs. $\ge10$ 	& \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt}  \\
                		& \verb|\bibliography{99}|	&    &    \\
		\bottomrule   %\SI{0.25}{in}
	\end{tabular}
\end{table}

\subsection{Footnotes}

Footnotes on the title and author lines may be used for acknowledgements
and e-mail addresses. A non-numeric sequence of characters (*, \#,
\dag, \ddag, \P) should be used to indicate the footnote.
These “pseudo footnotes” should only
appear at the bottom of the first column on the first page.

Any other footnote in the body of the paper should
use the normal numeric sequencing (i.\,e., 1, 2, 3)
and appear at the bottom of the same column in which
it is used.  All footnotes are of 8pt font size.

\subsection{Acronyms}

Acronyms should be defined the first time they appear, 
both in the abstract and in the rest of the paper.

\section{STYLES}

Table~\ref{tab:styles} summarizes the fonts and spacing used in the styles of
a JACoW template. In \LaTeX, these 
are implemented in the ‘jacow’ class file.

\section{PAGE NUMBERS}

\textbf{DO NOT include any page numbers}. They will be added
when the final proceedings are produced.

\section{TEMPLATES}

Template documents for the recommended word processing
software are available from the JACoW website~\cite{jacow-help}
and exist for \LaTeX, Microsoft Word (Mac and PC)
and LibreOffice/Apache OpenOffice for US letter and A4
paper sizes. Use the correct template for your paper size and
platform.

Fonts are embedded by default with pdf\LaTeX. Using \LaTeX{} with `dvips', 
make sure that `ps2pdf' has the option \texttt{-dEmbedAllFonts=true}'.
Fonts of included figure graphics in PDF or EPS are often not embedded. 
So make sure that this done when generating them or reprocess them 
in `Ghostscript' with the switch \texttt{-dEmbedAllFonts=true}' set.

\flushcolsend

\section{CHECKLIST FOR ELECTRONIC PUBLICATION}
Authors are requested to go over the following checklist for electronic publication:
\begin{Itemize}
	\item  Use only Times or Times New Roman (standard, bold or italic) and Symbol
	fonts for text, \SI{10}{pt} except references, which should be \SI{9}{pt}.

	\item  Figures should use Times or Times New Roman (standard, bold or italic) and
	Symbol fonts when possible---\SI{6}{pt} minimum, with fonts embedded.
	\item  Check that citations to references appear in sequential order and
	that all references are cited.
	\item  Check that the PDF file prints correctly.
	\item  Check that there are no page numbers.
	\item  Check that the margins on the printed version are within \SI{\pm1}{mm}
	of the specifications.
	\item  \LaTeX{} users can check their margins by invoking the
	\texttt{boxit} option.
\end{Itemize}

Please also check the list of common oversights which can be found in \textbf{ANNEX C}.

\section{CONCLUSION}

Any conclusions should be in a separate section directly preceding
the \textbf{ACKNOWLEDGEMENTS}, \textbf{APPENDIX}, or \textbf{REFERENCES} sections, in that
order.

\section{ACKNOWLEDGEMENTS}
Any acknowledgement should be in a separate section directly preceding
the \textbf{REFERENCES} or \textbf{APPENDIX} section.

\section{APPENDIX}
Any appendix should be in a separate section directly preceding
the \textbf{REFERENCES} section. If there is no \textbf{REFERENCES} section,
this should be the last section of the paper.

%
% only for "biblatex"
%
\ifboolexpr{bool{jacowbiblatex}}%
	{\printbibliography}%
	{%
	% "biblatex" is not used, go the "manual" way

	%\begin{thebibliography}{99}   % Use for  10-99  references
	\begin{thebibliography}{9} % Use for 1-9 references

	\bibitem{jacow-help}
		JACoW,
		\url{http://www.jacow.org}

	\bibitem{IEEE}
		\textit{IEEE Editorial Style Manual},
		IEEE Periodicals, Piscataway,
		NJ, USA, Oct. 2014, pp. 34--52.

	\bibitem{journal-abbreviations}
	\url{https://woodward.library.ubc.ca/researchhelp/journal-abbreviations/}

	\end{thebibliography}
} % end \ifboolexpr
%
% for use as JACoW template the inclusion of the ANNEX parts have been commented out
% to generate the complete documentation please remove the "%" of the next two commands
% 
%%%\newpage

%%%\include{annexes-A4}

\end{document}

### 2024-02-25 bibliography.tex
separated acknowledgements appendix and bibliography

--- 2024-02-25 paper.tex
@@
-% !TeX spellcheck = en_GB
-% !TeX program = lualatex
-
-\documentclass[a4paper,
-               %boxit,        % check whether paper is inside correct margins
-               %titlepage,    % separate title page
-               %refpage       % separate references
-               %biblatex,     % biblatex is used
-               keeplastbox,   % flushend option: not to un-indent last line in References
-               %nospread,     % flushend option: do not fill with whitespace to balance columns
-               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
-               %xetex,        % use XeLaTeX to process the file
-               %luatex,       % use LuaLaTeX to process the file
-               ]{jacow}
-%
-% ONLY FOR \footnote in table/tabular
-%
-\usepackage{pdfpages,multirow,ragged2e} %
-%
-% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
-% ----------------------------------------------------
-% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
-%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
-%    might generates errors, therefore PNG and JPG first
-%
-\makeatletter%
-	\ifboolexpr{bool{xetex}}
-	 {\renewcommand{\Gin@extensions}{.pdf,%
-	                    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
-	                    .eps,.ps,%
-	                    }}{}
-\makeatother
-
-% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
-% --------------------------------------------------------
-%   utf8  is default for XeTeX/LuaTeX
-%   utf8  in LaTeX only realises a small portion of codes
-%
-\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
- {}                                      % input encoding is utf8 by default
- {\usepackage[utf8]{inputenc}}           % switch to utf8
-
-\usepackage[USenglish]{babel}
-
-%
-% if BibLaTeX is used
-%
-\ifboolexpr{bool{jacowbiblatex}}%
- {%
-  \addbibresource{jacow-test.bib}
-  \addbibresource{biblatex-examples.bib}
- }{}
-\listfiles
-
-%%
-%%   Lengths for the spaces in the title
-%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
-%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
-%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em
-
-\begin{document}
-
-\title{preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}}
-
-\author{A. N. Author\thanks{email address}, H. Coauthor, Name of Institute or Affiliation, City, Country \\
-		P. Contributor\textsuperscript{1}, Name of Institute or Affiliation, City, Country \\
-		\textsuperscript{1}also at Name of Secondary Institute or Affiliation, City, Country}
-
-\maketitle
-
-%
-\begin{abstract}
-   Many conference series have adopted the same standards
-   for electronic publication and have joined the Joint
-   Accelerator Conferences Website (JACoW) collaboration
-   for the publication of their proceedings. This document
-   describes the common requirements for the submission of
-   papers to these conferences. Please consult individual
-   conference information for page limits, method of electronic
-   submission, etc. It is not intended that this should
-   be a tutorial in word processing; the aim is to explain the
-   particular requirements for electronic publication at
-   www.JACoW.org. The abstract itself is to act as a stand-alone
-   entity and, as such, should not include citations. Any acronyms 
-   should be expanded on their first occurrence, both in the 
-   abstract and in the rest of the paper. 
-   The abstract itself is to act as a stand-alone entity and, 
-   as such, should not include citations. Any acronyms should 
-   be expanded on their first occurrence, both in the abstract 
-   and in the rest of the paper.
-\end{abstract}
-
-\section{SUBMISSION OF PAPERS}
-Each author should submit the PDF file and all source
-files (text and figures) to enable the paper to be
-reconstructed if there are processing difficulties.
-
-\section{MANUSCRIPTS}
-Templates are provided for recommended software and
-authors are advised to use them. Please consult the
-individual conference help pages if questions arise.
-
-\subsection{General Layout}
-
-These instructions are a typical implementation of the
-requirements. Manuscripts should have:
-\begin{Itemize}
-    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
-           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
-    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
-           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
-           authors must change this to 1 line.
-    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
-\end{Itemize}
-\begin{table}[!hbt]
-   \centering
-   \caption{Margin Specifications}
-   \begin{tabular}{lcc}
-       \toprule
-       \textbf{Margin} & \textbf{A4 Paper}                      & \textbf{US Letter Paper} \\
-       \midrule
-           Top         & \SI{37}{mm} (\SI{1.46}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
-          Bottom       & \SI{19}{mm} (\SI{0.75}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
-           Left        & \SI{20}{mm} (\SI{0.79}{in})            & \SI{0.79}{in} (\SI{20}{mm})        \\ %[3pt]
-           Right       & \SI{20}{mm} (\SI{0.79}{in})            & \SI{1.02}{in} (\SI{26}{mm})        \\
-       \bottomrule
-   \end{tabular}
-   \label{tab:margins}
-\end{table}
-
-\subsection{Fonts}
-
-In order to produce good Adobe Acrobat PDF files, authors
-using the `jacow' \LaTeX{} template are asked to use only the fonts
-defined in the ‘jacow’ class file (v2.3 of 2019/01/15) in standard, 
-bold (i.\,e., \verb|\textbf|) or italic (i.\,e., \verb|\textit|) form and
-symbols from the standard set of fonts. In Word use only
-Symbol and, depending on your platform, Times or Times New Roman
-fonts in standard, bold or italic form.
-
-The layout of the text on the page is illustrated in
-Fig.~\ref{fig:paper_layout}. Note that the paper’s title and the author list should
-be the width of the full page. Tables and figures may span
-the whole \SI{170}{mm} page width, if desired (see Fig.~\ref{fig:jacow_team}), but
-if they span both columns, they should be placed at either
-the top or bottom of a page to ensure proper flow of the
-text (which should flow from top to bottom in each column).
-
-\begin{figure}[!htb]
-   \centering
-   \includegraphics*[width=.7\columnwidth]{JACpic_mc}
-   \caption{Layout of papers.}
-   \label{fig:paper_layout}
-\end{figure}
-
-\begin{figure*}[!tbh]
-    \centering
-    \includegraphics*[width=\textwidth]{JACpic2}
-
-    \caption{Example of a full-width figure showing the JACoW Team at their annual
-    	     meeting in December 2018. This figure has a multi-line caption that has to be
-    	     justified rather than centred.}
-    \label{fig:jacow_team}
-\end{figure*}
-
-\subsection{Title and Author List}
-
-The title should use \SI{14}{pt} bold uppercase letters and be centred on the page.
-Individual letters may be lowercased to avoid misinterpretation (e.\,g., mW, GeV, 
-SPring-8, SwissFEL).
-To include a funding support statement, put an asterisk after the title and
-the support text at the bottom of the first column on page~1---in Word,
-use a text box; in \LaTeX, use $\backslash$\texttt{thanks}. See also the
-subsection on footnotes.
-
-The names of authors, their organizations/affiliations and
-postal addresses should be grouped by affiliation and
-listed in \SI{12}{pt} upper- and lowercase letters. The name of
-the submitting or primary author should be first, followed
-by the coauthors, alphabetically by affiliation. Where
-authors have multiple affiliations, the secondary affiliation
-may be indicated with a superscript, as shown in the
-author listing of this paper. See \textbf{ANNEX~A} for further examples.
-
-\subsection{Section Headings}
-
-Section headings should not be numbered. They should
-use  \SI{12}{pt}  bold  uppercase  letters  and  be  centred  in  the
-column. All section headings should appear directly above
-the text---there should never be a column break between a heading and the
-following paragraph.
-
-\subsection{Subsection Headings}
-
-Subsection  headings  should  not  be  numbered.
-They should use \SI{12}{pt} italic letters and be left aligned in the column.
-Subsection headings use Title Case (or Initial Caps)
-and should appear directly above the text---there should never be a column break
-between a subheading and the following paragraph.
-
-\subsubsection{Third-level Headings} These should use \SI{10}{pt} bold
-letters and be run into the paragraph text. In \LaTeX{} these headings are
-created with \LaTeX's \verb|\subsubsection| command.
-In the Word templates authors must bold the heading text themselves.
-This heading should be used sparingly. See Table~\ref{tab:styles}
-for its style details.
-
-\subsection{Paragraph Text}
-
-Paragraphs should use \SI{10}{pt} font and be justified (touch each side) in
-the column. The beginning of each paragraph should be indented
-approximately \SI{0.33}{cm} (\SI{0.13}{in}). The last line of a paragraph should not be
-printed by itself at the beginning of a column nor should the first line of
-a paragraph be printed by itself at the end of a column.
-
-\subsection{Figures, Tables and Equations}
-
-Place figures and tables as close to their place of mention as
-possible. Lettering in figures and tables should be large enough to
-reproduce clearly. Use of non-approved fonts in figures can lead to
-problems when the files are processed. \LaTeX{} users should be sure to use
-non-bitmapped versions of Computer Modern fonts in equations (Type\,1 PostScript
-or OpenType fonts are required. Their use is described in the help 
-pages of the JACoW website\cite{jacow-help}).
-
-Each figure and table must be numbered in ascending
-order (1, 2, 3, etc.) throughout the paper. 
-Figure captions are placed below figures, and table
-captions are placed above tables.
-
-Figure captions are formatted as shown in Figs.~\ref{fig:paper_layout} and \ref{fig:jacow_team},
-while table captions take the form of a heading,
-with initial letters of principle words, capitalized, and
-without a period at the end (see Tables~\ref{tab:margins} and~\ref{tab:styles}).
-Any reference to the contents of the table should be made from
-the body of the paper rather than from within the table
-caption itself.
-
-Single-line captions are centred in the column, while captions
-that span more than one line should be justified.
-The \LaTeX{} template uses the ‘booktabs’ package to
-format tables.
-
-When referring to a figure from within the text, the
-convention is to use the abbreviated form [e.\,g., Fig.~1]
-\emph{unless} the reference is at the start of the sentence, in
-which case “Figure” is written in full. Reference to a
-table, however, is never abbreviated [e.\,g., Table~1].
-
-If a displayed equation needs a number (i.\,e., it will be
-referenced), place it in parentheses, and flush with the
-right margin of the column. The equation itself should be
-indented and centred, as far as is possible:
-\begin{equation}\label{eq:label}
-    C_B=\frac{q^3}{3\epsilon_{0} mc}=\SI{3.54}{\micro eV/T}
-\end{equation}
-
-When referencing a numbered equation, use the word
-“Equation” at the start of a sentence, and the abbreviated
-form, “Eq.”, if in the text. The equation number is placed
-in parentheses [e.\,g., Eq.~\eqref{eq:label}], which can be 
-achieved in \LaTeX{} using \verb|\eqref{eq:label}|.
-
-\subsection{Units}
-
-Units should be written using the standard, roman font,
-not the italic font, as shown in Eq.~\eqref{eq:label}.
-An unbreakable space should precede a unit (in \LaTeX{} use a “\verb|\,|”,
-the template uses the ‘siunitx’ package to format units).
-Some examples are: \SI{3}{keV},
-\SI{100}{kW}, \SI{7}{µm}. When a unit appears in a hyphenated,
-compound adjective that precedes a noun, it takes on the
-singular form, e.\,g., the 3.8-metre long undulator.
-
-\subsection{References}
-%
-% References examples given here are not formatted using \cite as there
-%			 are only reference numbers [1] and [2] in the template
-%
-All bibliographical and web references should be numbered and listed at the
-end of the paper in a section called \textbf{REFERENCES}. When citing a
-reference in the text, place the corresponding reference number in square
-brackets~[1]. The reference citations in the text should be numbered
-in ascending order. Multiple citations should appear in
-the same bracket~[3, 4] and
-with ranges where appropriate~[1--4, 10].
-
-A URL or DOI may be included as part of a reference, but its
-hyperlink should NOT be added. The usual practice is to
-use a monospaced font for the URL so as to help distinguish
-it from normal text. In \LaTeX{} the ‘url’ package is used with its 
-default font now being switched to ``newtxtt'' which offers
-a better distinction between ``\texttt{O}'' and ``\texttt{0}''.
-
-For authors to properly cite the resources used when researching
-their papers is an obligation. In the interest of
-promoting uniformity and complete citations, the IEEE
-Editorial Style for Transactions and Journals, which itself 
-adheres to the Chicago Manual of Style, has been adopted~\cite{IEEE}. 
-When citing a periodical, the official abbreviation of the journal 
-should be used\cite{journal-abbreviations}.
-Please consult the appended material, \textbf{ANNEX~B},
-for details. The onus is on authors to pay attention to
-the details of the said style to ensure complete, accurate
-and properly formatted references.
-
-  \begin{table}[h!b]
-	\setlength\tabcolsep{3.5pt}
-	\centering
-	\caption{Summary of Styles}
-	\label{tab:styles}
-	\begin{tabular}{llcc}
-		\toprule
-		\textbf{Style} & \textbf{Font}               & \textbf{Space}  & \textbf{Space} \\
-		&                             & \textbf{Before} & \textbf{After} \\
-		\midrule
-		\textbf{PAPER}  & \SI{14}{pt}                 & \SI{0}{pt}      & \SI{3}{pt}  \\
-		\textbf{TITLE}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{EXCEPT FOR}         &                 &      \\
-		& \textbf{REQUIRED lowercase} &                 &      \\
-		& \textbf{letters}            &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Author list  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{12}{pt} \\
-		& UPPER- and lowercase        &                 &      \\[5pt]
-		%\midrule
-		\textit{Abstract} & \SI{12}{pt}                 & \SI{0}{pt}      & \SI{3}{pt} \\
-		\textit{Title}  & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Section}  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{3}{pt}  \\
-		\textbf{Heading}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{bold}               &                 &      \\[5pt]
-		%\midrule
-		\textit{Subsection} & \SI{12}{pt}                 & \SI{6}{pt}      & \SI{3}{pt}  \\
-		\textit{Heading}
-                             & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Third-level} & \SI{10}{pt}                 & \SI{6}{pt}      & \SI{0}{pt}  \\
-		\textbf{Heading}     
-                            & \textbf{Initial Caps}       &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Figure        & \SI{10}{pt}                 & \SI{3}{pt}      & $\ge$\SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Table         & \SI{10}{pt}                 & $\ge$\SI{3}{pt} & \SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Equations     & \SI{10}{pt} base font       & $\ge$\SI{6}{pt}     & $\ge$\SI{6}{pt} \\[5pt]
-		%\midrule
-		References      & \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt} \\
-        when $\le9$ 	& \verb|\bibliography{9}|	&                 &  \\[5pt]
-        Refs. $\ge10$ 	& \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt}  \\
-                		& \verb|\bibliography{99}|	&    &    \\
-		\bottomrule   %\SI{0.25}{in}
-	\end{tabular}
-\end{table}
-
-\subsection{Footnotes}
-
-Footnotes on the title and author lines may be used for acknowledgements
-and e-mail addresses. A non-numeric sequence of characters (*, \#,
-\dag, \ddag, \P) should be used to indicate the footnote.
-These “pseudo footnotes” should only
-appear at the bottom of the first column on the first page.
-
-Any other footnote in the body of the paper should
-use the normal numeric sequencing (i.\,e., 1, 2, 3)
-and appear at the bottom of the same column in which
-it is used.  All footnotes are of 8pt font size.
-
-\subsection{Acronyms}
-
-Acronyms should be defined the first time they appear, 
-both in the abstract and in the rest of the paper.
-
-\section{STYLES}
-
-Table~\ref{tab:styles} summarizes the fonts and spacing used in the styles of
-a JACoW template. In \LaTeX, these 
-are implemented in the ‘jacow’ class file.
-
-\section{PAGE NUMBERS}
-
-\textbf{DO NOT include any page numbers}. They will be added
-when the final proceedings are produced.
-
-\section{TEMPLATES}
-
-Template documents for the recommended word processing
-software are available from the JACoW website~\cite{jacow-help}
-and exist for \LaTeX, Microsoft Word (Mac and PC)
-and LibreOffice/Apache OpenOffice for US letter and A4
-paper sizes. Use the correct template for your paper size and
-platform.
-
-Fonts are embedded by default with pdf\LaTeX. Using \LaTeX{} with `dvips', 
-make sure that `ps2pdf' has the option \texttt{-dEmbedAllFonts=true}'.
-Fonts of included figure graphics in PDF or EPS are often not embedded. 
-So make sure that this done when generating them or reprocess them 
-in `Ghostscript' with the switch \texttt{-dEmbedAllFonts=true}' set.
-
-\flushcolsend
-
-\section{CHECKLIST FOR ELECTRONIC PUBLICATION}
-Authors are requested to go over the following checklist for electronic publication:
-\begin{Itemize}
-	\item  Use only Times or Times New Roman (standard, bold or italic) and Symbol
-	fonts for text, \SI{10}{pt} except references, which should be \SI{9}{pt}.
-
-	\item  Figures should use Times or Times New Roman (standard, bold or italic) and
-	Symbol fonts when possible---\SI{6}{pt} minimum, with fonts embedded.
-	\item  Check that citations to references appear in sequential order and
-	that all references are cited.
-	\item  Check that the PDF file prints correctly.
-	\item  Check that there are no page numbers.
-	\item  Check that the margins on the printed version are within \SI{\pm1}{mm}
-	of the specifications.
-	\item  \LaTeX{} users can check their margins by invoking the
-	\texttt{boxit} option.
-\end{Itemize}
-
-Please also check the list of common oversights which can be found in \textbf{ANNEX C}.
-
-\section{CONCLUSION}
-
-Any conclusions should be in a separate section directly preceding
-the \textbf{ACKNOWLEDGEMENTS}, \textbf{APPENDIX}, or \textbf{REFERENCES} sections, in that
-order.
-
-\section{ACKNOWLEDGEMENTS}
-Any acknowledgement should be in a separate section directly preceding
-the \textbf{REFERENCES} or \textbf{APPENDIX} section.
-
-\section{APPENDIX}
-Any appendix should be in a separate section directly preceding
-the \textbf{REFERENCES} section. If there is no \textbf{REFERENCES} section,
-this should be the last section of the paper.
-
-%
-% only for "biblatex"
-%
 \ifboolexpr{bool{jacowbiblatex}}%
@@
 } % end \ifboolexpr
-%
-% for use as JACoW template the inclusion of the ANNEX parts have been commented out
-% to generate the complete documentation please remove the "%" of the next two commands
-% 
-%%%\newpage
-
-%%%\include{annexes-A4}
-
-\end{document}

### 2024-02-25 paper.tex
separated acknowledgements appendix and bibliography

@@
 \section{CONCLUSION}
-
 Any conclusions should be in a separate section directly preceding
@@
 
-\section{ACKNOWLEDGEMENTS}
-Any acknowledgement should be in a separate section directly preceding
-the \textbf{REFERENCES} or \textbf{APPENDIX} section.
-
-\section{APPENDIX}
-Any appendix should be in a separate section directly preceding
-the \textbf{REFERENCES} section. If there is no \textbf{REFERENCES} section,
-this should be the last section of the paper.
-
-%
-% only for "biblatex"
-%
-\ifboolexpr{bool{jacowbiblatex}}%
-	{\printbibliography}%
-	{%
-	% "biblatex" is not used, go the "manual" way
-
-	%\begin{thebibliography}{99}   % Use for  10-99  references
-	\begin{thebibliography}{9} % Use for 1-9 references
-
-	\bibitem{jacow-help}
-		JACoW,
-		\url{http://www.jacow.org}
-
-	\bibitem{IEEE}
-		\textit{IEEE Editorial Style Manual},
-		IEEE Periodicals, Piscataway,
-		NJ, USA, Oct. 2014, pp. 34--52.
-
-	\bibitem{journal-abbreviations}
-	\url{https://woodward.library.ubc.ca/researchhelp/journal-abbreviations/}
-
-	\end{thebibliography}
-} % end \ifboolexpr
+\input{acknowledgements}
+\input{appendix}
+\input{bibliography}
 %

### 2024-03-11 tables/margins.tex
tables in individual files

--- 2024-02-25 paper.tex
@@
-% !TeX spellcheck = en_GB
-% !TeX program = lualatex
-
-\documentclass[a4paper,
-               %boxit,        % check whether paper is inside correct margins
-               %titlepage,    % separate title page
-               %refpage       % separate references
-               %biblatex,     % biblatex is used
-               keeplastbox,   % flushend option: not to un-indent last line in References
-               %nospread,     % flushend option: do not fill with whitespace to balance columns
-               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
-               %xetex,        % use XeLaTeX to process the file
-               %luatex,       % use LuaLaTeX to process the file
-               ]{jacow}
-%
-% ONLY FOR \footnote in table/tabular
-%
-\usepackage{pdfpages,multirow,ragged2e} %
-%
-% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
-% ----------------------------------------------------
-% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
-%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
-%    might generates errors, therefore PNG and JPG first
-%
-\makeatletter%
-	\ifboolexpr{bool{xetex}}
-	 {\renewcommand{\Gin@extensions}{.pdf,%
-	                    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
-	                    .eps,.ps,%
-	                    }}{}
-\makeatother
-
-% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
-% --------------------------------------------------------
-%   utf8  is default for XeTeX/LuaTeX
-%   utf8  in LaTeX only realises a small portion of codes
-%
-\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
- {}                                      % input encoding is utf8 by default
- {\usepackage[utf8]{inputenc}}           % switch to utf8
-
-\usepackage[USenglish]{babel}
-
-%
-% if BibLaTeX is used
-%
-\ifboolexpr{bool{jacowbiblatex}}%
- {%
-  \addbibresource{jacow-test.bib}
-  \addbibresource{biblatex-examples.bib}
- }{}
-\listfiles
-
-%%
-%%   Lengths for the spaces in the title
-%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
-%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
-%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em
-
-\begin{document}
-
-\title{preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}}
-
-\author{A. N. Author\thanks{email address}, H. Coauthor, Name of Institute or Affiliation, City, Country \\
-		P. Contributor\textsuperscript{1}, Name of Institute or Affiliation, City, Country \\
-		\textsuperscript{1}also at Name of Secondary Institute or Affiliation, City, Country}
-
-\maketitle
-
-%
-\begin{abstract}
-   Many conference series have adopted the same standards
-   for electronic publication and have joined the Joint
-   Accelerator Conferences Website (JACoW) collaboration
-   for the publication of their proceedings. This document
-   describes the common requirements for the submission of
-   papers to these conferences. Please consult individual
-   conference information for page limits, method of electronic
-   submission, etc. It is not intended that this should
-   be a tutorial in word processing; the aim is to explain the
-   particular requirements for electronic publication at
-   www.JACoW.org. The abstract itself is to act as a stand-alone
-   entity and, as such, should not include citations. Any acronyms 
-   should be expanded on their first occurrence, both in the 
-   abstract and in the rest of the paper. 
-   The abstract itself is to act as a stand-alone entity and, 
-   as such, should not include citations. Any acronyms should 
-   be expanded on their first occurrence, both in the abstract 
-   and in the rest of the paper.
-\end{abstract}
-
-\section{SUBMISSION OF PAPERS}
-Each author should submit the PDF file and all source
-files (text and figures) to enable the paper to be
-reconstructed if there are processing difficulties.
-
-\section{MANUSCRIPTS}
-Templates are provided for recommended software and
-authors are advised to use them. Please consult the
-individual conference help pages if questions arise.
-
-\subsection{General Layout}
-
-These instructions are a typical implementation of the
-requirements. Manuscripts should have:
-\begin{Itemize}
-    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
-           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
-    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
-           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
-           authors must change this to 1 line.
-    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
-\end{Itemize}
 \begin{table}[!hbt]
@@
 \end{table}
-
-\subsection{Fonts}
-
-In order to produce good Adobe Acrobat PDF files, authors
-using the `jacow' \LaTeX{} template are asked to use only the fonts
-defined in the ‘jacow’ class file (v2.3 of 2019/01/15) in standard, 
-bold (i.\,e., \verb|\textbf|) or italic (i.\,e., \verb|\textit|) form and
-symbols from the standard set of fonts. In Word use only
-Symbol and, depending on your platform, Times or Times New Roman
-fonts in standard, bold or italic form.
-
-The layout of the text on the page is illustrated in
-Fig.~\ref{fig:paper_layout}. Note that the paper’s title and the author list should
-be the width of the full page. Tables and figures may span
-the whole \SI{170}{mm} page width, if desired (see Fig.~\ref{fig:jacow_team}), but
-if they span both columns, they should be placed at either
-the top or bottom of a page to ensure proper flow of the
-text (which should flow from top to bottom in each column).
-
-\begin{figure}[!htb]
-   \centering
-   \includegraphics*[width=.7\columnwidth]{JACpic_mc}
-   \caption{Layout of papers.}
-   \label{fig:paper_layout}
-\end{figure}
-
-\begin{figure*}[!tbh]
-    \centering
-    \includegraphics*[width=\textwidth]{JACpic2}
-
-    \caption{Example of a full-width figure showing the JACoW Team at their annual
-    	     meeting in December 2018. This figure has a multi-line caption that has to be
-    	     justified rather than centred.}
-    \label{fig:jacow_team}
-\end{figure*}
-
-\subsection{Title and Author List}
-
-The title should use \SI{14}{pt} bold uppercase letters and be centred on the page.
-Individual letters may be lowercased to avoid misinterpretation (e.\,g., mW, GeV, 
-SPring-8, SwissFEL).
-To include a funding support statement, put an asterisk after the title and
-the support text at the bottom of the first column on page~1---in Word,
-use a text box; in \LaTeX, use $\backslash$\texttt{thanks}. See also the
-subsection on footnotes.
-
-The names of authors, their organizations/affiliations and
-postal addresses should be grouped by affiliation and
-listed in \SI{12}{pt} upper- and lowercase letters. The name of
-the submitting or primary author should be first, followed
-by the coauthors, alphabetically by affiliation. Where
-authors have multiple affiliations, the secondary affiliation
-may be indicated with a superscript, as shown in the
-author listing of this paper. See \textbf{ANNEX~A} for further examples.
-
-\subsection{Section Headings}
-
-Section headings should not be numbered. They should
-use  \SI{12}{pt}  bold  uppercase  letters  and  be  centred  in  the
-column. All section headings should appear directly above
-the text---there should never be a column break between a heading and the
-following paragraph.
-
-\subsection{Subsection Headings}
-
-Subsection  headings  should  not  be  numbered.
-They should use \SI{12}{pt} italic letters and be left aligned in the column.
-Subsection headings use Title Case (or Initial Caps)
-and should appear directly above the text---there should never be a column break
-between a subheading and the following paragraph.
-
-\subsubsection{Third-level Headings} These should use \SI{10}{pt} bold
-letters and be run into the paragraph text. In \LaTeX{} these headings are
-created with \LaTeX's \verb|\subsubsection| command.
-In the Word templates authors must bold the heading text themselves.
-This heading should be used sparingly. See Table~\ref{tab:styles}
-for its style details.
-
-\subsection{Paragraph Text}
-
-Paragraphs should use \SI{10}{pt} font and be justified (touch each side) in
-the column. The beginning of each paragraph should be indented
-approximately \SI{0.33}{cm} (\SI{0.13}{in}). The last line of a paragraph should not be
-printed by itself at the beginning of a column nor should the first line of
-a paragraph be printed by itself at the end of a column.
-
-\subsection{Figures, Tables and Equations}
-
-Place figures and tables as close to their place of mention as
-possible. Lettering in figures and tables should be large enough to
-reproduce clearly. Use of non-approved fonts in figures can lead to
-problems when the files are processed. \LaTeX{} users should be sure to use
-non-bitmapped versions of Computer Modern fonts in equations (Type\,1 PostScript
-or OpenType fonts are required. Their use is described in the help 
-pages of the JACoW website\cite{jacow-help}).
-
-Each figure and table must be numbered in ascending
-order (1, 2, 3, etc.) throughout the paper. 
-Figure captions are placed below figures, and table
-captions are placed above tables.
-
-Figure captions are formatted as shown in Figs.~\ref{fig:paper_layout} and \ref{fig:jacow_team},
-while table captions take the form of a heading,
-with initial letters of principle words, capitalized, and
-without a period at the end (see Tables~\ref{tab:margins} and~\ref{tab:styles}).
-Any reference to the contents of the table should be made from
-the body of the paper rather than from within the table
-caption itself.
-
-Single-line captions are centred in the column, while captions
-that span more than one line should be justified.
-The \LaTeX{} template uses the ‘booktabs’ package to
-format tables.
-
-When referring to a figure from within the text, the
-convention is to use the abbreviated form [e.\,g., Fig.~1]
-\emph{unless} the reference is at the start of the sentence, in
-which case “Figure” is written in full. Reference to a
-table, however, is never abbreviated [e.\,g., Table~1].
-
-If a displayed equation needs a number (i.\,e., it will be
-referenced), place it in parentheses, and flush with the
-right margin of the column. The equation itself should be
-indented and centred, as far as is possible:
-\begin{equation}\label{eq:label}
-    C_B=\frac{q^3}{3\epsilon_{0} mc}=\SI{3.54}{\micro eV/T}
-\end{equation}
-
-When referencing a numbered equation, use the word
-“Equation” at the start of a sentence, and the abbreviated
-form, “Eq.”, if in the text. The equation number is placed
-in parentheses [e.\,g., Eq.~\eqref{eq:label}], which can be 
-achieved in \LaTeX{} using \verb|\eqref{eq:label}|.
-
-\subsection{Units}
-
-Units should be written using the standard, roman font,
-not the italic font, as shown in Eq.~\eqref{eq:label}.
-An unbreakable space should precede a unit (in \LaTeX{} use a “\verb|\,|”,
-the template uses the ‘siunitx’ package to format units).
-Some examples are: \SI{3}{keV},
-\SI{100}{kW}, \SI{7}{µm}. When a unit appears in a hyphenated,
-compound adjective that precedes a noun, it takes on the
-singular form, e.\,g., the 3.8-metre long undulator.
-
-\subsection{References}
-%
-% References examples given here are not formatted using \cite as there
-%			 are only reference numbers [1] and [2] in the template
-%
-All bibliographical and web references should be numbered and listed at the
-end of the paper in a section called \textbf{REFERENCES}. When citing a
-reference in the text, place the corresponding reference number in square
-brackets~[1]. The reference citations in the text should be numbered
-in ascending order. Multiple citations should appear in
-the same bracket~[3, 4] and
-with ranges where appropriate~[1--4, 10].
-
-A URL or DOI may be included as part of a reference, but its
-hyperlink should NOT be added. The usual practice is to
-use a monospaced font for the URL so as to help distinguish
-it from normal text. In \LaTeX{} the ‘url’ package is used with its 
-default font now being switched to ``newtxtt'' which offers
-a better distinction between ``\texttt{O}'' and ``\texttt{0}''.
-
-For authors to properly cite the resources used when researching
-their papers is an obligation. In the interest of
-promoting uniformity and complete citations, the IEEE
-Editorial Style for Transactions and Journals, which itself 
-adheres to the Chicago Manual of Style, has been adopted~\cite{IEEE}. 
-When citing a periodical, the official abbreviation of the journal 
-should be used\cite{journal-abbreviations}.
-Please consult the appended material, \textbf{ANNEX~B},
-for details. The onus is on authors to pay attention to
-the details of the said style to ensure complete, accurate
-and properly formatted references.
-
-  \begin{table}[h!b]
-	\setlength\tabcolsep{3.5pt}
-	\centering
-	\caption{Summary of Styles}
-	\label{tab:styles}
-	\begin{tabular}{llcc}
-		\toprule
-		\textbf{Style} & \textbf{Font}               & \textbf{Space}  & \textbf{Space} \\
-		&                             & \textbf{Before} & \textbf{After} \\
-		\midrule
-		\textbf{PAPER}  & \SI{14}{pt}                 & \SI{0}{pt}      & \SI{3}{pt}  \\
-		\textbf{TITLE}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{EXCEPT FOR}         &                 &      \\
-		& \textbf{REQUIRED lowercase} &                 &      \\
-		& \textbf{letters}            &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Author list  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{12}{pt} \\
-		& UPPER- and lowercase        &                 &      \\[5pt]
-		%\midrule
-		\textit{Abstract} & \SI{12}{pt}                 & \SI{0}{pt}      & \SI{3}{pt} \\
-		\textit{Title}  & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Section}  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{3}{pt}  \\
-		\textbf{Heading}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{bold}               &                 &      \\[5pt]
-		%\midrule
-		\textit{Subsection} & \SI{12}{pt}                 & \SI{6}{pt}      & \SI{3}{pt}  \\
-		\textit{Heading}
-                             & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Third-level} & \SI{10}{pt}                 & \SI{6}{pt}      & \SI{0}{pt}  \\
-		\textbf{Heading}     
-                            & \textbf{Initial Caps}       &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Figure        & \SI{10}{pt}                 & \SI{3}{pt}      & $\ge$\SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Table         & \SI{10}{pt}                 & $\ge$\SI{3}{pt} & \SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Equations     & \SI{10}{pt} base font       & $\ge$\SI{6}{pt}     & $\ge$\SI{6}{pt} \\[5pt]
-		%\midrule
-		References      & \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt} \\
-        when $\le9$ 	& \verb|\bibliography{9}|	&                 &  \\[5pt]
-        Refs. $\ge10$ 	& \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt}  \\
-                		& \verb|\bibliography{99}|	&    &    \\
-		\bottomrule   %\SI{0.25}{in}
-	\end{tabular}
-\end{table}
-
-\subsection{Footnotes}
-
-Footnotes on the title and author lines may be used for acknowledgements
-and e-mail addresses. A non-numeric sequence of characters (*, \#,
-\dag, \ddag, \P) should be used to indicate the footnote.
-These “pseudo footnotes” should only
-appear at the bottom of the first column on the first page.
-
-Any other footnote in the body of the paper should
-use the normal numeric sequencing (i.\,e., 1, 2, 3)
-and appear at the bottom of the same column in which
-it is used.  All footnotes are of 8pt font size.
-
-\subsection{Acronyms}
-
-Acronyms should be defined the first time they appear, 
-both in the abstract and in the rest of the paper.
-
-\section{STYLES}
-
-Table~\ref{tab:styles} summarizes the fonts and spacing used in the styles of
-a JACoW template. In \LaTeX, these 
-are implemented in the ‘jacow’ class file.
-
-\section{PAGE NUMBERS}
-
-\textbf{DO NOT include any page numbers}. They will be added
-when the final proceedings are produced.
-
-\section{TEMPLATES}
-
-Template documents for the recommended word processing
-software are available from the JACoW website~\cite{jacow-help}
-and exist for \LaTeX, Microsoft Word (Mac and PC)
-and LibreOffice/Apache OpenOffice for US letter and A4
-paper sizes. Use the correct template for your paper size and
-platform.
-
-Fonts are embedded by default with pdf\LaTeX. Using \LaTeX{} with `dvips', 
-make sure that `ps2pdf' has the option \texttt{-dEmbedAllFonts=true}'.
-Fonts of included figure graphics in PDF or EPS are often not embedded. 
-So make sure that this done when generating them or reprocess them 
-in `Ghostscript' with the switch \texttt{-dEmbedAllFonts=true}' set.
-
-\flushcolsend
-
-\section{CHECKLIST FOR ELECTRONIC PUBLICATION}
-Authors are requested to go over the following checklist for electronic publication:
-\begin{Itemize}
-	\item  Use only Times or Times New Roman (standard, bold or italic) and Symbol
-	fonts for text, \SI{10}{pt} except references, which should be \SI{9}{pt}.
-
-	\item  Figures should use Times or Times New Roman (standard, bold or italic) and
-	Symbol fonts when possible---\SI{6}{pt} minimum, with fonts embedded.
-	\item  Check that citations to references appear in sequential order and
-	that all references are cited.
-	\item  Check that the PDF file prints correctly.
-	\item  Check that there are no page numbers.
-	\item  Check that the margins on the printed version are within \SI{\pm1}{mm}
-	of the specifications.
-	\item  \LaTeX{} users can check their margins by invoking the
-	\texttt{boxit} option.
-\end{Itemize}
-
-Please also check the list of common oversights which can be found in \textbf{ANNEX C}.
-
-\section{CONCLUSION}
-Any conclusions should be in a separate section directly preceding
-the \textbf{ACKNOWLEDGEMENTS}, \textbf{APPENDIX}, or \textbf{REFERENCES} sections, in that
-order.
-
-\input{acknowledgements}
-\input{appendix}
-\input{bibliography}
-%
-% for use as JACoW template the inclusion of the ANNEX parts have been commented out
-% to generate the complete documentation please remove the "%" of the next two commands
-% 
-%%%\newpage
-
-%%%\include{annexes-A4}
-
-\end{document}

### 2024-03-11 paper.tex
tables replaced by inputs

@@
 \end{Itemize}
-\begin{table}[!hbt]
-   \centering
-   \caption{Margin Specifications}
-   \begin{tabular}{lcc}
-       \toprule
-       \textbf{Margin} & \textbf{A4 Paper}                      & \textbf{US Letter Paper} \\
-       \midrule
-           Top         & \SI{37}{mm} (\SI{1.46}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
-          Bottom       & \SI{19}{mm} (\SI{0.75}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
-           Left        & \SI{20}{mm} (\SI{0.79}{in})            & \SI{0.79}{in} (\SI{20}{mm})        \\ %[3pt]
-           Right       & \SI{20}{mm} (\SI{0.79}{in})            & \SI{1.02}{in} (\SI{26}{mm})        \\
-       \bottomrule
-   \end{tabular}
-   \label{tab:margins}
-\end{table}
+
+\input{tables/margins.tex}
 
@@
 
-  \begin{table}[h!b]
-	\setlength\tabcolsep{3.5pt}
-	\centering
-	\caption{Summary of Styles}
-	\label{tab:styles}
-	\begin{tabular}{llcc}
-		\toprule
-		\textbf{Style} & \textbf{Font}               & \textbf{Space}  & \textbf{Space} \\
-		&                             & \textbf{Before} & \textbf{After} \\
-		\midrule
-		\textbf{PAPER}  & \SI{14}{pt}                 & \SI{0}{pt}      & \SI{3}{pt}  \\
-		\textbf{TITLE}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{EXCEPT FOR}         &                 &      \\
-		& \textbf{REQUIRED lowercase} &                 &      \\
-		& \textbf{letters}            &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Author list  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{12}{pt} \\
-		& UPPER- and lowercase        &                 &      \\[5pt]
-		%\midrule
-		\textit{Abstract} & \SI{12}{pt}                 & \SI{0}{pt}      & \SI{3}{pt} \\
-		\textit{Title}  & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Section}  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{3}{pt}  \\
-		\textbf{Heading}  & \textbf{UPPERCASE}          &                 &      \\
-		& \textbf{bold}               &                 &      \\[5pt]
-		%\midrule
-		\textit{Subsection} & \SI{12}{pt}                 & \SI{6}{pt}      & \SI{3}{pt}  \\
-		\textit{Heading}
-                             & \textit{Initial Caps}       &                 &      \\
-		& \textit{Italic}             &                 &      \\[5pt]
-		%\midrule
-		\textbf{Third-level} & \SI{10}{pt}                 & \SI{6}{pt}      & \SI{0}{pt}  \\
-		\textbf{Heading}     
-                            & \textbf{Initial Caps}       &                 &      \\
-		& \textbf{Bold}               &                 &      \\[5pt]
-		%\midrule
-		Figure        & \SI{10}{pt}                 & \SI{3}{pt}      & $\ge$\SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Table         & \SI{10}{pt}                 & $\ge$\SI{3}{pt} & \SI{3}{pt}  \\
-		Captions      &                             &                 &      \\[5pt]
-		%\midrule
-		Equations     & \SI{10}{pt} base font       & $\ge$\SI{6}{pt}     & $\ge$\SI{6}{pt} \\[5pt]
-		%\midrule
-		References      & \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt} \\
-        when $\le9$ 	& \verb|\bibliography{9}|	&                 &  \\[5pt]
-        Refs. $\ge10$ 	& \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt}  \\
-                		& \verb|\bibliography{99}|	&    &    \\
-		\bottomrule   %\SI{0.25}{in}
-	\end{tabular}
-\end{table}
+\input{tables/styles.tex}
 

### 2024-03-11 paper.tex
the first imports moved to single file which is then imported in the paper

@@
-% !TeX spellcheck = en_GB
-% !TeX program = lualatex
-
-\documentclass[a4paper,
-               %boxit,        % check whether paper is inside correct margins
-               %titlepage,    % separate title page
-               %refpage       % separate references
-               %biblatex,     % biblatex is used
-               keeplastbox,   % flushend option: not to un-indent last line in References
-               %nospread,     % flushend option: do not fill with whitespace to balance columns
-               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
-               %xetex,        % use XeLaTeX to process the file
-               %luatex,       % use LuaLaTeX to process the file
-               ]{jacow}
-%
-% ONLY FOR \footnote in table/tabular
-%
-\usepackage{pdfpages,multirow,ragged2e} %
-%
-% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
-% ----------------------------------------------------
-% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
-%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
-%    might generates errors, therefore PNG and JPG first
-%
-\makeatletter%
-	\ifboolexpr{bool{xetex}}
-	 {\renewcommand{\Gin@extensions}{.pdf,%
-	                    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
-	                    .eps,.ps,%
-	                    }}{}
-\makeatother
-
-% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
-% --------------------------------------------------------
-%   utf8  is default for XeTeX/LuaTeX
-%   utf8  in LaTeX only realises a small portion of codes
-%
-\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
- {}                                      % input encoding is utf8 by default
- {\usepackage[utf8]{inputenc}}           % switch to utf8
-
-\usepackage[USenglish]{babel}
-
-%
-% if BibLaTeX is used
-%
-\ifboolexpr{bool{jacowbiblatex}}%
- {%
-  \addbibresource{jacow-test.bib}
-  \addbibresource{biblatex-examples.bib}
- }{}
-\listfiles
-
-%%
-%%   Lengths for the spaces in the title
-%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
-%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
-%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em
+\input{header.tex}
 

### 2024-03-11 paper.tex
added abstract and title of the paper

@@
 
-\title{preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}}
+\title{LHC abort gap monitor electronics upgrade}
 
-\author{A. N. Author\thanks{email address}, H. Coauthor, Name of Institute or Affiliation, City, Country \\
-		P. Contributor\textsuperscript{1}, Name of Institute or Affiliation, City, Country \\
-		\textsuperscript{1}also at Name of Secondary Institute or Affiliation, City, Country}
+\author{P. Pacner\thanks{petr.pacner@cern.ch}, Brno University of Technology, Brno, Czech Republic \\
+		S. B. Pedersen, D. Belohrad, M. M. Nieto, S. Mazzoni, CERN, Geneva, Switzerland}
 
@@
 
-%
 \begin{abstract}
-   Many conference series have adopted the same standards
-   for electronic publication and have joined the Joint
-   Accelerator Conferences Website (JACoW) collaboration
-   for the publication of their proceedings. This document
-   describes the common requirements for the submission of
-   papers to these conferences. Please consult individual
-   conference information for page limits, method of electronic
-   submission, etc. It is not intended that this should
-   be a tutorial in word processing; the aim is to explain the
-   particular requirements for electronic publication at
-   www.JACoW.org. The abstract itself is to act as a stand-alone
-   entity and, as such, should not include citations. Any acronyms 
-   should be expanded on their first occurrence, both in the 
-   abstract and in the rest of the paper. 
-   The abstract itself is to act as a stand-alone entity and, 
-   as such, should not include citations. Any acronyms should 
-   be expanded on their first occurrence, both in the abstract 
-   and in the rest of the paper.
+    The LHC Abort Gap Monitor (AGM) is part of the LHC machine protection
+    system (MPS) and is designed to measure the particle population in a 3us
+    wide region known as the "abort gap." This region needs to be kept empty to
+    ensure safe beam dumps. The AGM captures the synchrotron light generated in
+    the visible part of the spectra and converts it into an electric signal.
+    This signal is then processed by an acquisition system and can trigger the
+    ‘abort gap cleaning’ process.\\
+    The current AGM, which has been in operation since 2010, uses an analogue
+    integrator ASIC and a 40 MHz analogue-to-digital (ADC) converter to provide
+    the particle population information. However, this solution is now
+    considered obsolete and is being replaced by a digital signal processing
+    approach. Working directly in the digital domain not only offers more
+    scalability but also better determinism and reliability. \\
+    This work presents the new technical solution for the acquisition chain,
+    compares the characteristics of both implementations, and showcases recent
+    measurements conducted on the LHC ion and proton beams.
 \end{abstract}

### 2024-03-12 bibliography.tex
added literature from my thesis

@@
 \ifboolexpr{bool{jacowbiblatex}}%
-	{\printbibliography}%
-	{%
-	% "biblatex" is not used, go the "manual" way
+{\printbibliography}{
 
-	%\begin{thebibliography}{99}   % Use for  10-99  references
-	\begin{thebibliography}{9} % Use for 1-9 references
+    \begin{thebibliography}{99}
 
-	\bibitem{jacow-help}
-		JACoW,
-		\url{http://www.jacow.org}
+        % http://cds.cern.ch/record/782076/files/CERN-2004-003-V1.pdf?version=2
+        \bibitem{LHC_report} BR\"UNING, O. \emph{LHC design report Volume I The LHC
+            Main Ring}. Geneva: European Organization for Nuclear Research, c2004-. CERN
+            (Series), 2004-003. ISBN 92-9083-224-0
 
-	\bibitem{IEEE}
-		\textit{IEEE Editorial Style Manual},
-		IEEE Periodicals, Piscataway,
-		NJ, USA, Oct. 2014, pp. 34--52.
+        \bibitem{abort_gap_monitor}De Santis, S., Beche, J., Byrd, J., Placidi, M.,
+            Turner, W. \& Zolotorev, M. \emph{Development of an Abort Gap Monitor for the
+            Large Hadron Collider}.  (2004), \url{https://cds.cern.ch/record/823343}
 
-	\bibitem{journal-abbreviations}
-	\url{https://woodward.library.ubc.ca/researchhelp/journal-abbreviations/}
+        % https://cds.cern.ch/record/1272172/files/CERN-BE-2010-026.pdf
+        \bibitem{bsra_operation}Bart Pedersen, S., Lefevre, T., Bravin, E., Boccardi, A.,
+            Goldblatt, A., Jeff, A., Roncarolo, F. \& Fisher, A. \emph{First Operation of
+            the Abort Gap Monitors for LHC}.  (2010,5), \url{http://cds.cern.ch/record/1272172}
 

### 2024-03-12 paper.tex
added introduction part - needs to be modified yet

@@
 
-\section{SUBMISSION OF PAPERS}
-Each author should submit the PDF file and all source
-files (text and figures) to enable the paper to be
-reconstructed if there are processing difficulties.
+\section{Introduction}
+The Large Hadron Collider (LHC) operates with high-energy beams that possess
+the capacity to melt metals and induce quenching in magnets, necessitating
+precise control measures to manage the beam when exiting vacuum compartments.
+The LHC beam consists of 2808 bunch slots, organized in bunch trains with a
+3~$\mu$s gap, determined by kicker magnet specifications for controlled
+beam expulsion from vacuum chambers.\\
+This paper addresses the imperative need for an electronics upgrade in the AGM
+system. The current AGM, operational since 2010, relies on an analogue
+integrator ASIC and a 40 MHz analogue-to-digital converter (ADC) for particle
+population measurements. Recognizing the obsolescence of this analogue
+solution, the paper introduces a transition to a digital signal processing
+approach. Working directly in the digital domain not only offers more
+scalability but also better determinism and reliability.\\
+The following sections delve into the current AGM system, its limitations, the
+rationale for the upgrade, the new technical solution, a comparative
+measurements.
 
-\section{MANUSCRIPTS}
-Templates are provided for recommended software and
-authors are advised to use them. Please consult the
-individual conference help pages if questions arise.
+\section{Current system design}
+        %description of the system
+        %Utilization of Analogue Integrator ASIC
+        %40 MHz Analogue-to-Digital Converter (ADC)
+        %Operation Since 2010
+        %Reasons for Obsolescence
+        %Digital Signal Processing Approach why and outcomes
+    \subsection{Technical Solution}
+        %Utilization of Analogue Integrator ASIC
+        %40 MHz Analogue-to-Digital Converter (ADC)
+        %Operation Since 2010
+        %Reasons for Obsolescence
+        %Digital Signal Processing Approach why and outcomes
 
-\subsection{General Layout}
+\section{New fully digitized AGM}
+    \subsection{}
 
-These instructions are a typical implementation of the
-requirements. Manuscripts should have:
-\begin{Itemize}
-    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
-           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
-    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
-           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
-           authors must change this to 1 line.
-    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
-\end{Itemize}
+\section{Comparison of Implementations}
+    %compare the changes and comment the expected changes
 
-\input{tables/margins.tex}
+\section{Recent Measurements}
 
-\subsection{Fonts}
+\section{Discussion}
+    \subsection{Significance of the Upgrade}
+    \subsection{Future Implications}
+    % \subsubsection{Potential for Further Enhancements or Modifications}
+    % \subsubsection{Integration with Other Accelerator Technologies}
 
-In order to produce good Adobe Acrobat PDF files, authors
-using the `jacow' \LaTeX{} template are asked to use only the fonts
-defined in the ‘jacow’ class file (v2.3 of 2019/01/15) in standard, 
-bold (i.\,e., \verb|\textbf|) or italic (i.\,e., \verb|\textit|) form and
-symbols from the standard set of fonts. In Word use only
-Symbol and, depending on your platform, Times or Times New Roman
-fonts in standard, bold or italic form.
-
-The layout of the text on the page is illustrated in
-Fig.~\ref{fig:paper_layout}. Note that the paper’s title and the author list should
-be the width of the full page. Tables and figures may span
-the whole \SI{170}{mm} page width, if desired (see Fig.~\ref{fig:jacow_team}), but
-if they span both columns, they should be placed at either
-the top or bottom of a page to ensure proper flow of the
-text (which should flow from top to bottom in each column).
-
-\begin{figure}[!htb]
-   \centering
-   \includegraphics*[width=.7\columnwidth]{JACpic_mc}
-   \caption{Layout of papers.}
-   \label{fig:paper_layout}
-\end{figure}
-
-\begin{figure*}[!tbh]
-    \centering
-    \includegraphics*[width=\textwidth]{JACpic2}
-
-    \caption{Example of a full-width figure showing the JACoW Team at their annual
-    	     meeting in December 2018. This figure has a multi-line caption that has to be
-    	     justified rather than centred.}
-    \label{fig:jacow_team}
-\end{figure*}
-
-\subsection{Title and Author List}
-
-The title should use \SI{14}{pt} bold uppercase letters and be centred on the page.
-Individual letters may be lowercased to avoid misinterpretation (e.\,g., mW, GeV, 
-SPring-8, SwissFEL).
-To include a funding support statement, put an asterisk after the title and
-the support text at the bottom of the first column on page~1---in Word,
-use a text box; in \LaTeX, use $\backslash$\texttt{thanks}. See also the
-subsection on footnotes.
-
-The names of authors, their organizations/affiliations and
-postal addresses should be grouped by affiliation and
-listed in \SI{12}{pt} upper- and lowercase letters. The name of
-the submitting or primary author should be first, followed
-by the coauthors, alphabetically by affiliation. Where
-authors have multiple affiliations, the secondary affiliation
-may be indicated with a superscript, as shown in the
-author listing of this paper. See \textbf{ANNEX~A} for further examples.
-
-\subsection{Section Headings}
-
-Section headings should not be numbered. They should
-use  \SI{12}{pt}  bold  uppercase  letters  and  be  centred  in  the
-column. All section headings should appear directly above
-the text---there should never be a column break between a heading and the
-following paragraph.
-
-\subsection{Subsection Headings}
-
-Subsection  headings  should  not  be  numbered.
-They should use \SI{12}{pt} italic letters and be left aligned in the column.
-Subsection headings use Title Case (or Initial Caps)
-and should appear directly above the text---there should never be a column break
-between a subheading and the following paragraph.
-
-\subsubsection{Third-level Headings} These should use \SI{10}{pt} bold
-letters and be run into the paragraph text. In \LaTeX{} these headings are
-created with \LaTeX's \verb|\subsubsection| command.
-In the Word templates authors must bold the heading text themselves.
-This heading should be used sparingly. See Table~\ref{tab:styles}
-for its style details.
-
-\subsection{Paragraph Text}
-
-Paragraphs should use \SI{10}{pt} font and be justified (touch each side) in
-the column. The beginning of each paragraph should be indented
-approximately \SI{0.33}{cm} (\SI{0.13}{in}). The last line of a paragraph should not be
-printed by itself at the beginning of a column nor should the first line of
-a paragraph be printed by itself at the end of a column.
-
-\subsection{Figures, Tables and Equations}
-
-Place figures and tables as close to their place of mention as
-possible. Lettering in figures and tables should be large enough to
-reproduce clearly. Use of non-approved fonts in figures can lead to
-problems when the files are processed. \LaTeX{} users should be sure to use
-non-bitmapped versions of Computer Modern fonts in equations (Type\,1 PostScript
-or OpenType fonts are required. Their use is described in the help 
-pages of the JACoW website\cite{jacow-help}).
-
-Each figure and table must be numbered in ascending
-order (1, 2, 3, etc.) throughout the paper. 
-Figure captions are placed below figures, and table
-captions are placed above tables.
-
-Figure captions are formatted as shown in Figs.~\ref{fig:paper_layout} and \ref{fig:jacow_team},
-while table captions take the form of a heading,
-with initial letters of principle words, capitalized, and
-without a period at the end (see Tables~\ref{tab:margins} and~\ref{tab:styles}).
-Any reference to the contents of the table should be made from
-the body of the paper rather than from within the table
-caption itself.
-
-Single-line captions are centred in the column, while captions
-that span more than one line should be justified.
-The \LaTeX{} template uses the ‘booktabs’ package to
-format tables.
-
-When referring to a figure from within the text, the
-convention is to use the abbreviated form [e.\,g., Fig.~1]
-\emph{unless} the reference is at the start of the sentence, in
-which case “Figure” is written in full. Reference to a
-table, however, is never abbreviated [e.\,g., Table~1].
-
-If a displayed equation needs a number (i.\,e., it will be
-referenced), place it in parentheses, and flush with the
-right margin of the column. The equation itself should be
-indented and centred, as far as is possible:
-\begin{equation}\label{eq:label}
-    C_B=\frac{q^3}{3\epsilon_{0} mc}=\SI{3.54}{\micro eV/T}
-\end{equation}
-
-When referencing a numbered equation, use the word
-“Equation” at the start of a sentence, and the abbreviated
-form, “Eq.”, if in the text. The equation number is placed
-in parentheses [e.\,g., Eq.~\eqref{eq:label}], which can be 
-achieved in \LaTeX{} using \verb|\eqref{eq:label}|.
-
-\subsection{Units}
-
-Units should be written using the standard, roman font,
-not the italic font, as shown in Eq.~\eqref{eq:label}.
-An unbreakable space should precede a unit (in \LaTeX{} use a “\verb|\,|”,
-the template uses the ‘siunitx’ package to format units).
-Some examples are: \SI{3}{keV},
-\SI{100}{kW}, \SI{7}{µm}. When a unit appears in a hyphenated,
-compound adjective that precedes a noun, it takes on the
-singular form, e.\,g., the 3.8-metre long undulator.
-
-\subsection{References}
-%
-% References examples given here are not formatted using \cite as there
-%			 are only reference numbers [1] and [2] in the template
-%
-All bibliographical and web references should be numbered and listed at the
-end of the paper in a section called \textbf{REFERENCES}. When citing a
-reference in the text, place the corresponding reference number in square
-brackets~[1]. The reference citations in the text should be numbered
-in ascending order. Multiple citations should appear in
-the same bracket~[3, 4] and
-with ranges where appropriate~[1--4, 10].
-
-A URL or DOI may be included as part of a reference, but its
-hyperlink should NOT be added. The usual practice is to
-use a monospaced font for the URL so as to help distinguish
-it from normal text. In \LaTeX{} the ‘url’ package is used with its 
-default font now being switched to ``newtxtt'' which offers
-a better distinction between ``\texttt{O}'' and ``\texttt{0}''.
-
-For authors to properly cite the resources used when researching
-their papers is an obligation. In the interest of
-promoting uniformity and complete citations, the IEEE
-Editorial Style for Transactions and Journals, which itself 
-adheres to the Chicago Manual of Style, has been adopted~\cite{IEEE}. 
-When citing a periodical, the official abbreviation of the journal 
-should be used\cite{journal-abbreviations}.
-Please consult the appended material, \textbf{ANNEX~B},
-for details. The onus is on authors to pay attention to
-the details of the said style to ensure complete, accurate
-and properly formatted references.
-
-\input{tables/styles.tex}
-
-\subsection{Footnotes}
-
-Footnotes on the title and author lines may be used for acknowledgements
-and e-mail addresses. A non-numeric sequence of characters (*, \#,
-\dag, \ddag, \P) should be used to indicate the footnote.
-These “pseudo footnotes” should only
-appear at the bottom of the first column on the first page.
-
-Any other footnote in the body of the paper should
-use the normal numeric sequencing (i.\,e., 1, 2, 3)
-and appear at the bottom of the same column in which
-it is used.  All footnotes are of 8pt font size.
-
-\subsection{Acronyms}
-
-Acronyms should be defined the first time they appear, 
-both in the abstract and in the rest of the paper.
-
-\section{STYLES}
-
-Table~\ref{tab:styles} summarizes the fonts and spacing used in the styles of
-a JACoW template. In \LaTeX, these 
-are implemented in the ‘jacow’ class file.
-
-\section{PAGE NUMBERS}
-
-\textbf{DO NOT include any page numbers}. They will be added
-when the final proceedings are produced.
-
-\section{TEMPLATES}
-
-Template documents for the recommended word processing
-software are available from the JACoW website~\cite{jacow-help}
-and exist for \LaTeX, Microsoft Word (Mac and PC)
-and LibreOffice/Apache OpenOffice for US letter and A4
-paper sizes. Use the correct template for your paper size and
-platform.
-
-Fonts are embedded by default with pdf\LaTeX. Using \LaTeX{} with `dvips', 
-make sure that `ps2pdf' has the option \texttt{-dEmbedAllFonts=true}'.
-Fonts of included figure graphics in PDF or EPS are often not embedded. 
-So make sure that this done when generating them or reprocess them 
-in `Ghostscript' with the switch \texttt{-dEmbedAllFonts=true}' set.
-
-\flushcolsend
-
-\section{CHECKLIST FOR ELECTRONIC PUBLICATION}
-Authors are requested to go over the following checklist for electronic publication:
-\begin{Itemize}
-	\item  Use only Times or Times New Roman (standard, bold or italic) and Symbol
-	fonts for text, \SI{10}{pt} except references, which should be \SI{9}{pt}.
-
-	\item  Figures should use Times or Times New Roman (standard, bold or italic) and
-	Symbol fonts when possible---\SI{6}{pt} minimum, with fonts embedded.
-	\item  Check that citations to references appear in sequential order and
-	that all references are cited.
-	\item  Check that the PDF file prints correctly.
-	\item  Check that there are no page numbers.
-	\item  Check that the margins on the printed version are within \SI{\pm1}{mm}
-	of the specifications.
-	\item  \LaTeX{} users can check their margins by invoking the
-	\texttt{boxit} option.
-\end{Itemize}
-
-Please also check the list of common oversights which can be found in \textbf{ANNEX C}.
-
-\section{CONCLUSION}
-Any conclusions should be in a separate section directly preceding
-the \textbf{ACKNOWLEDGEMENTS}, \textbf{APPENDIX}, or \textbf{REFERENCES} sections, in that
-order.
+\section{Conclusion}
+\section{Acknowledgments}
 
@@
 \input{bibliography}
-%
-% for use as JACoW template the inclusion of the ANNEX parts have been commented out
-% to generate the complete documentation please remove the "%" of the next two commands
-% 
-%%%\newpage
 

### 2024-03-13 plots/ions.py
added python code to generate measured data

@@ -1,0 +1,124 @@
+import sys, os
+import matplotlib
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+# matplotlib.use("pgf")
+# matplotlib.rcParams.update({
+#     "pgf.texsystem": "pdflatex",
+#     'font.family': 'serif',
+#     'text.usetex': True,
+#     'pgf.rcfonts': False})
+
+# dir_path = os.path.dirname(sys.argv[1])
+# a = np.loadtxt(os.path.join(dir_path, 'data/filter/indata.txt'), 
+#                encoding='ASCII', dtype='int', skiprows=1)
+# b = np.loadtxt(os.path.join(dir_path, 'data/filter/file_filter.txt'), 
+#                encoding='ASCII', dtype='int', skiprows=1)
+
+# def fixed_to_float(num, N, Q):
+#     binary_num = np.binary_repr(num, N)
+#     s_int = binary_num[0:Q]
+#     s_frac = binary_num[Q:]
+
+#     # resolve the integer part
+#     tmp = -1 if(s_int[0] != '0') else int(s_int, 2)
+#     if((Q > 1) and (s_int[0])):
+#         tmp = -1*(2**(Q-1)) + int(s_int[1:],2)
+#     s_int = tmp
+
+#     # resolve fractional part
+#     s_frac = int(s_frac,2)/(2**(N-Q))
+#     return s_int + s_frac
+
+# def align_array(array, multiples):
+#     tmp = (len(array)%multiples)
+#     if(not tmp): return array
+#     else: return array[:-tmp]
+
+# def data_aligner(data):
+#     #  make each line 64 nums long
+#     d = align_array(data, 64)
+#     arr = np.array(d, dtype=int)
+#     # reshape the data to matrix with
+#     # 64 columns and N rows and then
+#     # read data column by column
+#     arr = np.reshape(arr, (-1, 64))
+#     return arr
+
+# # N = number of digits
+# # Q = number of digits befor floating point
+# def convert_array(np_array, N, Q):
+#     c = lambda n:fixed_to_float(n, N, Q)
+#     convert = np.vectorize(c)
+#     return convert(np_array)
+
+
+# # NOTE this takes numpy array as
+# # an argument the beta and alpha
+# def smoothing_formula(data, alph):
+#     beta = 1 - alph
+#     tmp = np.copy(data)
+#     # add zero on the first place
[…]

### 2024-03-13 bibliography.tex
added new literature

@@
 
+        \bibitem{bsra_calib} A. Boccardi et a1., \emph{Calibration procedures and
+            automated actions for the Abort Gap Monitors of LHC}, (2015, 3), LHC-B SRA-
+            ES-OOOl, \url{https:edms.cern.ch/document/1337184/1}
+
+        \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
+            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
+            (CERN,2010), \url{https://cds.cern.ch/record/1261191}
+
+        \bibitem{particles_in_ag}Meddahi, M., Bart Pedersen, S., Boccardi, A.,
+            Butterworth, A., Fisher, A., Gianfelice-Wendt, E., Goddard, B., Hemelsoet,
+            G., Höfle, W., Jacquet, D., Jaussi, M., Kain, V., Lefevre, T., Shaposhnikova,
+            E., Uythoven, J. \& Valuch, D. LHC Abort Gap Monitoring and Cleaning.
+            (2010,6), \url{https://cds.cern.ch/record/1277630}
+
+        % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
+        \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
+            instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}
+
+        % https://cds.cern.ch/record/1261191/files/performance-note-014.pdf
+        \bibitem{expected_performance_bsrt}Fisher, A. Expected Performance of the LHC
+            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).
+            (CERN, 2010, 3), \url{https://cds.cern.ch/record/1261191}
+
+% other sources
+% https://indico.cern.ch/event/359810/contributions/853246/attachments/716754/983942/BSRA_BI_TB_Feb2015.pdf
+
     \end{thebibliography}

### 2024-03-17 plots/ions.py
pgf ions plot created

@@ -4,121 +4,44 @@ import matplotlib
 import numpy as np
 import matplotlib.pyplot as plt
 
+matplotlib.use("pdf")
+matplotlib.rcParams.update({
+    "pgf.texsystem": "pdflatex",
+    'font.family': 'serif',
+    'text.usetex': True,
+    'pgf.rcfonts': False})
 
-# matplotlib.use("pgf")
-# matplotlib.rcParams.update({
-#     "pgf.texsystem": "pdflatex",
-#     'font.family': 'serif',
-#     'text.usetex': True,
-#     'pgf.rcfonts': False})
+dir_path = os.path.dirname(sys.argv[1])
 
-# dir_path = os.path.dirname(sys.argv[1])
-# a = np.loadtxt(os.path.join(dir_path, 'data/filter/indata.txt'), 
-#                encoding='ASCII', dtype='int', skiprows=1)
-# b = np.loadtxt(os.path.join(dir_path, 'data/filter/file_filter.txt'), 
-#                encoding='ASCII', dtype='int', skiprows=1)
+agm_new = np.loadtxt(os.path.join(dir_path, 'timber_data/vfc_abort_gap_raw_data_spill.txt'), 
+               encoding='ASCII')
 
-# def fixed_to_float(num, N, Q):
-#     binary_num = np.binary_repr(num, N)
-#     s_int = binary_num[0:Q]
-#     s_frac = binary_num[Q:]
+agm_current = np.loadtxt(os.path.join(dir_path, 'timber_data/abort_gap_raw_data_spill.txt'), 
+               encoding='ASCII')
 
-#     # resolve the integer part
-#     tmp = -1 if(s_int[0] != '0') else int(s_int, 2)
-#     if((Q > 1) and (s_int[0])):
-#         tmp = -1*(2**(Q-1)) + int(s_int[1:],2)
-#     s_int = tmp
+fig, ax = plt.subplots()
+plt.plot(agm_current, '--', markersize=2, color=(0, 0.3, 0.3), linewidth=0.8)
+plt.plot(agm_new, '-o', markersize=2, color=(0, 0.3, 0.7), linewidth=0.8)
 
-#     # resolve fractional part
-#     s_frac = int(s_frac,2)/(2**(N-Q))
-#     return s_int + s_frac
+ax.tick_params(axis='both', direction='in', labelcolor='k',
+               labelsize='small', width=0.6, which='both',
+               top=True, right=True)
 
-# def align_array(array, multiples):
[…]

### 2024-03-17 plots/filters.py
3d plot of the output data

@@ -1,0 +1,48 @@
+#!/usr/bin/python
+import math
+import sys, os
+import matplotlib
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import cm
+
+# matplotlib.use("pgf")
+# matplotlib.rcParams.update({
+    # "pgf.texsystem": "pdflatex",
+    # 'font.family': 'serif',
+    # 'text.usetex': True,
+    # 'pgf.rcfonts': False})
+
+# dir_path = os.path.dirname(sys.argv[1])
+a = np.loadtxt(os.path.join('.', 'timber_data/vfc_abort_gap_raw_data_spill.txt'), 
+               encoding='ASCII')
+
+data = np.tile(a, (8, 1))
+
+X = np.arange(data.shape[1])
+Y = np.arange(data.shape[0])
+X, Y = np.meshgrid(X, Y)
+
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+ax.tick_params(axis='y',which='major',length=data.shape[0], width=1, labelsize=12)
+
+# ax.set_yticks([0, len(Y)-1, 1])
+# ax.set_xticks([0, len(X)-1, 1])
+
+surf = ax.plot_wireframe(X, Y, data, rstride=1, cstride=0,
+                   cmap='Oranges', edgecolor=None, linewidth=2, antialiased=True)
+
+plt.xticks(np.arange(0, 64, 9))
+plt.yticks(np.arange(0, 8, 1))
+
+ax.set_ylabel('Time [s]')
+ax.set_xlabel('Filters output [-]')
+ax.set_zlabel('Normalized Amplitude')
+
+ax.view_init(38, -148)
+# plt.show()
+
+# # NOTE USER HAVE TO PASS A PATH IN THE ARGUMENTS TO MAKE THE SCRIPT WORK
+plt.savefig(sys.argv[1])

### 2024-03-18 plots/filters.py
fixed wrong path in 3d plot

@@ -14,8 +14,8 @@ from matplotlib import cm
     # 'text.usetex': True,
     # 'pgf.rcfonts': False})
 
-# dir_path = os.path.dirname(sys.argv[1])
-a = np.loadtxt(os.path.join('.', 'timber_data/vfc_abort_gap_raw_data_spill.txt'), 
+dir_path = os.path.dirname(sys.argv[1])
+a = np.loadtxt(os.path.join(dir_path, 'timber_data/vfc_abort_gap_raw_data_spill.txt'), 
                encoding='ASCII')
 
 data = np.tile(a, (8, 1))

### 2024-03-18 paper.tex
added descriptions for ai
generated pictures added to the paper
created table for comparison of the two systems
added new pictures in the paper

@@
 
-\section{Current system design}
-        %description of the system
-        %Utilization of Analogue Integrator ASIC
-        %40 MHz Analogue-to-Digital Converter (ADC)
-        %Operation Since 2010
-        %Reasons for Obsolescence
-        %Digital Signal Processing Approach why and outcomes
+% lhc works with high energy beam which is strong enought to cause damage to
+% the machine beam bunch train has abort gap at the last bunch slots creating a
+% time gap of 3us this place should be empty because particles in this gap
+% don't get enough thrust to be directed towards the beam dumps and so they hit
+% hit the magnets controling the beam, which can cause quenching in the magnets
+% and losing the control over the beam. 
+% The Abort Gap monitor serves to continuously monitor amount of particles in
+% abort gap and gives the information to start the abort gap cleaning process.
+
+\section{system architecture}
+basic methodology how to monitor this area is to exploit the synchrotron
+radiation light (SL). This phenomena appears when a particle is moving on a
+circular trajectory. The energy of the beam is proportional to the changes in
+the radiated spectrum. With increasing energy, the light is shifted towards
+shorter wavelengths. Since the LHC works with the energy from 
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
+    \caption{BSRA Chain}
+    \label{fig:bsra_chain}
+\end{figure}
+
 \subsection{Technical Solution}
@@
 
+        \begin{figure}[!tbh]
+            \centering
+            \includegraphics[width=\columnwidth]{bsra_daq.pdf}
+            \caption{upgraded amplifier}
+            \label{fig:amplifier}
+        \end{figure}
+
 \section{New fully digitized AGM}
-    \subsection{}
 
-\section{Comparison of Implementations}
-    %compare the changes and comment the expected changes
+        \begin{figure}[!tbh]
+            \centering
+            \includegraphics[width=\columnwidth]{amp_schematics.pdf}
+            \caption{upgraded amplifier}
+            \label{fig:amplifier}
+        \end{figure}
+
+% \section{Comparison of Implementations}
+%     \input{tables/system_comparison.tex} 
+%     %compare the changes and comment the expected changes
 
@@
 
-\section{Discussion}
-    \subsection{Significance of the Upgrade}
-    \subsection{Future Implications}
-    % \subsubsection{Potential for Further Enhancements or Modifications}
-    % \subsubsection{Integration with Other Accelerator Technologies}
+    \begin{figure}[!htb]
+      \begin{center}
+          \scalebox{0.54}{\input{plots/ions.pgf}}
+          \caption{Comparison of AGMs}
+          \label{fig:comparison_chart}
+      \end{center}
+    \end{figure}
+
+% \section{Discussion}
+%     \subsection{Significance of the Upgrade}
+%     \subsection{Future Implications}
+%     % \subsubsection{Potential for Further Enhancements or Modifications}
+%     % \subsubsection{Integration with Other Accelerator Technologies}
 
 \section{Conclusion}
-\section{Acknowledgments}
 

### 2024-04-04 paper.tex
added installation picture to the tex document
added names of sections and subsection with dummy text

@@
 
-\section{system architecture}
+\section{System architecture}
 basic methodology how to monitor this area is to exploit the synchrotron
@@
 shorter wavelengths. Since the LHC works with the energy from
+
+\subsection{Working principle}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 \begin{figure}[!tbh]
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-\subsection{Technical Solution}
+\subsection{Current Solution}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+
+\subsection{Constraints and Limitations}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+
+\section{System Upgrade}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 %Utilization of Analogue Integrator ASIC
@@
 
+\subsection{Acquisition System}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\section{}
 \begin{figure}[!tbh]
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-\section{New fully digitized AGM}
-
+\subsection{Low band Amplifier}
+% \input{tables/system_comparison.tex} 
+%compare the changes and comment the expected changes
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 \begin{figure}[!tbh]
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-% \section{Comparison of Implementations}
-%     \input{tables/system_comparison.tex} 
-%     %compare the changes and comment the expected changes
+\subsection{Installation in LHC}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=\columnwidth]{installation.jpg}
+    \caption{installation picture}
+    \label{fig:amplifier}
+\end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-\section{Recent Measurements}
+\section{Control Interface}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=\columnwidth]{control_interface.jpg}
+    \caption{installation picture}
+    \label{fig:amplifier}
+\end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
+\section{Measurements}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 \begin{figure}[!htb]
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-% \section{Discussion}
-%     \subsection{Significance of the Upgrade}
-%     \subsection{Future Implications}
-%     % \subsubsection{Potential for Further Enhancements or Modifications}
-%     % \subsubsection{Integration with Other Accelerator Technologies}
+\section{Discussion}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
 \section{Conclusion}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
-\input{acknowledgements}
-\input{appendix}
+% \input{acknowledgements}
+% \input{appendix}
 \input{bibliography}

### 2024-04-05 paper.tex
changed caption of the bsra daq picture
existing system picture added to paper

@@
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=\columnwidth]{existing_system_processing.pdf}
+    \caption{Current system block diagram}
+    \label{fig:current_system_processing}
+\end{figure}
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
@@
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-\section{}
 \begin{figure}[!tbh]
@@
     \includegraphics[width=\columnwidth]{bsra_daq.pdf}
-    \caption{upgraded amplifier}
-    \label{fig:amplifier}
+    \caption{Ackquisition system schematics}
+    \label{fig:bsra_daq}
 \end{figure}
@@
     \caption{upgraded amplifier}
-    \label{fig:amplifier}
+    \label{fig:amp_schematics}
 \end{figure}
@@
     \caption{installation picture}
-    \label{fig:amplifier}
+    \label{fig:installation}
 \end{figure}
@@
     \caption{installation picture}
-    \label{fig:amplifier}
+    \label{fig:control_interface}
 \end{figure}

### 2024-04-07 paper.tex
added introduction

@@
     This signal is then processed by an acquisition system and can trigger the
-    ‘abort gap cleaning’ process.\\
-    The current AGM, which has been in operation since 2010, uses an analogue
-    integrator ASIC and a 40 MHz analogue-to-digital (ADC) converter to provide
-    the particle population information. However, this solution is now
-    considered obsolete and is being replaced by a digital signal processing
-    approach. Working directly in the digital domain not only offers more
-    scalability but also better determinism and reliability. \\
-    This work presents the new technical solution for the acquisition chain,
-    compares the characteristics of both implementations, and showcases recent
-    measurements conducted on the LHC ion and proton beams.
+    ‘abort gap cleaning’ process. The current AGM, which has been in operation
+    since 2010, uses an analogue integrator ASIC and a 40 MHz
+    analogue-to-digital (ADC) converter to provide the particle population
+    information. However, this solution is now considered obsolete and is being
+    replaced by a digital signal processing approach. Working directly in the
+    digital domain not only offers more scalability but also better determinism
+    and reliability. This work presents the new technical solution for the
+    acquisition chain, compares the characteristics of both implementations,
+    and showcases recent measurements conducted on the LHC ion and proton
+    beams.
 \end{abstract}
@@
 \section{Introduction}
-The Large Hadron Collider (LHC) operates with high-energy beams that possess
-the capacity to melt metals and induce quenching in magnets, necessitating
-precise control measures to manage the beam when exiting vacuum compartments.
-The LHC beam consists of 2808 bunch slots, organized in bunch trains with a
-3~$\mu$s gap, determined by kicker magnet specifications for controlled
-beam expulsion from vacuum chambers.\\
-This paper addresses the imperative need for an electronics upgrade in the AGM
-system. The current AGM, operational since 2010, relies on an analogue
-integrator ASIC and a 40 MHz analogue-to-digital converter (ADC) for particle
-population measurements. Recognizing the obsolescence of this analogue
-solution, the paper introduces a transition to a digital signal processing
-approach. Working directly in the digital domain not only offers more
-scalability but also better determinism and reliability.\\
-The following sections delve into the current AGM system, its limitations, the
-rationale for the upgrade, the new technical solution, a comparative
-measurements.
-
-% lhc works with high energy beam which is strong enought to cause damage to
-% the machine beam bunch train has abort gap at the last bunch slots creating a
-% time gap of 3us this place should be empty because particles in this gap
-% don't get enough thrust to be directed towards the beam dumps and so they hit
-% hit the magnets controling the beam, which can cause quenching in the magnets
-% and losing the control over the beam. 
-% The Abort Gap monitor serves to continuously monitor amount of particles in
-% abort gap and gives the information to start the abort gap cleaning process.
+The maximum beam energy in~LHC at flat-top distributed in 2808 bunches can
+reach \SI{350}{MJ}, while having its average transverse size smaller than
+\SI{1}{mm}[LHCreport]. Such energy density can cause damage to the machine. 
+Inervention with conductive surface is enough to melt metallic surfaces and
+quenching a superconductiv magnet. The Beam dump system safely removes beam
+from the vacuum chamber. Its kicker magnets need \SI{3}{\micro\second} to ramp
+up their magnetic field and diverge particles towards beam dumps. The particles
+inside AG due to inperfections get insufficient kick and deflect towards the
+vacuum chamber. At certain energy accumulated in AG, the magnet can quench.
+Therefore continuous monitoring of the AG population is required. This is the
+purpose of the AGM~[abortgapmonitor].\\ 
+This paper reviews upgrade of the current AGM system installed in the LHC since
+2010. It describes first general system architecture and analog electronics
+chain of the current implementation. Discusses the temperature dependence,
+timing instabilities and compares the current and upgraded system.
 
 \section{System architecture}
-basic methodology how to monitor this area is to exploit the synchrotron
-radiation light (SL). This phenomena appears when a particle is moving on a
-circular trajectory. The energy of the beam is proportional to the changes in
-the radiated spectrum. With increasing energy, the light is shifted towards
-shorter wavelengths. Since the LHC works with the energy from
+Abort gap monitoring methodology is non-invasive, because it exploits
+synchrotron radiation light (SL). This phenomena appears, when a particle is
+losing it's energy on a circular trajectory. The energy is emitted in the form
+of light tangentially to the curved beam. The spectrum of the SL is
+proportional to the energy of the particles in the beam [REF]. At the flat-top
+energy (6.8TeV) the light is in visible range and can be measured by a
+photomultiplier (PMT), which converts light to electric current.
 
 \subsection{Working principle}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The~AGM uses the SR
+spontaneously emitted by the beam to quantify the fraction of particles present
+in the AG.
+
+System operational principle is depicted in the Fig.~\ref{fig:bsra_chain}.
+
+The signal is collected in the point 4, where it is measured by the PMT. The
+signal is converted and amplified depending on the voltage at the anode.
+
+The Emitted SL is collected by the PMT. It converts light to the electrict
+signal. This goes to through amplifier to the integrator, where it is decimated
+by factor 10. The system measure window is \SI{6.4}{\micro\second} long, which
+consist of 64 values after decimation process. Each of these values goes to the
+Exponential moving averager. This type of filter has a feedback remmembering
+all samples from system start.  
 \begin{figure}[!tbh]
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
@@
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
 \subsection{Constraints and Limitations}
+% This relies on an analogue
+% integrator ASIC and a 40 MHz analogue to digital converter (ADC) for particle
+% population measurements. Recognizing the obsolescence of this analogue
+% solution, the paper introduces a transition to a digital signal processing
+% approach. Working directly in the digital domain not only offers more
+% scalability but also better determinism and reliability.
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
@@
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 \begin{figure}[!tbh]
@@
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 
 \subsection{Installation in LHC}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
@@
 \end{figure}
+nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
 nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth

### 2024-04-21 plots/filters.py
this plot is meant for poster - it generates svg picture

@@ -45,4 +45,6 @@ ax.view_init(38, -148)
 # plt.show()
 
 # # NOTE USER HAVE TO PASS A PATH IN THE ARGUMENTS TO MAKE THE SCRIPT WORK
-plt.savefig(sys.argv[1])
+
+file_name = sys.argv[1].split('.')[0]
+plt.savefig(f"{file_name}.svg", transparent=True)

### 2024-04-21 plots/ions.py
changed point symbols in the agm picture

@@ -42,7 +42,7 @@ plt.xlim([0, 63])
 plt.grid(color=(0.7, 0.7, 0.7), linestyle='--', linewidth=0.6)
 
 ax2 = ax.twinx() 
-ax2.plot(agm_error, '-s', markersize=2, color=(0.961, 0.761, 0.067), linewidth=0.8)  
+ax2.plot(agm_error, '-o', markersize=5, color=(0.961, 0.761, 0.067), linewidth=0.8)  
 
 ax2.tick_params(axis='both', direction='in', labelcolor='k',
                labelsize='small', width=0.6, which='both',

### 2024-04-21 paper.tex
chapters filled with drafts

@@
 \section{Introduction}
+The LHC can store a maximum beam energy of up to 350 MJ across 2808 bunches
+during its flat-top phase, with an average transverse beam size under 1 mm
+(LHCreport). This high energy density poses a risk of machine damage, as
+conductive surface intervention can melt metallic surfaces and quench
+superconducting magnets. The Beam Dump system, utilizing kicker magnets with a
+3-microsecond ramp-up time to diverting particles, takes care of removing the beam
+from the vacuum chamber. It exploits a gap in the beam called abort gap (AG),
+to ramp up the magnets and divert the beam towards beam dumps.
+Imperfections in the accelerator may result in accumulation of particles inside
+AG. This results in insufficient kicks, causing particles to deflect
+towards the vacuum chamber and potentially leading to magnet quenching. This
+why the AG needs to be continuously monitored by the abort gap monitor (AGM).
+
+This paper reviews the upgrade of the current AGM system in the LHC since 2010,
+focusing on system architecture, analog electronics chain, temperature
+dependence, timing instabilities, and a comparison with the upgraded system.
+
 The maximum beam energy in~LHC at flat-top distributed in 2808 bunches can
@@
 \section{System architecture}
-Abort gap monitoring methodology is non-invasive, because it exploits
-synchrotron radiation light (SL). This phenomena appears, when a particle is
-losing it's energy on a circular trajectory. The energy is emitted in the form
-of light tangentially to the curved beam. The spectrum of the SL is
-proportional to the energy of the particles in the beam [REF]. At the flat-top
-energy (6.8TeV) the light is in visible range and can be measured by a
-photomultiplier (PMT), which converts light to electric current.
-
-\subsection{Working principle}
-The~AGM uses the SR
-spontaneously emitted by the beam to quantify the fraction of particles present
-in the AG.
-
-System operational principle is depicted in the Fig.~\ref{fig:bsra_chain}.
-
-The signal is collected in the point 4, where it is measured by the PMT. The
-signal is converted and amplified depending on the voltage at the anode.
-
-The Emitted SL is collected by the PMT. It converts light to the electrict
-signal. This goes to through amplifier to the integrator, where it is decimated
-by factor 10. The system measure window is \SI{6.4}{\micro\second} long, which
-consist of 64 values after decimation process. Each of these values goes to the
-Exponential moving averager. This type of filter has a feedback remmembering
-all samples from system start.  
+System is assambled from three major parts. First part is the optical font-end
+including preamplifier placed under the vacuum chamber. Second part is a
+gateware implemented on FPGA platform placed outside of the radiation area. The
+last part is the software reading out measured data and providing interface to
+interact with the gateware. The system architecture is depicted in
+Fig.~\ref{fig:bsra_chain}, where each part is enclosed in a frame with a
+number.
 \begin{figure}[!tbh]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+
+\subsection{Working principle}
+Abort gap monitoring is non-invasive beam measurement with high dynamic range.
+It exploits synchrotron radiation light (SL) present, when trajectory of a
+particle is bend due to magnetic forces. The particle loses it's energy in a
+form of light tangentally radiated to its trajectory. Any change in the light
+spectrum reflects the change in the beam [REF]. 
+The SL spectrum at the flat-top energy (6.8TeV) is in visible range, which
+is measured by a optical front-end. This consists of photomultiplier (PMT),
+converting SL to electric current, filters, and pre-amplifier to increase
+magnitude before sending the signal \SI{100}{m} far away data acquisition
+system (DAQ). The PMT is gate, that it opens just at the moment of abort gap.
+\\
+When SL is converted it is amplified and send to the DAQ. The system is
+synchronous with the RF timing, that it gets information about bunch position
+and turn start. The signal goes to through amplifier to the integrator, where
+it is decimated by factor 10. The system is gated. Its measure window is
+\SI{6.4}{\micro\second} long, but the gate opens just for the time of the abort
+gap. The decimate the data to \SI{100}{ns} sample period. In other words system
+measures 64 values, but just 30 have valid value. Each of these values goes to
+the Exponential moving averager. This type of filter has a feedback, so the
+its output reflects the evolution of the charge in the abort gap.
 
 \subsection{Current Solution}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The System is placed at the point 4 sharing the optical line with the BSRT
+[REF]. It converts incoming light through MCP-PMT HAMAMATSU R5916U-50 into
+electric current. The current is converted to voltage by transimpedance
+amplifier HAMAMATSU C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz}
+and the low cutoff frequency 50kHz.
+The amplified signal is send to the switching analog integrators inside ASIC
+lhcb2002b mounted to the IBMS FMC card. The card is connected to the DAB64x
+deploying FPGA Altera Stratix EP1S400. 
 \begin{figure}[!tbh]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The current system schematic is in Fig.~\ref{fig:current_system_processing}. It
+uses preintegration in the analog integrators behind the pre-amplifier. One
+outputs a value while the other one is measuring every \SI{25}{ns}. Inside the
+gateware the samples are summed to get 100ns integrals. Each analog integrator
+has different gain, offset and is not temperature invariant. Therefore
+different coefficients are applied at this stage as well. 
+The system provides the two sets of data. It measures the evolution of average
+and standard deviation. The 2 x 64 values are stored in the Block RAM and
+fetched by the PC with running FESA server.
 
 \subsection{Constraints and Limitations}
-% This relies on an analogue
-% integrator ASIC and a 40 MHz analogue to digital converter (ADC) for particle
-% population measurements. Recognizing the obsolescence of this analogue
-% solution, the paper introduces a transition to a digital signal processing
-% approach. Working directly in the digital domain not only offers more
-% scalability but also better determinism and reliability.
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The system bottle neck is the analog integration. There is one installation per
+beam each having IBMS with different gain, offset, correction coefficients and
+40 MHz ADCs. When the IBMS is replaced, it needs to be recalibrated. The ASIC
+has not deterministic time stamps, so dead-times lengths do not match. This is
+causing artefacts at the opening and closing of the gate in the output plot.
+The dynamic range can be controled by the optical filters not via amplifier,
+because of static gain. Finally the DAB64x is obsolate platform, which
+complicates its maintenance.
 
 \section{System Upgrade}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-%Utilization of Analogue Integrator ASIC
-%40 MHz Analogue-to-Digital Converter (ADC)
-%Operation Since 2010
-%Reasons for Obsolescence
-%Digital Signal Processing Approach why and outcomes
+The motivation to create a new Abort Gap Monitor is initiated by the problems
+associated with the analog integrators in lhcb2002b. These cause measurements
+errors and make the AGM difficult to calibrate[REF]. And the second driver to
+redesign the system was the platform obsolance reducing simplicity of
+maintenance. \\ 
+As a platform the new VFC-HD Carrier is used with additional RTM board
+providing driver for the gate and control of the built-in test LED. The last
+major change was of the shelf 500MSPS 14-bit ADC reducing the maintanence
+efford.
 
-\subsection{Acquisition System}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\subsection{Low band Amplifier}
+The amplifier installed close to the MCP-PMT was custom designed. The purpose
+is different light intensity of ion and proton beams to obtain higher dynamic
+range. \\ 
+% A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
+In the Fig. \ref{fig:amp_schematics} is shown amplifier's block scheme. All the
+settings is controlled via UART interface. It provides changing the variable
+current-to-voltage conversion factor from \SI{5.8}{mV/\micro A} -
+\SI{1.1}{V/\micro A}. This corresponds to the Voltage gain from \SI{41}{dB} to
+\SI{87}{dB}. The ADC has a no zero offset, so the signal can be shifted in the
+amplifier before post-processing.\\
+The amplifier features also alarm signal generator. This serves to turn of the
+gate, when the light impinging is to intense and it could damage the
+multi-channel plate inside the PMT. The alarm signal is send to the gateware,
+where it is handled. The alarm feature has a variable threshold set.   
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
+    \caption{upgraded amplifier}
+    \label{fig:amp_schematics}
+\end{figure}
+The amplifier design has three switches. First switch can set pre-integrator,
+to filter out spikes caused by dark counts of the PMT. Second switch can
+activate either manual or gate driven integration of the acquisition window.  
+Last switch activates low pass filtering with cutoff frequency of 40MHz.
+
+\subsection{Acquisition system}
+The DAQ was completly redesigned, because of the new platform and additional HW
+components. The Fig. \ref{fig:bsra_daq} shows, how the signal is processed an
+published from the DAQ.
 \begin{figure}[!tbh]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-
-\subsection{Low band Amplifier}
-% \input{tables/system_comparison.tex} 
-%compare the changes and comment the expected changes
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-\begin{figure}[!tbh]
-    \centering
-    \includegraphics[width=\columnwidth]{amp_schematics.pdf}
-    \caption{upgraded amplifier}
-    \label{fig:amp_schematics}
-\end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The ADC takes amplified data from MCP-PMT and samples them with 500MSPS
+asynchronously to the LHC timing. To calculate the integrals, the system tags
+each of the sample. This is done, that tagging block resamples LHC timing by
+500MSPS and creates bunch and turn clock vector masks. Those store the
+information about both clocks rising edge phase. The 14-bit data from ADC are
+left aligned to 16-bit values. The tagger sets their two LSBs to one, when the
+ADC sample falls into the edge range. \\
+The ADC provides four frames of four 16-bit samples every \SI{8}{\nano s} each
+belonging to one ADC channel. The tag can appear in any of the four values. The
+system stores data from region of interest, using FIFO. The synchronizer counts
+4 turns and then generates a trigger for FIFO. Stored data are then processed as
+a stream of values passed to the integrator. This starts summing up values,
+when it hits the tag in the data marking the start of the bunch. It creates 64
+values offseted by the user when needed. This correct the baseline. The values
+are then sent to the exponential moving averager. The result is then stored in
+the block ram available on to read from VME64x bus.
 
 \subsection{Installation in LHC}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The instrument front and Acquistion system is located in Point 4 near RF
+system. The new installation is shown in Fig. \ref{fig:installation}
+highlighted with violet frame. On its right side is the currently working AGM
+and on the left side is the BSRS. All the instruments share the same light
+source with the BSRT. 
 \begin{figure}[!tbh]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The beam input is demonstrated by the yellow line. It shows beam arriving to
+the MCP-PMT. On top of the reflective foil directing light towards the MCP-PMT
+is a LED simulating the light source. This helps verifying the system
+operation. The AGM amplifier is placed on top of the optical front-end to be
+reachable in case of intervention. For reducing the light intensity, there are
+pneumatically controlled optical filters in front of the PMT.
 
 \section{Control Interface}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The gateware outputs data from four different block rams. The first stores raw
+data from the ADC, that is used correctly set the initial delay of the
+instrument's timing. It stores 1.5 turns and therefore it is published with
+\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
+data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
+which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
+averaged data taken every \SI{10}{ms} defining the publishing rate. The
+fetching handles the FESA server, which obtains interrupt every time the data
+are ready. 
 \begin{figure}[!tbh]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+To simplify the setup tunining a new interface had to be created. It runs as
+client of FESA server and displays the content of all the block rams. The main
+control panel is depicted in Fig. \ref{fig:control_interface}. It displays
+three plots, raw data from the ADC (top plot), processed averaged data (down
+plot on the left) and and evolution of the data in time (down plot on the
+right). The menu on the left controls the amplifier and bottom menu controls
+the acquisition delays and optical filters.
 
-\section{Measurements}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\section{First acquired plots}
+First measurements were taken in November 2023 on the ion beam. The
+optical system splits the SL in ratio 1:8, so the new system gets
+significantly less light then current one. In other word, we expect
+lower value deviation for system measuring light with higher intensity.  
 \begin{figure}[!htb]
@@
 \end{figure}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+The Fig. \ref{fig:comparison_chart} shows first acquisition of the new system
+in comparison with the current one. The red plot is measured by the current
+system and the blue chart is the new acquisition. In a range from 47th - 63th
+bin, the gate is already close. There is just white noise, but the red plot
+slowly decays and it continues below the zero line. This artefact is caused by
+analog integrators and it is non-linear. The new system removes this effect.
+The value deviation of the new acqusition from the current system represents
+the yellow plot.   The relative value deviation of the new system from the
+current one is depicted with the yellow plot. In this measurement the maximum
+deviation is 4\% in the area of the decay of the red plot. The the deviation of
+2\% in the steep parts can be caused by the sample phase alignment of the two
+systems.
 
-\section{Discussion}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
+\section{Summary}
+The AGM has been implemented on the VFC-HD carrier board simplifying
+maintenance. The implementation is based on the direct digital conversion,
+which eliminates artefacts in the output plot from the current system using
+IBMS cards embedding analog integrators. It also solves the calibration hassle. 
+The comparison of the two systems is summarized in the following table Tab.
+\ref{tab:system_comparison}.
+\input{tables/system_comparison.tex} 
+The system is installed in the point 4 next to the current AGM collecting data
+to be further analyzed. For the complet reliability test and proper function
+verification, it needs to be collected more data and they have to be compared
+with the current system. The systems shows so far, that with less light, it can
+have still similar results to the current AGM.
 
-\section{Conclusion}
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-nteaohutnha tnaheusnthae nsatheusnha thoaeut hh antuhentae u tahuenth tahuenth
-
-% \input{acknowledgements}
-% \input{appendix}
 \input{bibliography}
 
-%%%\include{annexes-A4}
-
 \end{document}

### 2024-04-21 paper.tex
rephrased introduction

@@
 \section{Introduction}
-The LHC can store a maximum beam energy of up to 350 MJ across 2808 bunches
-during its flat-top phase, with an average transverse beam size under 1 mm
-(LHCreport). This high energy density poses a risk of machine damage, as
-conductive surface intervention can melt metallic surfaces and quench
-superconducting magnets. The Beam Dump system, utilizing kicker magnets with a
-3-microsecond ramp-up time to diverting particles, takes care of removing the beam
-from the vacuum chamber. It exploits a gap in the beam called abort gap (AG),
-to ramp up the magnets and divert the beam towards beam dumps.
-Imperfections in the accelerator may result in accumulation of particles inside
-AG. This results in insufficient kicks, causing particles to deflect
-towards the vacuum chamber and potentially leading to magnet quenching. This
-why the AG needs to be continuously monitored by the abort gap monitor (AGM).
-
+During the flat-top phase, the LHC ring stores up to 350 MJ of beam energy,
+spread across 2808 bunches with an average beam transverse size under
+\SI{1}{mm}. This high energy density can melt metallic surfaces and quench
+superconducting magnets, posing a risk to the machine~\cite{LHC_report}. 
+To safely extract the beam from the vacuum compartments, a series of kicker
+magnets belonging to the beam dump system is used. These magnets take 3 us to
+ramp up their magnetic field~\cite{beam_dump_system}. This defines the size of
+an abort gap (AG) in the bunch train. Due to system imperfections, particles
+populate this gap. Average AG population is in order of $10^{9}$ particles. The
+population in a single bunch is four orders of magnitude higher in comparison.
+When the beam dump is initiated, the particles in AG do not receive full
+extraction force. That causes deflection towards the vacuum chamber. When a
+certain energy accumulates in the AG, the magnet can quench. Therefore,
+continuous monitoring of the AG population is necessary, which is the purpose
+of the AGM~\cite{particles_in_ag}.\\
 This paper reviews the upgrade of the current AGM system in the LHC since 2010,
@@
 dependence, timing instabilities, and a comparison with the upgraded system.
-
-The maximum beam energy in~LHC at flat-top distributed in 2808 bunches can
-reach \SI{350}{MJ}, while having its average transverse size smaller than
-\SI{1}{mm}[LHCreport]. Such energy density can cause damage to the machine. 
-Inervention with conductive surface is enough to melt metallic surfaces and
-quenching a superconductiv magnet. The Beam dump system safely removes beam
-from the vacuum chamber. Its kicker magnets need \SI{3}{\micro\second} to ramp
-up their magnetic field and diverge particles towards beam dumps. The particles
-inside AG due to inperfections get insufficient kick and deflect towards the
-vacuum chamber. At certain energy accumulated in AG, the magnet can quench.
-Therefore continuous monitoring of the AG population is required. This is the
-purpose of the AGM~[abortgapmonitor].\\ 
-This paper reviews upgrade of the current AGM system installed in the LHC since
-2010. It describes first general system architecture and analog electronics
-chain of the current implementation. Discusses the temperature dependence,
-timing instabilities and compares the current and upgraded system.
 

### 2024-04-21 bibliography.tex
added abort gap monitor acquisition system thesis to bibliography
added linke to one of the bsra status presentation
rephrased introduction
edited system architecture chapture

@@
 
+        \bibitem{beam_dump_system} Filippini, R., Carlier, E., Ducimetière, L., Goddard,
+            B. \& Uythoven, J. \emph{Reliability Analysis of the LHC Beam Dumping System}.
+            (2005,6), \url{https://cds.cern.ch/record/841092}
+
+        \bibitem{particles_in_ag}Meddahi, M., Bart Pedersen, S., Boccardi, A.,
+            Butterworth, A., Fisher, A., Gianfelice-Wendt, E., Goddard, B., Hemelsoet,
+            G., Höfle, W., Jacquet, D., Jaussi, M., Kain, V., Lefevre, T., Shaposhnikova,
+            E., Uythoven, J. \& Valuch, D. LHC Abort Gap Monitoring and Cleaning.
+            (2010,6), \url{https://cds.cern.ch/record/1277630}
+
         \bibitem{abort_gap_monitor}De Santis, S., Beche, J., Byrd, J., Placidi, M.,
@@
             Large Hadron Collider}.  (2004), \url{https://cds.cern.ch/record/823343}
+
+        \bibitem{ttc_distribution} Taylor, B. \emph{TTC distribution for LHC detectors}.
+            {\em IEEE Trans. Nucl. Sci.}. \textbf{45} pp. 821-828 (1998),
+            \url{https://cds.cern.ch/record/363087}
 
@@
 
-        \bibitem{bsra_calib} A. Boccardi et a1., \emph{Calibration procedures and
-            automated actions for the Abort Gap Monitors of LHC}, (2015, 3), LHC-B SRA-
-            ES-OOOl, \url{https:edms.cern.ch/document/1337184/1}
-
         \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
@@
             (CERN,2010), \url{https://cds.cern.ch/record/1261191}
-
-        \bibitem{particles_in_ag}Meddahi, M., Bart Pedersen, S., Boccardi, A.,
-            Butterworth, A., Fisher, A., Gianfelice-Wendt, E., Goddard, B., Hemelsoet,
-            G., Höfle, W., Jacquet, D., Jaussi, M., Kain, V., Lefevre, T., Shaposhnikova,
-            E., Uythoven, J. \& Valuch, D. LHC Abort Gap Monitoring and Cleaning.
-            (2010,6), \url{https://cds.cern.ch/record/1277630}
 
@@
 
+        \bibitem{abort_gap_monitor_thesis}Pacner, P. LHC Abort Gap Monitor
+            Acquisition System, Master thesis, (Brno, 2022, 59)
+
 % other sources
 % https://indico.cern.ch/event/359810/contributions/853246/attachments/716754/983942/BSRA_BI_TB_Feb2015.pdf
+% https://edms.cern.ch/document/2794287/1
+%
 

### 2024-04-21 paper.tex
edited system architecture chapture

@@
 \section{Introduction}
-During the flat-top phase, the LHC ring stores up to 350 MJ of beam energy,
+During the flat-top phase, the LHC ring stores up to \SI{350}{MJ} of beam energy,
 spread across 2808 bunches with an average beam transverse size under
@@
 \section{System architecture}
-System is assambled from three major parts. First part is the optical font-end
-including preamplifier placed under the vacuum chamber. Second part is a
-gateware implemented on FPGA platform placed outside of the radiation area. The
-last part is the software reading out measured data and providing interface to
-interact with the gateware. The system architecture is depicted in
-Fig.~\ref{fig:bsra_chain}, where each part is enclosed in a frame with a
-number.
+The system comprises three main parts. The first part is the optical front-end
+(OF), which includes a preamplifier positioned beneath the vacuum chamber. The
+second part is a data acquisition system (DAQ) deployed on an FPGA platform
+located outside the radiation area. The third part involves software (SW) that
+retrieves, interprets, and presents the measured data, facilitating interaction
+with the instrument. The system architecture is illustrated in
+Fig.~\ref{fig:bsra_chain}, with each part labeled accordingly.
 \begin{figure}[!tbh]
@@
 \end{figure} 
+The diagram on the left depicts the layout of the LHC, with beam 1 represented
+in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
+LHCb, and CMS). The AGM is situated at Point 4 (indicated by the yellow
+square), close to the CMS experiment. The Timing, Trigger, and Control system
+(TTC) is shown as a purple rectangle in the center of the LHC ring. This system
+receives RF clocking and broadcasts it as messages on the network (TTC
+distribution)~\cite{ttc_distribution}. The AGM extracts bunch clock information
+(corresponding to the position of bunches) and turn clock information (marking
+the start of a turn) from these messages.\\
+Beam intensity is gathered by measuring the synchrotron light (SL), as
+indicated by the red arrow directed towards the Multi-channel photomultiplier
+(MCP-PMT). The light reaches the MCP-PMT in the optical front-end (OF).
+Subsequently, the signal is transmitted over a \SI{100}{m} cable. To compensate
+for losses in the cable, the signal is amplified beforehand. It then proceeds
+to the Data Acquisition (DAQ) system, which measures \SI{6.4}{\micro\second}
+window and integrates the intervals of \SI{100}{\nano\second}. This creates set
+of 64 values published to the SW every \SI{10}{\micro\second}.
 
 \subsection{Working principle}
-Abort gap monitoring is non-invasive beam measurement with high dynamic range.
-It exploits synchrotron radiation light (SL) present, when trajectory of a
-particle is bend due to magnetic forces. The particle loses it's energy in a
-form of light tangentally radiated to its trajectory. Any change in the light
-spectrum reflects the change in the beam [REF]. 
-The SL spectrum at the flat-top energy (6.8TeV) is in visible range, which
-is measured by a optical front-end. This consists of photomultiplier (PMT),
+The SL spectrum at the flat-top energy \SI{6.8}{TeV} is in visible band, which
+is measured by a optical front-end. This consists of MCP-PMT,
 converting SL to electric current, filters, and pre-amplifier to increase

### 2024-04-22 paper.tex
added new bibtexs and working principle finished

@@
 \subsection{Working principle}
-The SL spectrum at the flat-top energy \SI{6.8}{TeV} is in visible band, which
-is measured by a optical front-end. This consists of MCP-PMT,
-converting SL to electric current, filters, and pre-amplifier to increase
-magnitude before sending the signal \SI{100}{m} far away data acquisition
-system (DAQ). The PMT is gate, that it opens just at the moment of abort gap. 
-\\
-When SL is converted it is amplified and send to the DAQ. The system is
-synchronous with the RF timing, that it gets information about bunch position
-and turn start. The signal goes to through amplifier to the integrator, where
-it is decimated by factor 10. The system is gated. Its measure window is
-\SI{6.4}{\micro\second} long, but the gate opens just for the time of the abort
-gap. The decimate the data to \SI{100}{ns} sample period. In other words system
-measures 64 values, but just 30 have valid value. Each of these values goes to
-the Exponential moving averager. This type of filter has a feedback, so the
-its output reflects the evolution of the charge in the abort gap.
+
+The measurement period is determined by the MCP-PMT used, which is the gated
+HAMAMATSU R5916U-50 with a duty cycle of \SI{1}{\%}. With a gate pulse duration
+of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
+measurements are taken every 4th clock cycle (\SI{356}{\micro\second}),
+reducing the duty cycle to \SI{0.84}{\%}.\\
+The system captures 64 values with a granularity of \SI{100}{\nano\second}. The
+MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
+freedom in system control. The data undergo exponential moving
+averaging and are provided to the software every \SI{100}{\micro\second}. Due to
+variatous particle effects, the time taken to populate the AG ranges from
+\SI{1.6}{\second} to \SI{25}{\second}~\cite{high_sensitivity_measurement}.
 

### 2024-04-24 bibliography.tex
added new bibtexs and working principle finished
updated old system und new system daq chapters

@@
 
-        % https://cds.cern.ch/record/1272172/files/CERN-BE-2010-026.pdf
-        \bibitem{bsra_operation}Bart Pedersen, S., Lefevre, T., Bravin, E., Boccardi, A.,
+        \bibitem{high_sensitivity_measurement} C. Fischer, \emph{High Sensitivity
+            Measurement of the Beam Longitudinal Distribution of the LHC Beams}, 
+            (2003,1), LHC-BP-ES-0005, rev. 2.0,
+            \url{https://edms.cern.ch/document/328145/2.0}
+
+        \bibitem{bsra_first_operation}Bart Pedersen, S., Lefevre, T., Bravin, E., Boccardi, A.,
           Goldblatt, A., Jeff, A., Roncarolo, F. \& Fisher, A. \emph{First Operation of
@@
 
-        \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
-            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
-            (CERN,2010), \url{https://cds.cern.ch/record/1261191}
+        \bibitem{lhcb_asic} Böhner, G., Falvard, A., Lecoq, J., Perret, P. \& Trouilleau,
+            C. \emph{Very front-end electronics for the LHCb preshower}.  (CERN,2000,10),
+            \url{http://cds.cern.ch/record/691512}
 
-        % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
-        \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
-            instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}
+        \bibitem{my_thesis}Pacner, P. LHC Abort Gap Monitor
+            Acquisition System, Master thesis, (Brno, 2022, 59)
 
-        % https://cds.cern.ch/record/1261191/files/performance-note-014.pdf
-        \bibitem{expected_performance_bsrt}Fisher, A. Expected Performance of the LHC
-            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).
-            (CERN, 2010, 3), \url{https://cds.cern.ch/record/1261191}
+        % \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
+        %     Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
+        %     (CERN,2010), \url{https://cds.cern.ch/record/1261191}
 
-        \bibitem{abort_gap_monitor_thesis}Pacner, P. LHC Abort Gap Monitor
-            Acquisition System, Master thesis, (Brno, 2022, 59)
+        % % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
+        % \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
+        %     instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}
 

### 2024-04-24 paper.tex
updated old system und new system daq chapters

@@
 Beam intensity is gathered by measuring the synchrotron light (SL), as
-indicated by the red arrow directed towards the Multi-channel photomultiplier
-(MCP-PMT). The light reaches the MCP-PMT in the optical front-end (OF).
-Subsequently, the signal is transmitted over a \SI{100}{m} cable. To compensate
-for losses in the cable, the signal is amplified beforehand. It then proceeds
-to the Data Acquisition (DAQ) system, which measures \SI{6.4}{\micro\second}
-window and integrates the intervals of \SI{100}{\nano\second}. This creates set
-of 64 values published to the SW every \SI{10}{\micro\second}.
+indicated by the red line directed towards the Multi-channel photomultiplier
+(MCP-PMT) in the optical front-end (OF). The beam travers first optical
+filters, which increase system dynamic range. Subsequently, the signal is
+transmitted over a \SI{100}{m} cable. To compensate for losses in the cable,
+the signal is amplified beforehand. It then proceeds to the Data Acquisition
+(DAQ) system, which measures \SI{6.4}{\micro\second} window and integrates the
+intervals of \SI{100}{\nano\second}. This creates set of 64 values published to
+the SW every \SI{10}{\micro\second}.
 
 \subsection{Working principle}
-
 The measurement period is determined by the MCP-PMT used, which is the gated
@@
 MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
-freedom in system control. The data undergo exponential moving
-averaging and are provided to the software every \SI{100}{\micro\second}. Due to
-variatous particle effects, the time taken to populate the AG ranges from
-\SI{1.6}{\second} to \SI{25}{\second}~\cite{high_sensitivity_measurement}.
+freedom in system control. Each \SI{100}{\nano\second} value is averaged in an
+extra EMA and provided to the software every \SI{100}{\micro\second}. This
+time is enough to react to changes in AG. The population can change from
+\SI{1.6}{\second} to \SI{25}{\second} due to different
+effects~\cite{high_sensitivity_measurement}.
 
 \subsection{Current Solution}
-The System is placed at the point 4 sharing the optical line with the BSRT
-[REF]. It converts incoming light through MCP-PMT HAMAMATSU R5916U-50 into
-electric current. The current is converted to voltage by transimpedance
-amplifier HAMAMATSU C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz}
-and the low cutoff frequency 50kHz.
-The amplified signal is send to the switching analog integrators inside ASIC
-lhcb2002b mounted to the IBMS FMC card. The card is connected to the DAB64x
-deploying FPGA Altera Stratix EP1S400. 
+The current solution uses DAB64x card deploying FPGA Altera Stratix EP1S40. The
+platform has two FMC connectors. There are mounted two IBMS module. Those
+modules integrate voltage on input using ASIC lhcb2002b~\cite{lhcb_asic}.
+To get the maximal resolution of the ADC, the signal is amplified by HAMAMATSU
+C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz} and the low cutoff
+frequency 50kHz.
 \begin{figure}[!tbh]
@@
 \end{figure}
-The current system schematic is in Fig.~\ref{fig:current_system_processing}. It
-uses preintegration in the analog integrators behind the pre-amplifier. One
-outputs a value while the other one is measuring every \SI{25}{ns}. Inside the
-gateware the samples are summed to get 100ns integrals. Each analog integrator
-has different gain, offset and is not temperature invariant. Therefore
-different coefficients are applied at this stage as well. 
-The system provides the two sets of data. It measures the evolution of average
-and standard deviation. The 2 x 64 values are stored in the Block RAM and
-fetched by the PC with running FESA server.
+The system schematic is in Fig.~\ref{fig:current_system_processing}. The OF is
+the same as described in the system architecture chapter. The picture omits the
+filters, because they are used in all cases. The MCP-PMT signal needs to be
+amplified by at least 34dB to use the full scale of the 40Mhz ADC. The
+Hamamatsu C559 is used~\cite{bsra_first_operation}. The signal belonging
+to one bunch (\SI{25}{ns}) is integrated in the IBMS (blue triangle with a
+capacitor in the feedback) sampled by ADC (violet rectangle in the figure). The
+DAQ integrates 4 samples (light blue rectangle with $\sum$ symbol) to calculate
+charge in \SI{100}{ns} interval. It produces 64 values, from which are created
+two sets of 64 values with the standard deviation and the mean value is
+calculated. Both sets are passed to the EMA block (green rectangle in
+the figure). All data are saved in the block ram. This is is than shared with
+the PC over wishbone to VME64 bridge. The PC runs server which provides the
+FESA interface to the connected clients.
 
 \subsection{Constraints and Limitations}
-The system bottle neck is the analog integration. There is one installation per
-beam each having IBMS with different gain, offset, correction coefficients and
-40 MHz ADCs. When the IBMS is replaced, it needs to be recalibrated. The ASIC
-has not deterministic time stamps, so dead-times lengths do not match. This is
-causing artefacts at the opening and closing of the gate in the output plot.
-The dynamic range can be controled by the optical filters not via amplifier,
-because of static gain. Finally the DAB64x is obsolate platform, which
-complicates its maintenance.
+The current AGM returns artefacts in the measurements. The signal, which lays
+outside of the gate is not reflecting behaviour of white noise. This is caused
+by the lhcb2002b ASIC. The integrators gain is not linear, have different
+offset and dead times. This means, that system needs to correct at each
+integrator these effects, which creates uncertainties in the results. This
+results in complicated calibration procedur.\\
+The system uses old FPGA platform for which development sofware tools are not
+compatible with newest operation systems. The amplifier is not variable, which
+results in lower resolution for smaller magnitudes.
 
 \section{System Upgrade}
-The motivation to create a new Abort Gap Monitor is initiated by the problems
-associated with the analog integrators in lhcb2002b. These cause measurements
-errors and make the AGM difficult to calibrate[REF]. And the second driver to
-redesign the system was the platform obsolance reducing simplicity of
-maintenance. \\ 
-As a platform the new VFC-HD Carrier is used with additional RTM board
-providing driver for the gate and control of the built-in test LED. The last
-major change was of the shelf 500MSPS 14-bit ADC reducing the maintanence
-efford.
+To resolve the issue of the maintenance, the VFC-HD carrier is used with
+additional RTM board providing driver for the gate and control of the built-in
+test LED. The same carrier board with 500MSPS 14-bit ADC has been used in other
+projects and so it provided the requirement for reducing the maintenance efford.
+The new system removes IBMS cards with lhcb2002b integrators and moving the
+whole integration process to the gateware.
 
 \subsection{Low band Amplifier}
-The amplifier installed close to the MCP-PMT was custom designed. The purpose
-is different light intensity of ion and proton beams to obtain higher dynamic
-range. \\ 
+The new custom amplififer is designed to allow work with higher signal dynamic
+range, because of its variability.  
 % A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
@@
 \SI{1.1}{V/\micro A}. This corresponds to the Voltage gain from \SI{41}{dB} to
-\SI{87}{dB}. The ADC has a no zero offset, so the signal can be shifted in the
+\SI{87}{dB}. The AGM ADC has a no zero offset, so the signal can be shifted in the
 amplifier before post-processing.\\
@@
     \includegraphics[width=\columnwidth]{amp_schematics.pdf}
-    \caption{upgraded amplifier}
+    \caption{New AGM custom amplifier}
     \label{fig:amp_schematics}
@@
 \subsection{Acquisition system}
-The DAQ was completly redesigned, because of the new platform and additional HW
-components. The Fig. \ref{fig:bsra_daq} shows, how the signal is processed an
-published from the DAQ.
+The DAQ had to be redesigned to be compatible with the new VFC-HD carrier. It
+needed Rear transition module (RTM) to control the gate and built-in test LED.  
+The Fig.~\ref{fig:bsra_daq} is depicted DAQ functionality principle. 
 \begin{figure}[!tbh]
@@
 \end{figure}
-The ADC takes amplified data from MCP-PMT and samples them with 500MSPS
-asynchronously to the LHC timing. To calculate the integrals, the system tags
-each of the sample. This is done, that tagging block resamples LHC timing by
-500MSPS and creates bunch and turn clock vector masks. Those store the
-information about both clocks rising edge phase. The 14-bit data from ADC are
+The new DAQ gets asynchronous data samples from ADC 500MSPS 14-bit (violet
+rectangle) in the block of 4 frames every \SI{8}{\nano s} belonging to one
+channel. Each frame has 4 x \SI{16}{bit} values. To calculate the integrals of
+\SI{100}{\nano\second}, the system tags the data. The tagging block resamples
+LHC timing by 500MSPS and creates bunch and turn clock vector masks. Those
+store the information about both clocks phases. The 14-bit data from ADC are
 left aligned to 16-bit values. The tagger sets their two LSBs to one, when the
-ADC sample falls into the edge range. \\
-The ADC provides four frames of four 16-bit samples every \SI{8}{\nano s} each
-belonging to one ADC channel. The tag can appear in any of the four values. The
-system stores data from region of interest, using FIFO. The synchronizer counts
-4 turns and then generates a trigger for FIFO. Stored data are then processed as
-a stream of values passed to the integrator. This starts summing up values,
-when it hits the tag in the data marking the start of the bunch. It creates 64
-values offseted by the user when needed. This correct the baseline. The values
-are then sent to the exponential moving averager. The result is then stored in
-the block ram available on to read from VME64x bus.
+ADC sample falls into the edge range. The system stores data from region of
+interest, into the FIFO using the synchronization block pulse. Stored data are
+then processed as a stream of values passed to the integrator. This starts
+summing up values, when it hits the tag in the data indicating the start of the
+bunch. It creates 64 values offseted from the pedestal memory (P[63:0]). This
+subtracts accumulated charge at the gate opening and closing edge. The values
+are then sent to the EMA and the result stored in the block ram available on
+the VME64x bus. The format of the data provided to the PC with runnig FESA
+server is the same with the current AGM~\cite{my_thesis}.
 
 \subsection{Installation in LHC}
-The instrument front and Acquistion system is located in Point 4 near RF
-system. The new installation is shown in Fig. \ref{fig:installation}
-highlighted with violet frame. On its right side is the currently working AGM
+The instrument front and Acquistion system is located in LHC Point 4 near RF
+system. The new installation is shown in Fig.~\ref{fig:installation}
+highlighted with violet frame. On its right side is the currently used AGM
 and on the left side is the BSRS. All the instruments share the same light
-source with the BSRT. 
+source with the BSRT. The instrument is pulled out from the shielding and the
+red arrow ilustrates, where the light comes from and goes in to the MCP-PMT of
+the new AGM.
 \begin{figure}[!tbh]
@@
     \includegraphics[width=\columnwidth]{installation.jpg}
-    \caption{installation picture}
+    \caption{New AGM installed in Point 4 next to BSRT}
     \label{fig:installation}
 \end{figure}
-The beam input is demonstrated by the yellow line. It shows beam arriving to
-the MCP-PMT. On top of the reflective foil directing light towards the MCP-PMT
+On top of the reflective foil directing light towards the MCP-PMT
 is a LED simulating the light source. This helps verifying the system
@@
 reachable in case of intervention. For reducing the light intensity, there are
-pneumatically controlled optical filters in front of the PMT.
+pneumatically controlled optical filters in front of the MCP-PMT.
 
@@
     \includegraphics[width=\columnwidth]{control_interface.jpg}
-    \caption{installation picture}
+    \caption{New AGM expert graphical interface}
     \label{fig:control_interface}
@@
         \scalebox{0.54}{\input{plots/ions.pgf}}
-        \caption{Comparison of AGMs}
+        \caption{Features comparison of AGMs}
         \label{fig:comparison_chart}

### 2024-04-25 paper.tex
edited summary

@@
 client of FESA server and displays the content of all the block rams. The main
-control panel is depicted in Fig. \ref{fig:control_interface}. It displays
+control panel is depicted in Fig.~\ref{fig:control_interface}. It displays
 three plots, raw data from the ADC (top plot), processed averaged data (down
@@
 \section{Summary}
-The AGM has been implemented on the VFC-HD carrier board simplifying
-maintenance. The implementation is based on the direct digital conversion,
-which eliminates artefacts in the output plot from the current system using
-IBMS cards embedding analog integrators. It also solves the calibration hassle. 
-The comparison of the two systems is summarized in the following table Tab.
+The new AGM has been implemented on the CERN BI standard platform VFC-HD
+carrier simplifying maintenance. The design removed the IBMS cads with ASIC
+lhcb2002b and so resolved the issue with cumbersome calibration and artefacts
+in the output plots.  It also The changes in the AGM design compared to the
+current AGM are summarized in the following table Tab.
 \ref{tab:system_comparison}.
 \input{tables/system_comparison.tex} 
-The system is installed in the point 4 next to the current AGM collecting data
+The system is installed in LHC the point 4 next to the current AGM collecting data
 to be further analyzed. For the complet reliability test and proper function
-verification, it needs to be collected more data and they have to be compared
-with the current system. The systems shows so far, that with less light, it can
-have still similar results to the current AGM.
+verification, it needs to be collected more data, that will help evalate system
+goodness. The systems shows so far, that with less light, it can have still
+comparable outputs to the current AGM.
 

### 2024-04-25 paper.tex
rephrased some chapters

@@
 \subsection{Current Solution}
-The current solution uses DAB64x card deploying FPGA Altera Stratix EP1S40. The
-platform has two FMC connectors. There are mounted two IBMS module. Those
-modules integrate voltage on input using ASIC lhcb2002b~\cite{lhcb_asic}.
-To get the maximal resolution of the ADC, the signal is amplified by HAMAMATSU
-C5594 with static gain \SI{36}{dBV}, bandwith \SI{1.5}{GHz} and the low cutoff
-frequency 50kHz.
+The current setup employs a DAB64x card with an FPGA Altera Stratix EP1S40 for
+data processing. The platform features two FMC connectors, each hosting an IBMS
+module integrating voltage input via the lhcb2002b ASIC~\cite{lhcb_asic}. To
+maximize ADC resolution, the signal undergoes amplification using a HAMAMATSU
+C5594 amplifier with a static gain of \SI{36}{dBV}, a bandwidth of
+\SI{1.5}{GHz}, and a low cutoff frequency of \SI{50}{Hz}.
 \begin{figure}[!tbh]
@@
 \end{figure}
-The system schematic is in Fig.~\ref{fig:current_system_processing}. The OF is
-the same as described in the system architecture chapter. The picture omits the
-filters, because they are used in all cases. The MCP-PMT signal needs to be
-amplified by at least 34dB to use the full scale of the 40Mhz ADC. The
-Hamamatsu C559 is used~\cite{bsra_first_operation}. The signal belonging
-to one bunch (\SI{25}{ns}) is integrated in the IBMS (blue triangle with a
-capacitor in the feedback) sampled by ADC (violet rectangle in the figure). The
-DAQ integrates 4 samples (light blue rectangle with $\sum$ symbol) to calculate
-charge in \SI{100}{ns} interval. It produces 64 values, from which are created
-two sets of 64 values with the standard deviation and the mean value is
-calculated. Both sets are passed to the EMA block (green rectangle in
-the figure). All data are saved in the block ram. This is is than shared with
-the PC over wishbone to VME64 bridge. The PC runs server which provides the
-FESA interface to the connected clients.
+The system schematic is depicted in Fig.\ref{fig:current_system_processing}.
+The OF remains consistent with the description provided
+in the system architecture chapter. Notably, filters are not represented in the
+image as they are universally applied. For optimal utilization of the \SI{40}{MHz}
+ADC's full scale, the MCP-PMT signal necessitates a minimum amplification of
+\SI{34}{dB}, a task accomplished by the Hamamatsu C559
+amplifier\cite{bsra_first_operation}.\\
+Within the schematic, the signal corresponding to a single bunch (\SI{25}{ns})
+is integrated within the IBMS module (denoted by a blue triangle with a
+capacitor in the feedback loop) and subsequently sampled by the ADC
+(represented by a violet rectangle). The DAQ system integrates four samples
+(indicated by a light blue rectangle with a $\sum$ symbol) to compute the
+charge over a \SI{100}{ns} interval. This process generates 64 values, from
+which two sets of 64 values are derived, encompassing the standard deviation
+and mean value calculations. Both sets are then forwarded to the Exponential
+Moving Average (EMA) block (depicted by a green rectangle). All collected data
+are stored within the block RAM and subsequently shared with a PC via a
+Wishbone to VME64 bridge. The PC operates a server, facilitating the FESA
+interface for connected clients.
 
 \subsection{Constraints and Limitations}
-The current AGM returns artefacts in the measurements. The signal, which lays
-outside of the gate is not reflecting behaviour of white noise. This is caused
-by the lhcb2002b ASIC. The integrators gain is not linear, have different
-offset and dead times. This means, that system needs to correct at each
-integrator these effects, which creates uncertainties in the results. This
-results in complicated calibration procedur.\\
-The system uses old FPGA platform for which development sofware tools are not
-compatible with newest operation systems. The amplifier is not variable, which
-results in lower resolution for smaller magnitudes.
+The present AGM exhibits artifacts in the measurements. Signals outside the
+gating range do not exhibit the characteristics of white noise, attributed to
+the lhcb2002b ASIC. The integrators' gain lacks linearity, featuring distinct
+offsets and dead times. Consequently, the system necessitates correction for
+these effects at each integrator, leading to uncertainties in the outcomes and
+necessitating intricate calibration procedures.\\
+The system relies on an outdated FPGA platform, rendering its development
+software incompatible with the latest operating systems. Additionally, the
+fixed amplifier configuration contributes to reduced resolution for signals of
+smaller magnitudes.
 
 \section{System Upgrade}
-To resolve the issue of the maintenance, the VFC-HD carrier is used with
-additional RTM board providing driver for the gate and control of the built-in
-test LED. The same carrier board with 500MSPS 14-bit ADC has been used in other
-projects and so it provided the requirement for reducing the maintenance efford.
-The new system removes IBMS cards with lhcb2002b integrators and moving the
-whole integration process to the gateware.
+To address maintenance concerns, the VFC-HD carrier is employed alongside an
+additional RTM board, facilitating gate driver functionality and control of the
+built-in test LED. Leveraging the same carrier board equipped with a 500MSPS
+14-bit ADC from previous projects meets the requirement for reducing
+maintenance efforts. The updated system eliminates IBMS cards featuring
+lhcb2002b integrators, transitioning the entire integration process to the
+gateware.
 
 \subsection{Low band Amplifier}
-The new custom amplififer is designed to allow work with higher signal dynamic
-range, because of its variability.  
+The newly developed custom amplifier is designed to accommodate a wider signal
+dynamic range by virtue of its variability.
 % A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
-In the Fig. \ref{fig:amp_schematics} is shown amplifier's block scheme. All the
-settings is controlled via UART interface. It provides changing the variable
-current-to-voltage conversion factor from \SI{5.8}{mV/\micro A} -
-\SI{1.1}{V/\micro A}. This corresponds to the Voltage gain from \SI{41}{dB} to
-\SI{87}{dB}. The AGM ADC has a no zero offset, so the signal can be shifted in the
-amplifier before post-processing.\\
-The amplifier features also alarm signal generator. This serves to turn of the
-gate, when the light impinging is to intense and it could damage the
-multi-channel plate inside the PMT. The alarm signal is send to the gateware,
-where it is handled. The alarm feature has a variable threshold set.   
+Figure \ref{fig:amp_schematics} illustrates the block diagram of the amplifier.
+All configurations are managed through a UART interface, facilitating
+adjustments to the variable current-to-voltage conversion factor ranging from
+\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}. This corresponds to a voltage
+gain range of \SI{41}{dB} to \SI{87}{dB}. The AGM ADC does not exhibit a zero
+offset, allowing for signal shifting within the amplifier prior to
+post-processing.\\
+Additionally, the amplifier incorporates an alarm signal generator designed to
+deactivate the gate when the incident light intensity exceeds safe levels,
+potentially risking damage to the multi-channel plate within the PMT. The alarm
+signal is transmitted to the gateware for processing and management. Notably,
+the alarm feature includes a variable threshold setting.
 \begin{figure}[!tbh]
@@
 \end{figure}
-The amplifier design has three switches. First switch can set pre-integrator,
-to filter out spikes caused by dark counts of the PMT. Second switch can
-activate either manual or gate driven integration of the acquisition window.  
-Last switch activates low pass filtering with cutoff frequency of 40MHz.
+The amplifier design includes three switches. The first switch can configure
+the pre-integrator to filter out spikes resulting from dark counts of the PMT.
+The second switch enables selection between manual or gate-driven integration
+of the acquisition window. The third switch activates low-pass filtering with a
+cutoff frequency of \SI{40}{MHz}.
 
 \subsection{Acquisition system}
-The DAQ had to be redesigned to be compatible with the new VFC-HD carrier. It
-needed Rear transition module (RTM) to control the gate and built-in test LED.  
-The Fig.~\ref{fig:bsra_daq} is depicted DAQ functionality principle. 
+The DAQ required redesigning for compatibility with the new VFC-HD carrier,
+necessitating the integration of a Rear Transition Module (RTM) to facilitate
+control of the gate and the built-in test LED. Figure~\ref{fig:bsra_daq}
+illustrates the principle of DAQ functionality.
 \begin{figure}[!tbh]
@@
 \end{figure}
-The new DAQ gets asynchronous data samples from ADC 500MSPS 14-bit (violet
-rectangle) in the block of 4 frames every \SI{8}{\nano s} belonging to one
-channel. Each frame has 4 x \SI{16}{bit} values. To calculate the integrals of
-\SI{100}{\nano\second}, the system tags the data. The tagging block resamples
-LHC timing by 500MSPS and creates bunch and turn clock vector masks. Those
-store the information about both clocks phases. The 14-bit data from ADC are
-left aligned to 16-bit values. The tagger sets their two LSBs to one, when the
-ADC sample falls into the edge range. The system stores data from region of
-interest, into the FIFO using the synchronization block pulse. Stored data are
-then processed as a stream of values passed to the integrator. This starts
-summing up values, when it hits the tag in the data indicating the start of the
-bunch. It creates 64 values offseted from the pedestal memory (P[63:0]). This
-subtracts accumulated charge at the gate opening and closing edge. The values
-are then sent to the EMA and the result stored in the block ram available on
-the VME64x bus. The format of the data provided to the PC with runnig FESA
-server is the same with the current AGM~\cite{my_thesis}.
+The new DAQ receives asynchronous data samples from a 500MSPS 14-bit ADC
+(depicted as a violet rectangle), organized in blocks of four frames
+every~\SI{8}{\nano s}, corresponding to one channel. Each frame contains 4 x
+16-bit values. To compute integrals over~\SI{100}{\nano\second}, the system
+employs data tagging. The tagging block resamples LHC timing at 500MSPS and
+generates bunch and turn clock vector masks, storing information about both
+clock phases. The 14-bit ADC data is left-aligned to 16-bit values. The tagger
+sets the two least significant bits to one when the ADC sample falls within the
+edge range.\\
+The system stores data from the region of interest into a FIFO using the
+synchronization block pulse. The stored data is then processed as a stream of
+values passed to the integrator. The integrator begins summing values upon
+encountering the tag indicating the start of the bunch, generating 64 values
+offset from the pedestal memory (P[63:0]). This process subtracts accumulated
+charge at the gate opening and closing edges. The resulting values are then
+sent to the EMA, and the results are stored in the
+block RAM accessible via the VME64x bus. The format of the data provided to the
+PC via the running FESA server matches that of the current
+AGM~\cite{my_thesis}.
 
 \subsection{Installation in LHC}
-The instrument front and Acquistion system is located in LHC Point 4 near RF
-system. The new installation is shown in Fig.~\ref{fig:installation}
-highlighted with violet frame. On its right side is the currently used AGM
-and on the left side is the BSRS. All the instruments share the same light
-source with the BSRT. The instrument is pulled out from the shielding and the
-red arrow ilustrates, where the light comes from and goes in to the MCP-PMT of
-the new AGM.
+
+The instrument OF and DAQ are situated in LHC Point 4 near the RF system. The
+new installation is depicted in Fig.~\ref{fig:installation}, delineated by a
+violet frame. Adjacent to its right side is the currently utilized AGM, while
+the BSRS occupies the left side. All instruments share the same light source
+with the BSRT. The instrument is extracted from the shielding, with the red
+arrow indicating the direction from which light emanates and enters the MCP-PMT
+of the new AGM.
 \begin{figure}[!tbh]
@@
 \end{figure}
-On top of the reflective foil directing light towards the MCP-PMT
-is a LED simulating the light source. This helps verifying the system
-operation. The AGM amplifier is placed on top of the optical front-end to be
-reachable in case of intervention. For reducing the light intensity, there are
-pneumatically controlled optical filters in front of the MCP-PMT.
+Atop the reflective foil, which directs light towards the MCP-PMT, there's a
+LED serving to simulate the light source, aiding in system verification. The
+AGM amplifier is positioned atop the optical front-end for easy access during
+interventions. To regulate light intensity, pneumatically controlled optical
+filters are positioned in front of the MCP-PMT.
 
 \section{Control Interface}
-The gateware outputs data from four different block rams. The first stores raw
-data from the ADC, that is used correctly set the initial delay of the
-instrument's timing. It stores 1.5 turns and therefore it is published with
-\SI{3.3}{Hz}. The next two memories store the actual snapshot data and averaged
-data, but with finer granularity. They store 10 samples per \SI{10}{ms} window,
-which gives the sample rate of \SI{100}{Hz}. The last memory is just bare
-averaged data taken every \SI{10}{ms} defining the publishing rate. The
-fetching handles the FESA server, which obtains interrupt every time the data
-are ready. 
+The gateware outputs data from four distinct block RAMs. The first RAM stores
+raw data from the ADC, crucial for accurately setting the initial timing delay
+of the instrument. It holds data for 1.5 turns, resulting in a publication rate
+of~\SI{3.3}{Hz}. The subsequent two memories store both snapshot and averaged
+data with finer granularity. They retain 10 samples per~\SI{10}{ms} window,
+yielding a sample rate of~\SI{100}{Hz}. The final memory exclusively stores
+averaged data collected every~\SI{10}{ms}, dictating the publication rate. Data
+retrieval is managed by the FESA server, which receives interrupts whenever the
+data becomes available.
 \begin{figure}[!tbh]
@@
 \end{figure}
-To simplify the setup tunining a new interface had to be created. It runs as
-client of FESA server and displays the content of all the block rams. The main
-control panel is depicted in Fig.~\ref{fig:control_interface}. It displays
-three plots, raw data from the ADC (top plot), processed averaged data (down
-plot on the left) and and evolution of the data in time (down plot on the
-right). The menu on the left controls the amplifier and bottom menu controls
-the acquisition delays and optical filters.
+To streamline setup tuning, a new interface was developed. Operating as a
+client of the FESA server, it showcases the content of all block RAMs. The
+primary control panel is illustrated in Fig.~\ref{fig:control_interface}. It
+features three plots: raw data from the ADC (top plot), processed averaged data
+(bottom-left plot), and the temporal evolution of the data (bottom-right plot).
+The left menu governs amplifier settings, while the bottom menu regulates
+acquisition delays and optical filters.
 
 \section{First acquired plots}
-First measurements were taken in November 2023 on the ion beam. The
-optical system splits the SL in ratio 1:8, so the new system gets
-significantly less light then current one. In other word, we expect
-lower value deviation for system measuring light with higher intensity.  
+The initial measurements were conducted in November 2023 using the ion beam.
+The optical system divides the SL in a 1:8 ratio, resulting in significantly
+less light reaching the new system compared to the current one. Consequently,
+we anticipate lower deviation values for the system measuring light with higher
+intensity.
 \begin{figure}[!htb]
@@
 \end{figure}
-The Fig. \ref{fig:comparison_chart} shows first acquisition of the new system
-in comparison with the current one. The red plot is measured by the current
-system and the blue chart is the new acquisition. In a range from 47th - 63th
-bin, the gate is already close. There is just white noise, but the red plot
-slowly decays and it continues below the zero line. This artefact is caused by
-analog integrators and it is non-linear. The new system removes this effect.
-The value deviation of the new acqusition from the current system represents
-the yellow plot. The relative value deviation of the new system from the
-current one is depicted with the yellow plot. In this measurement the maximum
-deviation is 4\% in the area of the decay of the red plot. The the deviation of
-2\% in the steep parts can be caused by the sample phase alignment of the two
-systems.
+Figure~\ref{fig:comparison_chart} displays the initial acquisition results of
+the new system compared to the current one. The red plot represents
+measurements by the current system, while the blue plot depicts the new
+acquisition. Within the range of the 47th to 63rd bin, the gate is closed,
+resulting in white noise. However, the red plot gradually decays and extends
+below the zero line due to artifacts stemming from analog integrators,
+exhibiting non-linear behavior. The new system effectively eliminates this
+artifact. The yellow plot illustrates the value deviation of the new
+acquisition from the current system, with the relative value deviation depicted
+as well. In this measurement, the maximum deviation is~4\% in the region
+corresponding to the decay of the red plot. Additionally, a deviation of~2\% in
+the steep sections may be attributed to sample phase misalignment between the
+two systems.
 
 \section{Summary}
-The new AGM has been implemented on the CERN BI standard platform VFC-HD
-carrier simplifying maintenance. The design removed the IBMS cads with ASIC
-lhcb2002b and so resolved the issue with cumbersome calibration and artefacts
-in the output plots.  It also The changes in the AGM design compared to the
-current AGM are summarized in the following table Tab.
-\ref{tab:system_comparison}.
+The new AGM has been integrated onto the CERN BI standard platform VFC-HD
+carrier, streamlining maintenance procedures. By eliminating IBMS cards
+featuring the lhcb2002b ASIC, the design has addressed issues related to
+cumbersome calibration and artifacts in the output plots. The changes in the
+AGM design compared to the current AGM are summarized in
+Table~\ref{tab:system_comparison}.\\
+The system is installed at LHC Point 4, alongside the current AGM, collecting
+data for further analysis. To conduct a comprehensive reliability test and
+verify proper functionality, additional data collection is required. Initial
+observations indicate that despite receiving less light, the new system can
+still achieve comparable performance to the current AGM.
 \input{tables/system_comparison.tex}
-The system is installed in LHC the point 4 next to the current AGM collecting data
-to be further analyzed. For the complet reliability test and proper function
-verification, it needs to be collected more data, that will help evalate system
-goodness. The systems shows so far, that with less light, it can have still
-comparable outputs to the current AGM.
 

### 2024-05-01 plots/filters.py
normalized values and changed color of the plots

@@ -18,10 +18,13 @@ dir_path = os.path.dirname(sys.argv[1])
 a = np.loadtxt(os.path.join(dir_path, 'timber_data/vfc_abort_gap_raw_data_spill.txt'), 
                encoding='ASCII')
 
+a = a/max(a) # normalize data
+
 data = np.tile(a, (8, 1))
 
 X = np.arange(data.shape[1])
 Y = np.arange(data.shape[0])
+
 X, Y = np.meshgrid(X, Y)
 
 fig = plt.figure()
@@ -31,8 +34,10 @@ ax.tick_params(axis='y',which='major',length=data.shape[0], width=1, labelsize=1
 # ax.set_yticks([0, len(Y)-1, 1])
 # ax.set_xticks([0, len(X)-1, 1])
 
-surf = ax.plot_wireframe(X, Y, data, rstride=1, cstride=0,
-                   cmap='Oranges', edgecolor=None, linewidth=2, antialiased=True)
+surf = ax.plot_wireframe(X, Y, data, 
+                         rstride=1, cstride=0, color='red', 
+                         linewidth=2, antialiased=True)
+
 
 plt.xticks(np.arange(0, 64, 9))
 plt.yticks(np.arange(0, 8, 1))

### 2024-05-01 plots/ions.py
ions generated for poster usage

@@ -64,3 +64,6 @@ frame.set_linewidth(0.5)
 # plt.show()
 
 plt.savefig(sys.argv[1])
+
+file_name = sys.argv[1].split('.')[0]
+plt.savefig(f"{file_name}.svg", transparent=True)

### 2024-05-01 bibliography.tex
Update on Overleaf.

@@
         % http://cds.cern.ch/record/782076/files/CERN-2004-003-V1.pdf?version=2
-        \bibitem{LHC_report} BR\"UNING, O. \emph{LHC design report Volume I The LHC
+        \bibitem{LHC_report} Br\"uning, O. \emph{LHC design report Volume I The LHC
             Main Ring}. Geneva: European Organization for Nuclear Research, c2004-. CERN
-            (Series), 2004-003. ISBN 92-9083-224-0
+            (Series), 2004-003, ISBN 92-9083-224-0.
 
@@
             B. \& Uythoven, J. \emph{Reliability Analysis of the LHC Beam Dumping System}.
-            (2005,6), \url{https://cds.cern.ch/record/841092}
+            (2005,6), \url{https://cds.cern.ch/record/841092}.
 
@@
             G., Höfle, W., Jacquet, D., Jaussi, M., Kain, V., Lefevre, T., Shaposhnikova,
-            E., Uythoven, J. \& Valuch, D. LHC Abort Gap Monitoring and Cleaning.
-            (2010,6), \url{https://cds.cern.ch/record/1277630}
+            E., Uythoven, J. \& Valuch, D. \emph{LHC Abort Gap Monitoring and Cleaning}.
+            (2010,6), \url{https://cds.cern.ch/record/1277630}.
 
@@
             Turner, W. \& Zolotorev, M. \emph{Development of an Abort Gap Monitor for the
-            Large Hadron Collider}.  (2004), \url{https://cds.cern.ch/record/823343}
+            Large Hadron Collider}.  (2004), \url{https://cds.cern.ch/record/823343}.
 
@@
             {\em IEEE Trans. Nucl. Sci.}. \textbf{45} pp. 821-828 (1998),
-            \url{https://cds.cern.ch/record/363087}
+            \url{https://cds.cern.ch/record/363087}.
 
-        \bibitem{high_sensitivity_measurement} C. Fischer, \emph{High Sensitivity
+        \bibitem{high_sensitivity_measurement} Fischer, C.  \emph{High Sensitivity
             Measurement of the Beam Longitudinal Distribution of the LHC Beams}, 
             (2003,1), LHC-BP-ES-0005, rev. 2.0,
-            \url{https://edms.cern.ch/document/328145/2.0}
+            \url{https://edms.cern.ch/document/328145/2.0}.
 
@@
           Goldblatt, A., Jeff, A., Roncarolo, F. \& Fisher, A. \emph{First Operation of
-          the Abort Gap Monitors for LHC}.  (2010,5), \url{http://cds.cern.ch/record/1272172}
+          the Abort Gap Monitors for LHC}.  (2010,5), \url{http://cds.cern.ch/record/1272172}.
 
         \bibitem{lhcb_asic} Böhner, G., Falvard, A., Lecoq, J., Perret, P. \& Trouilleau,
-            C. \emph{Very front-end electronics for the LHCb preshower}.  (CERN,2000,10),
-            \url{http://cds.cern.ch/record/691512}
+            C. \emph{Very front-end electronics for the LHCb preshower}. (CERN, 2000, 10), \url{http://cds.cern.ch/record/691512}.
 
-        \bibitem{my_thesis}Pacner, P. LHC Abort Gap Monitor
-            Acquisition System, Master thesis, (Brno, 2022, 59)
+        \bibitem{my_thesis}Pacner, P. \emph{LHC Abort Gap Monitor
+            Acquisition System}. Master thesis, (Brno, 2022, 59).
 

### 2024-05-01 paper.tex
Update on Overleaf.

@@
 \author{P. Pacner\thanks{petr.pacner@cern.ch}, Brno University of Technology, Brno, Czech Republic \\
-		S. B. Pedersen, D. Belohrad, M. M. Nieto, S. Mazzoni, CERN, Geneva, Switzerland}
+		S. B. Pedersen, D. Belohrad, M. Martin Nieto, S. Mazzoni, CERN, Geneva, Switzerland}
 
@@
     The LHC Abort Gap Monitor (AGM) is part of the LHC machine protection
-    system (MPS) and is designed to measure the particle population in a 3us
+    system (MPS) and is designed to measure the particle population in a \SI{3}{\micro\second}
     wide region known as the "abort gap." This region needs to be kept empty to
@@
 To safely extract the beam from the vacuum compartments, a series of kicker
-magnets belonging to the beam dump system is used. These magnets take 3 us to
+magnets belonging to the beam dump system is used. These magnets take \SI{3}{\micro\second} to
 ramp up their magnetic field~\cite{beam_dump_system}. This defines the size of
-an abort gap (AG) in the bunch train. Due to system imperfections, particles
-populate this gap. Average AG population is in order of $10^{9}$ particles. The
+an abort gap (AG) in the bunch train. Due to system imperfections, a~residual amount of particles
+populate this gap. The average AG population is in order of $10^{9}$ particles. The
 population in a single bunch is four orders of magnitude higher in comparison.
 When the beam dump is initiated, the particles in AG do not receive full
-extraction force. That causes deflection towards the vacuum chamber. When a
-certain energy accumulates in the AG, the magnet can quench. Therefore,
-continuous monitoring of the AG population is necessary, which is the purpose
+extraction force. That causes deflection towards the vacuum chamber. When a~certain energy accumulates in the AG, magnets can quench. Thus,
+a~continuous monitoring of the AG population is necessary, which is the purpose
 of the AGM~\cite{particles_in_ag}.\\
@@
 focusing on system architecture, analog electronics chain, temperature
-dependence, timing instabilities, and a comparison with the upgraded system.
+dependence, timing instabilities, and a~comparison with the upgraded system.
 
 \section{System architecture}
-The system comprises three main parts. The first part is the optical front-end
-(OF), which includes a preamplifier positioned beneath the vacuum chamber. The
+The AGM system comprises of three main parts. The first part is the optical front-end
+(OF), which includes~a pre-amplifier positioned beneath the vacuum chamber. The
 second part is a data acquisition system (DAQ) deployed on an FPGA platform
-located outside the radiation area. The third part involves software (SW) that
+located outside the radiation area. The third part involves a~control software (SW) that
 retrieves, interprets, and presents the measured data, facilitating interaction
@@
     \includegraphics[width=\columnwidth]{bsra_chain.pdf}
-    \caption{BSRA Chain}
+    \caption{BSRA Chain.}
     \label{fig:bsra_chain}
@@
 in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
-LHCb, and CMS). The AGM is situated at Point 4 (indicated by the yellow
+LHCb, and CMS). The AGM is located at Point 4 (indicated by the yellow
 square), close to the CMS experiment. The Timing, Trigger, and Control system
 (TTC) is shown as a purple rectangle in the center of the LHC ring. This system
-receives RF clocking and broadcasts it as messages on the network (TTC
+receives RF clocking and broadcasts it into the network (TTC
 distribution)~\cite{ttc_distribution}. The AGM extracts bunch clock information
 (corresponding to the position of bunches) and turn clock information (marking
-the start of a turn) from these messages.\\
-Beam intensity is gathered by measuring the synchrotron light (SL), as
-indicated by the red line directed towards the Multi-channel photomultiplier
-(MCP-PMT) in the optical front-end (OF). The beam travers first optical
-filters, which increase system dynamic range. Subsequently, the signal is
+the start of a~turn) from the LHC timing block messages.\\
+Beam intensity is measured using the synchrotron light (SL) radiation, as indicated by the red line directed towards the Multi-channel photomultiplier
+(MCP-PMT) in the optical front-end (OF). The beam traverses first optical
+filters, which increases the system dynamic range. Subsequently, the signal is
 transmitted over a \SI{100}{m} cable. To compensate for losses in the cable,
-the signal is amplified beforehand. It then proceeds to the Data Acquisition
+the signal is amplified beforehand. Then it proceeds to the Data Acquisition
 (DAQ) system, which measures \SI{6.4}{\micro\second} window and integrates the
@@
 of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
-measurements are taken every 4th clock cycle (\SI{356}{\micro\second}),
+measurements are taken every $4^{\text{th}}$ clock cycle (\SI{356}{\micro\second}),
 reducing the duty cycle to \SI{0.84}{\%}.\\
@@
 MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
-freedom in system control. Each \SI{100}{\nano\second} value is averaged in an
-extra EMA and provided to the software every \SI{100}{\micro\second}. This
-time is enough to react to changes in AG. The population can change from
-\SI{1.6}{\second} to \SI{25}{\second} due to different
+freedom in the system control. Each \SI{100}{\nano\second} value is averaged in an
+extra Exponential Moving Average (EMA) and provided to the software every \SI{100}{\micro\second}. This
+time is sufficient to react to changes in AG. The population can change from
+1.6 to \SI{25}{\second} due to different
 effects~\cite{high_sensitivity_measurement}.
 
-\subsection{Current Solution}
+\subsection{Current solution}
 The current setup employs a DAB64x card with an FPGA Altera Stratix EP1S40 for
@@
 C5594 amplifier with a static gain of \SI{36}{dBV}, a bandwidth of
-\SI{1.5}{GHz}, and a low cutoff frequency of \SI{50}{Hz}.
+\SI{1.5}{GHz}, and a low cutoff frequency of \SI{50}{kHz}.
 \begin{figure}[!tbh]
@@
 The OF remains consistent with the description provided
-in the system architecture chapter. Notably, filters are not represented in the
-image as they are universally applied. For optimal utilization of the \SI{40}{MHz}
-ADC's full scale, the MCP-PMT signal necessitates a minimum amplification of
+in the system architecture chapter. Note that filters are not represented in the
+figure as they are universally applied. For optimal utilization of the \SI{40}{MHz}
+ADC's full scale, the MCP-PMT signal requires a~minimum amplification of
 \SI{34}{dB}, a task accomplished by the Hamamatsu C559
 amplifier\cite{bsra_first_operation}.\\
-Within the schematic, the signal corresponding to a single bunch (\SI{25}{ns})
-is integrated within the IBMS module (denoted by a blue triangle with a
-capacitor in the feedback loop) and subsequently sampled by the ADC
+The signal corresponding to a~single bunch (\SI{25}{ns})
+is integrated within the IBMS module (denoted by a~blue triangle with a~capacitor in the feedback loop) and subsequently sampled by the ADC
 (represented by a violet rectangle). The DAQ system integrates four samples
-(indicated by a light blue rectangle with a $\sum$ symbol) to compute the
-charge over a \SI{100}{ns} interval. This process generates 64 values, from
+(indicated by a~light blue rectangle with a $\sum$ symbol) to compute the
+charge over a~\SI{100}{ns} interval. This process generates 64 values, from
 which two sets of 64 values are derived, encompassing the standard deviation
-and mean value calculations. Both sets are then forwarded to the Exponential
-Moving Average (EMA) block (depicted by a green rectangle). All collected data
+and mean value calculations. Both sets are then forwarded to the EMA block (depicted by a green rectangle). All collected data
 are stored within the block RAM and subsequently shared with a PC via a
-Wishbone to VME64 bridge. The PC operates a server, facilitating the FESA
+Wishbone to VME64 bridge. The PC operates a~server, facilitating the FESA
 interface for connected clients.
 
-\subsection{Constraints and Limitations}
+\subsection{Constraints and limitations}
 The present AGM exhibits artifacts in the measurements. Signals outside the
 gating range do not exhibit the characteristics of white noise, attributed to
-the lhcb2002b ASIC. The integrators' gain lacks linearity, featuring distinct
-offsets and dead times. Consequently, the system necessitates correction for
+the lhcb2002b ASIC. The gain of the integrators lacks linearity, featuring distinct
+offsets and dead times. Consequently, the system requires correction for
 these effects at each integrator, leading to uncertainties in the outcomes and
@@
 additional RTM board, facilitating gate driver functionality and control of the
-built-in test LED. Leveraging the same carrier board equipped with a 500MSPS
+built-in test LED. Leveraging the same carrier board equipped with a~500MSPS
 14-bit ADC from previous projects meets the requirement for reducing
@@
 
-\subsection{Low band Amplifier}
+\subsection{Low band amplifier}
 The newly developed custom amplifier is designed to accommodate a wider signal
@@
 Figure \ref{fig:amp_schematics} illustrates the block diagram of the amplifier.
-All configurations are managed through a UART interface, facilitating
+All configurations are managed through an~UART interface, facilitating
 adjustments to the variable current-to-voltage conversion factor ranging from
-\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}. This corresponds to a voltage
-gain range of \SI{41}{dB} to \SI{87}{dB}. The AGM ADC does not exhibit a zero
+\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}. This corresponds to a~voltage
+gain range from \SI{41}{dB} to \SI{87}{dB}. The AGM ADC does not exhibit a~zero
 offset, allowing for signal shifting within the amplifier prior to
@@
 Additionally, the amplifier incorporates an alarm signal generator designed to
-deactivate the gate when the incident light intensity exceeds safe levels,
+deactivate the gate, when the incident light intensity exceeds safe levels,
 potentially risking damage to the multi-channel plate within the PMT. The alarm
 signal is transmitted to the gateware for processing and management. Notably,
-the alarm feature includes a variable threshold setting.
+the alarm feature includes a~variable threshold setting.
 \begin{figure}[!tbh]
@@
     \includegraphics[width=\columnwidth]{amp_schematics.pdf}
-    \caption{New AGM custom amplifier}
+    \caption{New AGM custom amplifier.}
     \label{fig:amp_schematics}
@@
 the pre-integrator to filter out spikes resulting from dark counts of the PMT.
-The second switch enables selection between manual or gate-driven integration
-of the acquisition window. The third switch activates low-pass filtering with a
-cutoff frequency of \SI{40}{MHz}.
+The second switch enables selection between a~manual or a~gate-driven integration
+of the acquisition window. The third switch activates low-pass filtering with a~cutoff frequency of \SI{40}{MHz}.
 
@@
 The DAQ required redesigning for compatibility with the new VFC-HD carrier,
-necessitating the integration of a Rear Transition Module (RTM) to facilitate
-control of the gate and the built-in test LED. Figure~\ref{fig:bsra_daq}
+requiring the integration of a Rear Transition Module (RTM) to facilitate
+the control the gate and the built-in test LED. Figure~\ref{fig:bsra_daq}
 illustrates the principle of DAQ functionality.
@@
     \includegraphics[width=\columnwidth]{bsra_daq.pdf}
-    \caption{Ackquisition system schematics}
+    \caption{Acquisition system schematics.}
     \label{fig:bsra_daq}
 \end{figure}
-The new DAQ receives asynchronous data samples from a 500MSPS 14-bit ADC
-(depicted as a violet rectangle), organized in blocks of four frames
-every~\SI{8}{\nano s}, corresponding to one channel. Each frame contains 4 x
-16-bit values. To compute integrals over~\SI{100}{\nano\second}, the system
+The new DAQ receives asynchronous data samples from a~500MSPS 14-bit ADC
+(depicted as a~violet rectangle), organized in blocks of four frames
+every~\SI{8}{\nano s}, corresponding to one channel. Each frame contains 4$\times$16-bit values. To compute integrals over~\SI{100}{\nano\second}, the system
 employs data tagging. The tagging block resamples LHC timing at 500MSPS and
@@
 edge range.\\
-The system stores data from the region of interest into a FIFO using the
-synchronization block pulse. The stored data is then processed as a stream of
+The system stores data from the region of interest into a~FIFO using the
+synchronization block pulse. The stored data is then processed as a~stream of
 values passed to the integrator. The integrator begins summing values upon
-encountering the tag indicating the start of the bunch, generating 64 values
+encountering the tag indicating the start of the bunch, generating 64~values
 offset from the pedestal memory (P[63:0]). This process subtracts accumulated
-charge at the gate opening and closing edges. The resulting values are then
+charge at the gate opening and closing edges. The output values are then
 sent to the EMA, and the results are stored in the
@@
 
+\begin{figure}[!tbh]
+    \centering
+    \includegraphics[width=0.72\columnwidth]{installation.jpg}
+    \caption{New AGM installed in Point 4 next to BSRT.}
+    \label{fig:installation}
+\end{figure}
+
 \subsection{Installation in LHC}
 
-The instrument OF and DAQ are situated in LHC Point 4 near the RF system. The
-new installation is depicted in Fig.~\ref{fig:installation}, delineated by a
-violet frame. Adjacent to its right side is the currently utilized AGM, while
+The instrument OF and DAQ are situated in LHC Point~4 near the RF system. The
+new installation is depicted in Fig.~\ref{fig:installation}, highlighted by a~violet frame. Adjacent to its right side is the currently utilized AGM, while
 the BSRS occupies the left side. All instruments share the same light source
 with the BSRT. The instrument is extracted from the shielding, with the red
-arrow indicating the direction from which light emanates and enters the MCP-PMT
-of the new AGM.
-\begin{figure}[!tbh]
-    \centering
-    \includegraphics[width=\columnwidth]{installation.jpg}
-    \caption{New AGM installed in Point 4 next to BSRT}
-    \label{fig:installation}
-\end{figure}
-Atop the reflective foil, which directs light towards the MCP-PMT, there's a
-LED serving to simulate the light source, aiding in system verification. The
+arrow indicating the direction from which light emanates and enters the MCP-PMT of the new AGM.
+Atop the reflective foil, which directs light towards the MCP-PMT, there is a~LED for simulating the light source, aiding in system verification. The
 AGM amplifier is positioned atop the optical front-end for easy access during
@@
 raw data from the ADC, crucial for accurately setting the initial timing delay
-of the instrument. It holds data for 1.5 turns, resulting in a publication rate
+of the instrument. It holds data for 1.5 turns, resulting in a~publication rate
 of~\SI{3.3}{Hz}. The subsequent two memories store both snapshot and averaged
-data with finer granularity. They retain 10 samples per~\SI{10}{ms} window,
-yielding a sample rate of~\SI{100}{Hz}. The final memory exclusively stores
+data with finer granularity. They retain 10~samples per~\SI{10}{ms} window,
+yielding a~sample rate of~\SI{100}{Hz}. The final memory exclusively stores
 averaged data collected every~\SI{10}{ms}, dictating the publication rate. Data
@@
     \includegraphics[width=\columnwidth]{control_interface.jpg}
-    \caption{New AGM expert graphical interface}
+    \caption{New AGM expert graphical interface.}
     \label{fig:control_interface}
 \end{figure}
-To streamline setup tuning, a new interface was developed. Operating as a
-client of the FESA server, it showcases the content of all block RAMs. The
+To streamline setup tuning, a~new interface was developed. Operating as a~client of the FESA server, it showcases the content of all block RAMs. The
 primary control panel is illustrated in Fig.~\ref{fig:control_interface}. It
-features three plots: raw data from the ADC (top plot), processed averaged data
+features three plots: the raw data from the ADC (top plot), the processed averaged data
 (bottom-left plot), and the temporal evolution of the data (bottom-right plot).
-The left menu governs amplifier settings, while the bottom menu regulates
+The left menu controls amplifier settings, while the bottom menu regulates
 acquisition delays and optical filters.
@@
 The initial measurements were conducted in November 2023 using the ion beam.
-The optical system divides the SL in a 1:8 ratio, resulting in significantly
+The optical system divides the SL in a~1:8 ratio, resulting in significantly
 less light reaching the new system compared to the current one. Consequently,
@@
         \scalebox{0.54}{\input{plots/ions.pgf}}
-        \caption{Features comparison of AGMs}
+        \caption{Features comparison of the present and the upgraded AGMs.}
         \label{fig:comparison_chart}
@@
 \end{figure}
-Figure~\ref{fig:comparison_chart} displays the initial acquisition results of
-the new system compared to the current one. The red plot represents
-measurements by the current system, while the blue plot depicts the new
-acquisition. Within the range of the 47th to 63rd bin, the gate is closed,
-resulting in white noise. However, the red plot gradually decays and extends
-below the zero line due to artifacts stemming from analog integrators,
-exhibiting non-linear behavior. The new system effectively eliminates this
-artifact. The yellow plot illustrates the value deviation of the new
+Figure~\ref{fig:comparison_chart} displays the initial acquisition results of the new system compared to the current one. The red line represents
+measurements by the current system, while the blue line describes the new
+acquisition. Within the range of the $47^{\text{th}}$ to $63^{\text{rd}}$ bin, the gate is closed,
+resulting in a~white noise. However, the red distribution gradually decays and extends
+below zero due to artifacts stemming from analog integrators,
+exhibiting a~non-linear behavior. The new system effectively eliminates this
+artifact. The yellow distribution illustrates the value deviation of the new
 acquisition from the current system, with the relative value deviation depicted
-as well. In this measurement, the maximum deviation is~4\% in the region
-corresponding to the decay of the red plot. Additionally, a deviation of~2\% in
-the steep sections may be attributed to sample phase misalignment between the
-two systems.
+as well. In this measurement, the maximum deviation reaches~4\% in the region
+corresponding to the decay of the red distribution. Additionally, a~deviation of~2\% in
+the steep sections may be attributed to sample phase misalignment between the two systems.
 

### 2024-05-02 paper.tex
Update on Overleaf.

@@
     system (MPS) and is designed to measure the particle population in a \SI{3}{\micro\second}
-    wide region known as the "abort gap." This region needs to be kept empty to
+    wide region known as the "abort gap". This region needs to be kept empty to
     ensure safe beam dumps. The AGM captures the synchrotron light generated in
-    the visible part of the spectra and converts it into an electric signal.
+    the visible part of the spectrum and converts it into an electric signal.
     This signal is then processed by an acquisition system and can trigger the
@@
 ramp up their magnetic field~\cite{beam_dump_system}. This defines the size of
-an abort gap (AG) in the bunch train. Due to system imperfections, a~residual amount of particles
-populate this gap. The average AG population is in order of $10^{9}$ particles. The
-population in a single bunch is four orders of magnitude higher in comparison.
+an abort gap (AG) in the bunch train.
+Due to system imperfections, a residual amount of particles populate this gap.
+The typical AG population levels are two to three orders of magnitude lower in comparison to a single LHC bunch.
 When the beam dump is initiated, the particles in AG do not receive full
-extraction force. That causes deflection towards the vacuum chamber. When a~certain energy accumulates in the AG, magnets can quench. Thus,
+extraction force. That causes deflection towards the vacuum chamber. When a certain energy accumulates in the AG, magnets can quench. Thus,
 a~continuous monitoring of the AG population is necessary, which is the purpose
-of the AGM~\cite{particles_in_ag}.\\
+of the AGM \cite{particles_in_ag}.\\
 This paper reviews the upgrade of the current AGM system in the LHC since 2010,
 focusing on system architecture, analog electronics chain, temperature
-dependence, timing instabilities, and a~comparison with the upgraded system.
+dependence, timing instabilities, and a comparison with the upgraded system.
 
@@
 located outside the radiation area. The third part involves a~control software (SW) that
-retrieves, interprets, and presents the measured data, facilitating interaction
+retrieves, interprets, and publishes the measured data, facilitating interaction
 with the instrument. The system architecture is illustrated in
@@
 LHCb, and CMS). The AGM is located at Point 4 (indicated by the yellow
-square), close to the CMS experiment. The Timing, Trigger, and Control system
+square), next to the CMS experiment. The Timing, Trigger, and Control system
 (TTC) is shown as a purple rectangle in the center of the LHC ring. This system
@@
 Beam intensity is measured using the synchrotron light (SL) radiation, as indicated by the red line directed towards the Multi-channel photomultiplier
-(MCP-PMT) in the optical front-end (OF). The beam traverses first optical
-filters, which increases the system dynamic range. Subsequently, the signal is
-transmitted over a \SI{100}{m} cable. To compensate for losses in the cable,
+(MCP-PMT) in the optical front-end (OF). The beam traverses first Neutral Density optical filters, which increases the system dynamic range. Subsequently, the signal is
+transmitted over a \SI{100}{m}-long cable. To compensate for losses in the cable,
 the signal is amplified beforehand. Then it proceeds to the Data Acquisition
@@
 The measurement period is determined by the MCP-PMT used, which is the gated
-HAMAMATSU R5916U-50 with a duty cycle of \SI{1}{\%}. With a gate pulse duration
+HAMAMATSU R5916U-50 with a maximum duty cycle of \SI{1}{\%}. With a gate pulse duration
 of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
@@
 \subsection{Constraints and limitations}
-The present AGM exhibits artifacts in the measurements. Signals outside the
-gating range do not exhibit the characteristics of white noise, attributed to
-the lhcb2002b ASIC. The gain of the integrators lacks linearity, featuring distinct
-offsets and dead times. Consequently, the system requires correction for
-these effects at each integrator, leading to uncertainties in the outcomes and
-necessitating intricate calibration procedures.\\
+The present AGM exhibits artifacts in the measurements.
+Signals outside the gating range do not exhibit the characteristics of white noise, attributed to the lhcb2002b ASIC.
+The gain of the integrators lacks linearity, featuring distinct offsets and dead times.
+Consequently, the system requires correction for these effects at each integrator, leading to uncertainties in the outcomes and necessitating intricate calibration procedures.
+In addition, the amplifier bandwidth (50 kHz - 1,5 GHz) makes it necessary to implement a correction for the missing DC- 50 kHz band to correctly measure AG profiles needed during LHC commissioning phases.\\
 The system relies on an outdated FPGA platform, rendering its development

### 2024-05-03 plots/ions.py
percent sign change to latex look

@@ -48,7 +48,7 @@ ax2.tick_params(axis='both', direction='in', labelcolor='k',
                labelsize='small', width=0.6, which='both',
                top=True, right=True)
 
-ax2.set_ylabel('deviation [%]')
+ax2.set_ylabel('deviation [\%]')
 ax2.set_yticks(np.linspace(-8, 6, 8))
 ax2.set_ylim([-6.71, 4.51])
 

### 2024-05-06 plots/filters.py
changed x axis name in the plots

@@ -43,7 +43,7 @@ plt.xticks(np.arange(0, 64, 9))
 plt.yticks(np.arange(0, 8, 1))
 
 ax.set_ylabel('Time [s]')
-ax.set_xlabel('Filters output [-]')
+ax.set_xlabel('Output filter index [-]')
 ax.set_zlabel('Normalized Amplitude')
 
 ax.view_init(38, -148)

### 2024-05-06 plots/ions.py

@@ -37,7 +37,7 @@ plt.xticks(np.arange(0, 64, 9))
 
 
 plt.ylabel('Amplitude [-]')
-plt.xlabel('4xBunch sums [-]')
+plt.xlabel('Output filter index [-]')
 plt.xlim([0, 63])
 plt.grid(color=(0.7, 0.7, 0.7), linestyle='--', linewidth=0.6)
 

### 2024-05-06 paper.tex
Update on Overleaf.

@@
 When the beam dump is initiated, the particles in AG do not receive full
-extraction force. That causes deflection towards the vacuum chamber. When a certain energy accumulates in the AG, magnets can quench. Thus,
+extraction force. That causes the particles in the AG to deflect towards the vacuum chamber. When a certain energy accumulates in the AG, magnets can quench. Thus,
 a~continuous monitoring of the AG population is necessary, which is the purpose
@@
 \section{System architecture}
-The AGM system comprises of three main parts. The first part is the optical front-end
-(OF), which includes~a pre-amplifier positioned beneath the vacuum chamber. The
-second part is a data acquisition system (DAQ) deployed on an FPGA platform
-located outside the radiation area. The third part involves a~control software (SW) that
-retrieves, interprets, and publishes the measured data, facilitating interaction
-with the instrument. The system architecture is illustrated in
-Fig.~\ref{fig:bsra_chain}, with each part labeled accordingly.
+The AGM system consists of three main parts:
+
+\begin{itemize}
+    \item \textbf{optical front-end (OF)}, which includes~a pre-amplifier located beneath the vacuum chamber,
+    \item \textbf{data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area
+    \item \textbf{a~control software (SW)} that retrieves, interprets, and publishes the measured data, facilitating interaction with the instrument
+\end{itemize}
+
+The system architecture is illustrated in
+Fig.~\ref{fig:bsra_chain}, with each part labelled accordingly.
 \begin{figure}[!tbh]
@@
 \end{figure} 
-The diagram on the left depicts the layout of the LHC, with beam 1 represented
+The drawing depicts the layout of the LHC, with beam 1 represented
 in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
@@
 receives RF clocking and broadcasts it into the network (TTC
-distribution)~\cite{ttc_distribution}. The AGM extracts bunch clock information
-(corresponding to the position of bunches) and turn clock information (marking
+distribution) through an optical fiber~\cite{ttc_distribution}. The AGM extracts bunch clock 
+(corresponding to the position of bunches) and turn clock (marking
 the start of a~turn) from the LHC timing block messages.\\

### 2024-05-06 paper.tex
Update on Overleaf.

@@
 Beam intensity is measured using the synchrotron light (SL) radiation, as indicated by the red line directed towards the Multi-channel photomultiplier
-(MCP-PMT) in the optical front-end (OF). The beam traverses first Neutral Density optical filters, which increases the system dynamic range. Subsequently, the signal is
+(MCP-PMT) in the optical front-end (OF). The beam traverses first Neutral Density optical filters, which increase the system dynamic range. Subsequently, the signal is
 transmitted over a \SI{100}{m}-long cable. To compensate for losses in the cable,
 the signal is amplified beforehand. Then it proceeds to the Data Acquisition
-(DAQ) system, which measures \SI{6.4}{\micro\second} window and integrates the
-intervals of \SI{100}{\nano\second}. This creates set of 64 values published to
+(DAQ) system, which integrates the incoming signal in \SI{100}{\nano\second} intervals within a \SI{6.4}{\micro\second}-long acquisition window. This creates a set of 64 values published to
 the SW every \SI{10}{\micro\second}.
@@
 freedom in the system control. Each \SI{100}{\nano\second} value is averaged in an
-extra Exponential Moving Average (EMA) and provided to the software every \SI{100}{\micro\second}. This
+ Exponential Moving Average (EMA) and provided to the software every \SI{100}{\micro\second}. This
 time is sufficient to react to changes in AG. The population can change from
@@
 data processing. The platform features two FMC connectors, each hosting an IBMS
-module integrating voltage input via the lhcb2002b ASIC~\cite{lhcb_asic}. To
+module, integrating voltage input via the lhcb2002b ASIC~\cite{lhcb_asic}. To
 maximize ADC resolution, the signal undergoes amplification using a HAMAMATSU
@@
 \SI{1.5}{GHz}, and a low cutoff frequency of \SI{50}{kHz}.
+
 \begin{figure}[!tbh]
@@
 \end{figure}
-The system schematic is depicted in Fig.\ref{fig:current_system_processing}.
+
+The system schematic is depicted in Fig.~\ref{fig:current_system_processing}.
 The OF remains consistent with the description provided
@@
 The gain of the integrators lacks linearity, featuring distinct offsets and dead times.
-Consequently, the system requires correction for these effects at each integrator, leading to uncertainties in the outcomes and necessitating intricate calibration procedures.
+Consequently, the system requires correction for these effects for each integrator, leading to increased uncertainty of the measurement, necessitating intricate calibration procedures.
 In addition, the amplifier bandwidth (50 kHz - 1,5 GHz) makes it necessary to implement a correction for the missing DC- 50 kHz band to correctly measure AG profiles needed during LHC commissioning phases.\\
 The system relies on an outdated FPGA platform, rendering its development
-software incompatible with the latest operating systems. Additionally, the
-fixed amplifier configuration contributes to reduced resolution for signals of
-smaller magnitudes.
+software incompatible with the latest operating systems. Additionally, the fixed amplifier configuration contributes to reduced resolution for signals of smaller magnitudes.
 
 \section{System Upgrade}
-To address maintenance concerns, the VFC-HD carrier is employed alongside an
-additional RTM board, facilitating gate driver functionality and control of the
-built-in test LED. Leveraging the same carrier board equipped with a~500MSPS
-14-bit ADC from previous projects meets the requirement for reducing
-maintenance efforts. The updated system eliminates IBMS cards featuring
-lhcb2002b integrators, transitioning the entire integration process to the
-gateware.
+To address the long-term maintenance concerns, the original system described above had to be completely refurbished.
+While the optical path was kept untouched, the DAQ and the front-end amplifier were replaced by a modern solution.
+Original analogue integrators were replaced by a 500MSPS 14-bit FMC-form factor sampler.
+The original amplifier was replaced by a DC-coupled amplifier, allowing for dynamic change of the gain.
+The FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD) featuring 2$\times 8$GBits DDR3 memories and large Arria V FPGA.
+Such solution eliminates completely the need for analogue integrators as all the signal processing can be implemented into the GateWare.
 
 \subsection{Low band amplifier}
-The newly developed custom amplifier is designed to accommodate a wider signal
-dynamic range by virtue of its variability.
+
+Figure \ref{fig:amp_schematics} illustrates the block diagram of the new amplifier. The amplifier was designed to be highly configurable.
 % A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
-Figure \ref{fig:amp_schematics} illustrates the block diagram of the amplifier.
-All configurations are managed through an~UART interface, facilitating
-adjustments to the variable current-to-voltage conversion factor ranging from
-\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}. This corresponds to a~voltage
-gain range from \SI{41}{dB} to \SI{87}{dB}. The AGM ADC does not exhibit a~zero
-offset, allowing for signal shifting within the amplifier prior to
-post-processing.\\
-Additionally, the amplifier incorporates an alarm signal generator designed to
-deactivate the gate, when the incident light intensity exceeds safe levels,
-potentially risking damage to the multi-channel plate within the PMT. The alarm
-signal is transmitted to the gateware for processing and management. Notably,
-the alarm feature includes a~variable threshold setting.
+
+The configuration is done through an~UART interface, facilitating
+setting of a variable current-to-voltage conversion factor. The conversion factor can vary from
+\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}, corresponding to a~voltage gain ranging from \SI{41}{dB} to \SI{87}{dB} in a $50\Omega$ system.
+The amplifier also implements a programmatic DC-offset compensation, which can be used in the future to extend the signal-to-noise ratio of the measurement.
+Further, the amplifier provides an alarm signal designed to
+deactivate the PMT gate, when the incident light intensity exceeds safe levels.
+The alarm threshold is as well settable through UART.
+It is stored into the amplifier's non-volatile memory to be ready at the amplifier power-up.
+The alarm is transmitted to the gateware for processing and management.
+
 \begin{figure}[!tbh]
@@
 \end{figure}
+
 The amplifier design includes three switches. The first switch can configure

### 2024-05-06 paper.tex
Update on Overleaf.

@@
 
-\author{P. Pacner\thanks{petr.pacner@cern.ch}, Brno University of Technology, Brno, Czech Republic \\
-		S. B. Pedersen, D. Belohrad, M. Martin Nieto, S. Mazzoni, CERN, Geneva, Switzerland}
+\author{D. Belohrad, S. Mazzoni, M. Martin Nieto, P. Pacner\thanks{petr.pacner@cern.ch}, S. B. Pedersen,\\
+CERN, Geneva, Switzerland}
 
@@
 an abort gap (AG) in the bunch train.
-Due to system imperfections, a residual amount of particles populate this gap.
+Due to system imperfections, a residual amount of particles populates this gap.
 The typical AG population levels are two to three orders of magnitude lower in comparison to a single LHC bunch.
@@
 in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
-LHCb, and CMS). The AGM is located at Point 4 (indicated by the yellow
+LHCb, and CMS). The AGM is located at LHC IP4 (indicated by the yellow
 square), next to the CMS experiment. The Timing, Trigger, and Control system
@@
 and mean value calculations. Both sets are then forwarded to the EMA block (depicted by a green rectangle). All collected data
-are stored within the block RAM and subsequently shared with a PC via a
-Wishbone to VME64 bridge. The PC operates a~server, facilitating the FESA
+are stored in a RAM block shared with a front-end computer via VME64 bridge. The PC operates a~server, facilitating the FESA
 interface for connected clients.
@@
 Consequently, the system requires correction for these effects for each integrator, leading to increased uncertainty of the measurement, necessitating intricate calibration procedures.
-In addition, the amplifier bandwidth (50 kHz - 1,5 GHz) makes it necessary to implement a correction for the missing DC- 50 kHz band to correctly measure AG profiles needed during LHC commissioning phases.\\
+In addition, the amplifier bandwidth (50 kHz-1,5 GHz) makes it necessary to implement a correction for the missing DC- 50 kHz band to correctly measure AG profiles needed during LHC commissioning phases.\\
 The system relies on an outdated FPGA platform, rendering its development
@@
 The FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD) featuring 2$\times 8$GBits DDR3 memories and large Arria V FPGA.
-Such solution eliminates completely the need for analogue integrators as all the signal processing can be implemented into the GateWare.
+Such solution eliminates completely the need for analogue integrators, as all the signal processing can be implemented into the GateWare.
 
@@
 \subsection{Acquisition system}
-The DAQ required redesigning for compatibility with the new VFC-HD carrier,
-requiring the integration of a Rear Transition Module (RTM) to facilitate
-the control the gate and the built-in test LED. Figure~\ref{fig:bsra_daq}
+The new acquisition system is housed in a VME crate.
+The DAQ is composed of a VME-based VFC-HD carrier equipped with an FMC-form factor ADC module.
+Additional analogue electronics is implemented into a  Rear Transition Module (RTM), installed in the rear of the VME back plane.
+The RTM implements the PMT gate driver, and a current source used to operate a test light to check the system integrity.
+The RTM communicates to the DAQ through VME P2 connector.
+
+Figure~\ref{fig:bsra_daq}
 illustrates the principle of DAQ functionality.
@@
 \end{figure}
-The new DAQ receives asynchronous data samples from a~500MSPS 14-bit ADC
-(depicted as a~violet rectangle), organized in blocks of four frames
-every~\SI{8}{\nano s}, corresponding to one channel. Each frame contains 4$\times$16-bit values. To compute integrals over~\SI{100}{\nano\second}, the system
-employs data tagging. The tagging block resamples LHC timing at 500MSPS and
-generates bunch and turn clock vector masks, storing information about both
-clock phases. The 14-bit ADC data is left-aligned to 16-bit values. The tagger
-sets the two least significant bits to one when the ADC sample falls within the
-edge range.\\
-The system stores data from the region of interest into a~FIFO using the
-synchronization block pulse. The stored data is then processed as a~stream of
-values passed to the integrator. The integrator begins summing values upon
-encountering the tag indicating the start of the bunch, generating 64~values
-offset from the pedestal memory (P[63:0]). This process subtracts accumulated
-charge at the gate opening and closing edges. The output values are then
-sent to the EMA, and the results are stored in the
-block RAM accessible via the VME64x bus. The format of the data provided to the
-PC via the running FESA server matches that of the current
-AGM~\cite{my_thesis}.
+The new DAQ receives asynchronous data samples from a 4-channel~500MSPS 14-bit ADC
+(shown in violet), as a stream of four frames
+every~\SI{8}{\nano s}, each corresponding to one channel. Each frame contains 4$\times$16-bit samples. To compute integrals over 4$\times$~\SI{25}{\nano\second} bunch slots, the system
+employs data tagging. The tagging block resamples LHC timing into a 500MHz clock domain, and
+generates timing masks, allowing for identification of bunch and turn starts within each individual ADC frame.
+As the 14-bit ADC data is left-aligned, the tagger can use 2 LSBs of each sample to indicate the position of the start of the bunch or turn.\\
+The gateware stores data captured within the acquisition window into a~FIFO using the
+synchronization block pulse. The stored data is then integrated. The integrator begins summing values upon
+encountering the tag indicating the start of the bunch.
+In parallel, it reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
+The offset is on-fly subtracted from the integrated data stream.
+Such pedestal subtraction is needed to remove measurement artifacts caused by the PMT gate opening and closing.
+The output values are filtered by an EMA.
+Results are stored in a format compatible with the previous AGM~\cite{my_thesis}.
+A dual-port RAM, keeping the results, can be read out through the VME64x bus.
 
@@
     \includegraphics[width=0.72\columnwidth]{installation.jpg}
-    \caption{New AGM installed in Point 4 next to BSRT.}
+    \caption{New AGM installed in the LHC IP4, next to BSRT.}
     \label{fig:installation}
@@
 
-\subsection{Installation in LHC}
+\subsection{Installation in the LHC}
 
-The instrument OF and DAQ are situated in LHC Point~4 near the RF system. The
-new installation is depicted in Fig.~\ref{fig:installation}, highlighted by a~violet frame. Adjacent to its right side is the currently utilized AGM, while
-the BSRS occupies the left side. All instruments share the same light source
-with the BSRT. The instrument is extracted from the shielding, with the red
-arrow indicating the direction from which light emanates and enters the MCP-PMT of the new AGM.
-Atop the reflective foil, which directs light towards the MCP-PMT, there is a~LED for simulating the light source, aiding in system verification. The
-AGM amplifier is positioned atop the optical front-end for easy access during
-interventions. To regulate light intensity, pneumatically controlled optical
-filters are positioned in front of the MCP-PMT.
+The AGM~OF and DAQ are located in the LHC IP4, near the LHC RF system. The
+new installation is depicted \textit{in retracted position} in Fig.~\ref{fig:installation}, highlighted by a~violet frame. Adjacent to its right is the currently utilized AGM, while
+the longitudinal density monitor (LDM) occupies the left side. All instruments share the same light source
+provided by the LHC beam synchronous light telescope (BSRT). The red
+arrow indicates the direction of the light entering the entire table.
+The light is split using multiple reflective foils into their respective destinations.
+Both AGM systems are equipped with LEDs installed atop of their reflective foils.
+These serve to perform functional tests.
+The
+AGM amplifier is mounted on the top of the optical front-end. This allows for easy access during interventions. The position of the installed Neutral Density Filters is pneumatically controlled.
 
@@
 Table~\ref{tab:system_comparison}.\\
-The system is installed at LHC Point 4, alongside the current AGM, collecting
+The system is installed at LHC IP4, alongside the current AGM, collecting
 data for further analysis. To conduct a comprehensive reliability test and

### 2024-05-08 paper.tex
Update on Overleaf.

@@
 \section{Introduction}
-During the flat-top phase, the LHC ring stores up to \SI{350}{MJ} of beam energy,
-spread across 2808 bunches with an average beam transverse size under
-\SI{1}{mm}. This high energy density can melt metallic surfaces and quench
+During the flat-top phase, the LHC ring stores up to \SI{350}{MJ} of beam energy, spread across 2808 bunches with an average beam transverse size under \SI{1}{mm}.
+%
+This high energy density can melt metallic surfaces and quench
 superconducting magnets, posing a risk to the machine~\cite{LHC_report}.
-To safely extract the beam from the vacuum compartments, a series of kicker
-magnets belonging to the beam dump system is used. These magnets take \SI{3}{\micro\second} to
-ramp up their magnetic field~\cite{beam_dump_system}. This defines the size of
-an abort gap (AG) in the bunch train.
+%
+To safely extract the beam from the circulating beam lines, a series of kicker magnets belonging to the beam dump system is used. 
+%
+Kicker magnets need \SI{3}{\micro\second} to ramp up their magnetic field~\cite{beam_dump_system}.
+%
+This defines the size of an abort gap (AG) in the bunch train.
+%
 Due to system imperfections, a residual amount of particles populates this gap.
-The typical AG population levels are two to three orders of magnitude lower in comparison to a single LHC bunch.
+%
+The typical AG population levels are two to three orders of magnitude lower in comparison to a single pilot LHC bunch.
+%
 When the beam dump is initiated, the particles in AG do not receive full
-extraction force. That causes the particles in the AG to deflect towards the vacuum chamber. When a certain energy accumulates in the AG, magnets can quench. Thus,
-a~continuous monitoring of the AG population is necessary, which is the purpose
-of the AGM \cite{particles_in_ag}.\\
-This paper reviews the upgrade of the current AGM system in the LHC since 2010,
-focusing on system architecture, analog electronics chain, temperature
-dependence, timing instabilities, and a comparison with the upgraded system.
+extraction force.
+%
+That causes the particles in the AG to deflect towards the vacuum chamber, possibly causing the magnets to quench. 
+%
+Thus, a~continuous monitoring of the AG population is necessary, which is the purpose of the AGM \cite{particles_in_ag}.
+\\
+This paper discusses the upgrade of the current AGM system installed in the LHC since 2010, focusing on system architecture, analog electronics chain, temperature dependence, timing instabilities, and compares both systems.
 
 \section{System architecture}
-The AGM system consists of three main parts:
-
-\begin{itemize}
-    \item \textbf{optical front-end (OF)}, which includes~a pre-amplifier located beneath the vacuum chamber,
-    \item \textbf{data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area
-    \item \textbf{a~control software (SW)} that retrieves, interprets, and publishes the measured data, facilitating interaction with the instrument
-\end{itemize}
-
-The system architecture is illustrated in
-Fig.~\ref{fig:bsra_chain}, with each part labelled accordingly.
+The system architecture is shown in Fig.~\ref{fig:bsra_chain}.
+%
+It depicts the layout of the LHC, with beam 1 represented in blue and beam 2 in red.
+%
+The AGM consists of three main parts:
+%
+\begin{enumerate}
+    \item \textbf{an optical front-end (OF)}, which includes~a pre-amplifier, located beneath the vacuum chamber,
+    \item \textbf{a data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area
+    \item \textbf{a control software (SW)} that retrieves, interprets, and publishes the measured data,
+\end{enumerate}
+%
 \begin{figure}[!tbh]
@@
     \includegraphics[width=\columnwidth]{bsra_chain.pdf}
-    \caption{BSRA Chain.}
+    \caption{Overview of the BSRA system.}
     \label{fig:bsra_chain}
 \end{figure}
-The drawing depicts the layout of the LHC, with beam 1 represented
-in red and beam 2 in blue. It includes all four experiments (Alice, Atlas,
-LHCb, and CMS). The AGM is located at LHC IP4 (indicated by the yellow
-square), next to the CMS experiment. The Timing, Trigger, and Control system
-(TTC) is shown as a purple rectangle in the center of the LHC ring. This system
-receives RF clocking and broadcasts it into the network (TTC
-distribution) through an optical fiber~\cite{ttc_distribution}. The AGM extracts bunch clock 
-(corresponding to the position of bunches) and turn clock (marking
-the start of a~turn) from the LHC timing block messages.\\
-Beam intensity is measured using the synchrotron light (SL) radiation, as indicated by the red line directed towards the Multi-channel photomultiplier
-(MCP-PMT) in the optical front-end (OF). The beam traverses first Neutral Density optical filters, which increase the system dynamic range. Subsequently, the signal is
-transmitted over a \SI{100}{m}-long cable. To compensate for losses in the cable,
-the signal is amplified beforehand. Then it proceeds to the Data Acquisition
-(DAQ) system, which integrates the incoming signal in \SI{100}{\nano\second} intervals within a \SI{6.4}{\micro\second}-long acquisition window. This creates a set of 64 values published to
-the SW every \SI{10}{\micro\second}.
 
+%
+and is installed at LHC IP4 together with other beam diagnostic, and the LHC low-level RF system.
+%
+The LHC timing distribution (TTC) broadcasts through an optical cable - along the LHC - turn and bunch marks, together with other information, as e.g., actual beam energy.~\cite{ttc_distribution}.
+%
+The bunch and turn marks identify the start of each individual bunch, and the position of the first bunch in a turn.   
+%
+The AGM uses this information to re-synchronize its acquisition window to the AG.
+%
 \subsection{Working principle}
-The measurement period is determined by the MCP-PMT used, which is the gated
-HAMAMATSU R5916U-50 with a maximum duty cycle of \SI{1}{\%}. With a gate pulse duration
-of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
-measurements are taken every $4^{\text{th}}$ clock cycle (\SI{356}{\micro\second}),
-reducing the duty cycle to \SI{0.84}{\%}.\\
-The system captures 64 values with a granularity of \SI{100}{\nano\second}. The
-MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
-freedom in the system control. Each \SI{100}{\nano\second} value is averaged in an
- Exponential Moving Average (EMA) and provided to the software every \SI{100}{\micro\second}. This
-time is sufficient to react to changes in AG. The population can change from
-1.6 to \SI{25}{\second} due to different
-effects~\cite{high_sensitivity_measurement}.
+%
+The particle population in the AG is measured intercepting the synchrotron radiation (SR). 
+%
+The AGM uses a Multi-channel photo-multiplier (PMT) to convert the SR light, into an electric signal.
+%
+Additional Neutral Density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the PMT, thus optimize the system dynamic range.
+% 
+Subsequently, the electric signal is amplified, and transmitted over a \SI{100}{m}-long cable to a Data Acquisition (DAQ) system.
+%
+The DAQ integrates the incoming signal in \SI{100}{\nano\second} intervals within a \SI{6.4}{\micro\second}-long acquisition window.
+%
+Each of the sixty-four \SI{100}{\nano\second} integrals is independently averaged in an Exponential Moving Averager (EMA).
+%
+The averaged result is published to the software with a repetition rate of 10~Hz, which is sufficient to react to even the fastest changes in AG population.~\cite{high_sensitivity_measurement}.
+%
+\\
+The measurement period is determined by the PMT used.
+%
+In our case, it is HAMAMATSU R5916U-50. 
+%
+Its maximum duty cycle is \SI{1}{\%}. 
+%
+With a gate pulse duration of \SI{3}{\micro\second} and one LHC revolution period of \SI{89}{\micro\second}, the measurements are taken every $4^{\text{th}}$ clock cycle (\SI{356}{\micro\second}).
+%
+This corresponds to a duty cycle of \SI{0.84}{\%}.
+\\
+%
 
-\subsection{Current solution}
-The current setup employs a DAB64x card with an FPGA Altera Stratix EP1S40 for
-data processing. The platform features two FMC connectors, each hosting an IBMS
-module, integrating voltage input via the lhcb2002b ASIC~\cite{lhcb_asic}. To
-maximize ADC resolution, the signal undergoes amplification using a HAMAMATSU
-C5594 amplifier with a static gain of \SI{36}{dBV}, a bandwidth of
-\SI{1.5}{GHz}, and a low cutoff frequency of \SI{50}{kHz}.
-
+\subsection{Current system, used since 2010}
 \begin{figure}[!tbh]
@@
 
-The system schematic is depicted in Fig.~\ref{fig:current_system_processing}.
-The OF remains consistent with the description provided
-in the system architecture chapter. Note that filters are not represented in the
-figure as they are universally applied. For optimal utilization of the \SI{40}{MHz}
-ADC's full scale, the MCP-PMT signal requires a~minimum amplification of
-\SI{34}{dB}, a task accomplished by the Hamamatsu C559
-amplifier\cite{bsra_first_operation}.\\
-The signal corresponding to a~single bunch (\SI{25}{ns})
-is integrated within the IBMS module (denoted by a~blue triangle with a~capacitor in the feedback loop) and subsequently sampled by the ADC
-(represented by a violet rectangle). The DAQ system integrates four samples
-(indicated by a~light blue rectangle with a $\sum$ symbol) to compute the
-charge over a~\SI{100}{ns} interval. This process generates 64 values, from
-which two sets of 64 values are derived, encompassing the standard deviation
-and mean value calculations. Both sets are then forwarded to the EMA block (depicted by a green rectangle). All collected data
-are stored in a RAM block shared with a front-end computer via VME64 bridge. The PC operates a~server, facilitating the FESA
-interface for connected clients.
+The currently used system is shown in Fig.~\ref{fig:current_system_processing}.
+%
+The optical path, including filters, is common to both the actual version of the system, and the proposed upgrade. As well, the PMT type is the same in both systems.
 
-\subsection{Constraints and limitations}
-The present AGM exhibits artifacts in the measurements.
-Signals outside the gating range do not exhibit the characteristics of white noise, attributed to the lhcb2002b ASIC.
-The gain of the integrators lacks linearity, featuring distinct offsets and dead times.
-Consequently, the system requires correction for these effects for each integrator, leading to increased uncertainty of the measurement, necessitating intricate calibration procedures.
-In addition, the amplifier bandwidth (50 kHz-1,5 GHz) makes it necessary to implement a correction for the missing DC- 50 kHz band to correctly measure AG profiles needed during LHC commissioning phases.\\
-The system relies on an outdated FPGA platform, rendering its development
-software incompatible with the latest operating systems. Additionally, the fixed amplifier configuration contributes to reduced resolution for signals of smaller magnitudes.
+The actual setup uses a digital acquisition board (DAB64x) equipped by Altera Stratix EP1S40 FPGA, used for the data processing.
+%
+The DAB64x hosts two Individual Bunch Measurement Systems (IBMS)~\cite{ibms}, integrating the analogue input signal via the LHCb2002 ASIC~\cite{lhcb_asic}.
+%
+The analogue signal is provided by MCP PMT, and it is amplified before the integration to improve on the measurement SNR.
+%
+The amplifier used is HAMAMATSU C5594~\cite{bsra_first_operation}, featuring a static voltage gain of \SI{36}{dBV}, in the bandwidth of \SI{50}{kHz} to \SI{1.5}{GHz}.
+%
+The LHCb2002 in the IBMS integrates the input amplified signal in \SI{25}{\nano\second} intervals, producing a stream of analogue 'DC-like' values.
+%
+These are subsequently sampled by a 40MSPS 14-bit ADC, resulting in a digital data stream, where each value corresponds to an integral of an individual LHC bunch.
+%
+The DAQ gateware sums four consecutive samples to compute the
+bunch charge present on a~\SI{100}{ns} interval.
+%
+This process generates 64 values per single turn acquisition.
+%
+For each individual value, a standard deviation and mean value is calculated, and separately filtered by EMA. 
+%
+All collected data are stored in a dual-port RAM block shared to a front-end computer (FEC) via VME64 bridge.
+%
+The front-end acts as a server, publishing the data upstream through FESA~\cite{fesa}.
+
+\subsection{Reasons for Upgrade}
+The present AGM uses old technology to measure the beam charge. 
+%
+The analogue integrators used in IBMS are manufactured using obsoleted technology, rendering them impossible to get.
+%
+In addition, each integrator is unique: different gain, different switching characteristics, different offsets. 
+%
+So, the gateware must correct these effects.
+%
+Further, the amplifier bandwidth (50 kHz-1,5 GHz) increases system complexity, as a correction for the missing DC component needs to be implemented.
+%
+The amplifier gain is also fixed, so the ADC cannot optimally re-use available dynamic range.
+\\
+The system relies on an outdated FPGA platform, and the development SW is no more compatible with the latest operating systems.
 
 \section{System Upgrade}
-To address the long-term maintenance concerns, the original system described above had to be completely refurbished.
-While the optical path was kept untouched, the DAQ and the front-end amplifier were replaced by a modern solution.
-Original analogue integrators were replaced by a 500MSPS 14-bit FMC-form factor sampler.
-The original amplifier was replaced by a DC-coupled amplifier, allowing for dynamic change of the gain.
-The FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD) featuring 2$\times 8$GBits DDR3 memories and large Arria V FPGA.
-Such solution eliminates completely the need for analogue integrators, as all the signal processing can be implemented into the GateWare.
+To address the long-term maintenance concerns, the original system described above has to be completely refurbished. 
+%
+An updated version of the AGM was installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
+%
+While the optics of the new system was copied from the old one, the DAQ and the front-end amplifier were replaced by a modern solution.
+%
+A new DC-coupled amplifier was designed, allowing for dynamic change of the gain.
+%
+Original analogue integrators were replaced by a 4-channel 500MSPS 14-bit FMC-form factor sampler.
+%
+FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD), featuring 2$\times 8$GBits DDR3 memories and a large Arria V FPGA.
+%
+Such solution eliminates completely the need for analogue integrators, as all the signal processing can be implemented in the gateware.
 
-\subsection{Low band amplifier}
+\subsection{New DC-coupled amplifier}
 
-Figure \ref{fig:amp_schematics} illustrates the block diagram of the new amplifier. The amplifier was designed to be highly configurable.
+Figure \ref{fig:amp_schematics} illustrates the block diagram of the new amplifier.
+%
+The amplifier was designed to match the used PMT, while being highly configurable.
 % A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
-
-The configuration is done through an~UART interface, facilitating
-setting of a variable current-to-voltage conversion factor. The conversion factor can vary from
-\SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}, corresponding to a~voltage gain ranging from \SI{41}{dB} to \SI{87}{dB} in a $50\Omega$ system.
-The amplifier also implements a programmatic DC-offset compensation, which can be used in the future to extend the signal-to-noise ratio of the measurement.
-Further, the amplifier provides an alarm signal designed to
-deactivate the PMT gate, when the incident light intensity exceeds safe levels.
-The alarm threshold is as well settable through UART.
-It is stored into the amplifier's non-volatile memory to be ready at the amplifier power-up.
-The alarm is transmitted to the gateware for processing and management.
-
+%
+A~UART interface allows for setting a transimpedance gain.
+%
+The gain is selectable in a range of \SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}.
+%
+This corresponds to a~voltage gain of \SI{41}{dB} to \SI{87}{dB} in a $50\Omega$ system.
+%
+A programmatic DC-offset compensation is implemented in the amplifier.
+%
+It can be used - together with variable gain - to optimize the signal's amplitude for the ADC.
+%
+The amplifier implements an alarm, which interlocks the PMT gate when the incident light generates a current, that is near the PMT's maximum allowable average current.
+%
+The alarm threshold setting is stored through UART into the amplifier's non-volatile memory, so that it protects the PMT immediately at the amplifier power-up.
+%
+The alarm status is also transmitted to the gateware.
+%
 \begin{figure}[!tbh]
@@
 \end{figure}
-
-The amplifier design includes three switches. The first switch can configure
-the pre-integrator to filter out spikes resulting from dark counts of the PMT.
-The second switch enables selection between a~manual or a~gate-driven integration
-of the acquisition window. The third switch activates low-pass filtering with a~cutoff frequency of \SI{40}{MHz}.
-
+%
 \subsection{Acquisition system}
-The new acquisition system is housed in a VME crate.
-The DAQ is composed of a VME-based VFC-HD carrier equipped with an FMC-form factor ADC module.
-Additional analogue electronics is implemented into a  Rear Transition Module (RTM), installed in the rear of the VME back plane.
-The RTM implements the PMT gate driver, and a current source used to operate a test light to check the system integrity.
-The RTM communicates to the DAQ through VME P2 connector.
-
-Figure~\ref{fig:bsra_daq}
-illustrates the principle of DAQ functionality.
 \begin{figure}[!tbh]
@@
 \end{figure}
-The new DAQ receives asynchronous data samples from a 4-channel~500MSPS 14-bit ADC
-(shown in violet), as a stream of four frames
-every~\SI{8}{\nano s}, each corresponding to one channel. Each frame contains 4$\times$16-bit samples. To compute integrals over 4$\times$~\SI{25}{\nano\second} bunch slots, the system
-employs data tagging. The tagging block resamples LHC timing into a 500MHz clock domain, and
-generates timing masks, allowing for identification of bunch and turn starts within each individual ADC frame.
-As the 14-bit ADC data is left-aligned, the tagger can use 2 LSBs of each sample to indicate the position of the start of the bunch or turn.\\
-The gateware stores data captured within the acquisition window into a~FIFO using the
-synchronization block pulse. The stored data is then integrated. The integrator begins summing values upon
-encountering the tag indicating the start of the bunch.
+%
+The new DAQ (Fig.~\ref{fig:bsra_daq}) receives asynchronous data samples as a stream of four frames every~\SI{8}{\nano s}, each corresponding to one channel.
+%
+Each frame contains 4$\times$16-bit words, storing left-aligned 14-bit ADC samples. 
+%
+To compute integrals over 4$\times$~\SI{25}{\nano\second} bunch slots, the system employs data tagging. 
+%
+The tagger resamples LHC timing, and generates timing masks, allowing for identification of bunch and turn starts within each individual ADC frame.
+%
+The tagger uses 2 LSBs of each word to indicate the position of the start of the bunch or turn.
+\\
+The start of the capture is synchronized through data tags to the AG.
+%
+The captured data are stored into a~FIFO, and integrated. 
+%
+The integrator begins summing values upon encountering the start of the bunch tag.
+%
 In parallel, it reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
+%
 The offset is on-fly subtracted from the integrated data stream. 
+%
 Such pedestal subtraction is needed to remove measurement artifacts caused by the PMT gate opening and closing. 
-The output values are filtered by an EMA.
-Results are stored in a format compatible with the previous AGM~\cite{my_thesis}.
-A dual-port RAM, keeping the results, can be read out through the VME64x bus.
+%
+The output values are filtered by an EMA, results are kept in dual-port RAM, and read out through the VME64x bus~\cite{my_thesis}.
 
@@
 AGM amplifier is mounted on the top of the optical front-end. This allows for easy access during interventions. The position of the installed Neutral Density Filters is pneumatically controlled.
-
-\section{Control Interface}
-The gateware outputs data from four distinct block RAMs. The first RAM stores
-raw data from the ADC, crucial for accurately setting the initial timing delay
-of the instrument. It holds data for 1.5 turns, resulting in a~publication rate
-of~\SI{3.3}{Hz}. The subsequent two memories store both snapshot and averaged
-data with finer granularity. They retain 10~samples per~\SI{10}{ms} window,
-yielding a~sample rate of~\SI{100}{Hz}. The final memory exclusively stores
-averaged data collected every~\SI{10}{ms}, dictating the publication rate. Data
-retrieval is managed by the FESA server, which receives interrupts whenever the
-data becomes available.
-\begin{figure}[!tbh]
-    \centering
-    \includegraphics[width=\columnwidth]{control_interface.jpg}
-    \caption{New AGM expert graphical interface.}
-    \label{fig:control_interface}
-\end{figure}
-To streamline setup tuning, a~new interface was developed. Operating as a~client of the FESA server, it showcases the content of all block RAMs. The
-primary control panel is illustrated in Fig.~\ref{fig:control_interface}. It
-features three plots: the raw data from the ADC (top plot), the processed averaged data
-(bottom-left plot), and the temporal evolution of the data (bottom-right plot).
-The left menu controls amplifier settings, while the bottom menu regulates
-acquisition delays and optical filters.
 
@@
 featuring the lhcb2002b ASIC, the design has addressed issues related to
-cumbersome calibration and artifacts in the output plots. The changes in the
-AGM design compared to the current AGM are summarized in
-Table~\ref{tab:system_comparison}.\\
+cumbersome calibration and artifacts in the output plots. \\
 The system is installed at LHC IP4, alongside the current AGM, collecting
@@
 still achieve comparable performance to the current AGM.
-\input{tables/system_comparison.tex}
 

### 2024-05-08 bibliography.tex

@@
             (2010,6), \url{https://cds.cern.ch/record/1277630}.
+
+        \bibitem{ibms} Guerrero, A., Jakob, H., Jones, R., Savioz, J.J,
+        \emph{The SPS Individual Bunch Measurement System}. (2001), DIPAC 2001, Grenoble, \url{https://accelconf.web.cern.ch/d01/papers/PM12.pdf}
+
+        \bibitem{fesa} Arruat, M., Fernanderz, L., Jackson, S., Locci, F., Nougaret, J.L., Peryt, M., Radeva, A., Sobczak, M., Vanden Eynden, M., (2007), ICALEPCS2007, \url{https://accelconf.web.cern.ch/ica07/TALKS/WOPA04_TALK.PDF}
 

### 2024-05-08 paper.tex
Update on Overleaf.

@@
 \\
-This paper discusses the upgrade of the current AGM system installed in the LHC since 2010, focusing on system architecture, analog electronics chain, temperature dependence, timing instabilities, and compares both systems.
+This paper discusses the upgrade of the operational AGM system installed in the LHC since 2010, focusing on system architecture, analog electronics chain, temperature dependence, timing instabilities, and compares both systems.
 
@@
     \includegraphics[width=\columnwidth]{bsra_chain.pdf}
-    \caption{Overview of the BSRA system.}
+    \caption{Overview of the abort gap monitor system.}
     \label{fig:bsra_chain}
@@
 
-\subsection{Current system, used since 2010}
+\subsection{Operational system, used since 2010}
 \begin{figure}[!tbh]
@@
     \includegraphics[width=\columnwidth]{existing_system_processing.pdf}
-    \caption{Current system block diagram}
+    \caption{Operational AGM system overview}
     \label{fig:current_system_processing}
@@
 %
-All collected data are stored in a dual-port RAM block shared to a front-end computer (FEC) via VME64 bridge.
+All collected data are stored in a RAM block shared to a front-end computer (FEC) via VME64 bridge.
 %
@@
 %
-While the optics of the new system was copied from the old one, the DAQ and the front-end amplifier were replaced by a modern solution.
+While the optics of the new system was copied from the operational one, the DAQ and the front-end amplifier were replaced by a modern solution.
 %
@@
 %
-The tagger uses 2 LSBs of each word to indicate the position of the start of the bunch or turn.
+Tags are written into 2 LSBs of each word to indicate the position of the start of the bunch or turn.
 \\
-The start of the capture is synchronized through data tags to the AG.
 %
@@
 %
-The integrator begins summing values upon encountering the start of the bunch tag.
+The integrator begins summing values upon encountering the first bunch tag appearing within the acquisition window.
 %
@@
 %
-Such pedestal subtraction is needed to remove measurement artifacts caused by the PMT gate opening and closing. 
+Such pedestal subtraction is needed to remove systematic effects, e.g., PMT gate opening. 
 %
-The output values are filtered by an EMA, results are kept in dual-port RAM, and read out through the VME64x bus~\cite{my_thesis}.
+The output values are filtered by an EMA, results are kept in RAM, and read out through the VME64x bus~\cite{my_thesis}.
 
@@
     \centering
-    \includegraphics[width=0.72\columnwidth]{installation.jpg}
+    \includegraphics[width=1.0\columnwidth]{installation.jpg}
     \caption{New AGM installed in the LHC IP4, next to BSRT.}
@@
 
-The AGM~OF and DAQ are located in the LHC IP4, near the LHC RF system. The
-new installation is depicted \textit{in retracted position} in Fig.~\ref{fig:installation}, highlighted by a~violet frame. Adjacent to its right is the currently utilized AGM, while
-the longitudinal density monitor (LDM) occupies the left side. All instruments share the same light source
-provided by the LHC beam synchronous light telescope (BSRT). The red
-arrow indicates the direction of the light entering the entire table.
-The light is split using multiple reflective foils into their respective destinations.
-Both AGM systems are equipped with LEDs installed atop of their reflective foils.
+The new installation is depicted \textit{in retracted position} in Fig.~\ref{fig:installation}, highlighted by a~violet frame.
+%
+Adjacent to its right is the operational AGM, while the longitudinal density monitor (LDM) occupies the left side.
+%
+All instruments share the same light source provided by the LHC beam synchronous light telescope (BSRT).
+%
+The red arrow indicates the direction of the light entering the optical table.
+%
+The light is unequally split using multiple reflective foils into their respective destinations such, that the new AGM intercepts only 10\% of luminosity of the operational AGM.
+%
+Both AGMs are equipped with LEDs installed atop of their reflective foils.
+%
 These serve to perform functional tests.
-The
-AGM amplifier is mounted on the top of the optical front-end. This allows for easy access during interventions. The position of the installed Neutral Density Filters is pneumatically controlled.
+%
+The new AGM amplifier is mounted on the top of the optical front-end to ease the interventions.
 
-\section{First acquired plots}
-The initial measurements were conducted in November 2023 using the ion beam.
-The optical system divides the SL in a~1:8 ratio, resulting in significantly
-less light reaching the new system compared to the current one. Consequently,
-we anticipate lower deviation values for the system measuring light with higher
-intensity.
+\section{First measurements}
 \begin{figure}[!htb]
@@
         \scalebox{0.54}{\input{plots/ions.pgf}}
-        \caption{Features comparison of the present and the upgraded AGMs.}
+        \caption{Comparison of the AGM measurements}
         \label{fig:comparison_chart}
@@
 \end{figure}
-Figure~\ref{fig:comparison_chart} displays the initial acquisition results of the new system compared to the current one. The red line represents
-measurements by the current system, while the blue line describes the new
-acquisition. Within the range of the $47^{\text{th}}$ to $63^{\text{rd}}$ bin, the gate is closed,
-resulting in a~white noise. However, the red distribution gradually decays and extends
-below zero due to artifacts stemming from analog integrators,
-exhibiting a~non-linear behavior. The new system effectively eliminates this
-artifact. The yellow distribution illustrates the value deviation of the new
-acquisition from the current system, with the relative value deviation depicted
-as well. In this measurement, the maximum deviation reaches~4\% in the region
-corresponding to the decay of the red distribution. Additionally, a~deviation of~2\% in
-the steep sections may be attributed to sample phase misalignment between the two systems.
+
+The initial measurements were conducted in November 2023 using the LHC ion beam.
+%
+Figure~\ref{fig:comparison_chart} shows the very first measurements, compared to the operational AGM.
+%
+Both measurements agree to 2\% within the operational area, signals however deviate starting at $47^{\text{th}}$ bin, resulting in maximum relative error of 4\%.
+%
+This is surprising, as no signal shall be present - the PMT gates are closed. 
+%
+However, the operational AGM signal gradually decays, and extends below zero.
+%
+This effect is systematic, and is mostly caused by analogue signal processing chain and non-ideal analogue integration.
+%
+The new system effectively eliminates this.
 
 \section{Summary}
-The new AGM has been integrated onto the CERN BI standard platform VFC-HD
-carrier, streamlining maintenance procedures. By eliminating IBMS cards
-featuring the lhcb2002b ASIC, the design has addressed issues related to
-cumbersome calibration and artifacts in the output plots. \\
-The system is installed at LHC IP4, alongside the current AGM, collecting
-data for further analysis. To conduct a comprehensive reliability test and
-verify proper functionality, additional data collection is required. Initial
-observations indicate that despite receiving less light, the new system can
-still achieve comparable performance to the current AGM.
+The presented text describes upgrade of the operational abort gap monitor. 
+%
+The operational system, using obsolete parts, has to be replaced in the near future by a new AGM to assure long-term maintainability.
+%
+A fully digital solution was developed.
+%
+To assess its performance, it was installed in the LHC, on beam 1, in parallel with the operational AGM.
+%
+Very first measurements from November 2023 show exceptionally good performance even using considerably lower amount of intercepted light.
+%
+The upgraded AGM is now collecting data from the LHC 2024 proton run.
+%
+Further analysis in terms of accuracy, reliability, and stability has to be conducted, with the ultimate goal of replacing both operational AGMs by their new versions.
 

### 2024-05-08 plots/ions.py
changed names and size of fonts in the ions plot

@@ -30,14 +30,14 @@ plt.plot(agm_current_norm, '-x', markersize=4, color=(0.878, 0.106, 0.141), line
 plt.plot(agm_new_norm, '-o', markersize=2, color=(0, 0.3, 0.7), linewidth=0.8)
 
 ax.tick_params(axis='both', direction='in', labelcolor='k',
-               labelsize='small', width=0.6, which='both',
+               labelsize='x-large', width=0.6, which='both',
                top=True, right=True)
 
 plt.xticks(np.arange(0, 64, 9))
 
 
-plt.ylabel('Amplitude [-]')
-plt.xlabel('Output filter index [-]')
+plt.ylabel('Amplitude [-]', fontsize="x-large")
+plt.xlabel('Output filter index [-]', fontsize="x-large")
 plt.xlim([0, 63])
 plt.grid(color=(0.7, 0.7, 0.7), linestyle='--', linewidth=0.6)
 
@@ -45,16 +45,16 @@ ax2 = ax.twinx()
 ax2.plot(agm_error, '-o', markersize=5, color=(0.961, 0.761, 0.067), linewidth=0.8)  
 
 ax2.tick_params(axis='both', direction='in', labelcolor='k',
-               labelsize='small', width=0.6, which='both',
+               labelsize='x-large', width=0.6, which='both',
                top=True, right=True)
 
-ax2.set_ylabel('deviation [\%]')
+ax2.set_ylabel('Relative Error [\%]', fontsize="x-large")
 ax2.set_yticks(np.linspace(-8, 6, 8))
 ax2.set_ylim([-6.71, 4.51])
 
-legend = fig.legend(['Current AGM', 'New AGM', 'Deviation'], 
+legend = fig.legend(['Operational AGM', 'New AGM', 'Relative Error'], 
          loc='upper left', shadow=False, frameon=True, borderpad=0.5,
-         framealpha=1, facecolor='white', fancybox=False, edgecolor=(0, 0, 0),
+         framealpha=1, fontsize="x-large", facecolor='white', fancybox=False, edgecolor=(0, 0, 0),
                     bbox_to_anchor=(0,1), bbox_transform=ax.transAxes)
 
 frame = legend.get_frame()

### 2024-05-09 paper.tex
Update on Overleaf.

@@
 \section{Introduction}
-During the flat-top phase, the LHC ring stores up to \SI{350}{MJ} of beam energy, spread across 2808 bunches with an average beam transverse size under \SI{1}{mm}.
+During its operation at flat top energy, the LHC ring stores up to \SI{350}{MJ} of beam energy, spread across 2808 bunches with an average beam transverse size under \SI{1}{mm}.
 %
@@
 %
-This defines the size of an abort gap (AG) in the bunch train.
+This defines the size of an Abort Gap (AG) in the bunch train.
 %
@@
 %
-When the beam dump is initiated, the particles in AG do not receive full
-extraction force.
+When the beam dump is initiated, the particles in the AG do not receive full
+extraction force, are lost on their way to the dump line and can generate damages or magnet quenches.  
 %
-That causes the particles in the AG to deflect towards the vacuum chamber, possibly causing the magnets to quench. 
+%That causes the particles in the AG to
+%are deflects towards the vacuum chamber, possibly causing the magnets to quench. 
 %
-Thus, a~continuous monitoring of the AG population is necessary, which is the purpose of the AGM \cite{particles_in_ag}.
+The purpose of the AGM \cite{particles_in_ag} is to 
+a~continuous monitoring of the AG population in order to trigger the abort gap cleaning when  necessary. 
 \\
-This paper discusses the upgrade of the operational AGM system installed in the LHC since 2010, focusing on system architecture, analog electronics chain, temperature dependence, timing instabilities, and compares both systems.
+This paper discusses the upgrade of the operational AGM installed in the LHC since 2010, detailing the system architecture and analog electronics chain, and provide a first performance comparison  of both systems.
 
@@
 %
-The AGM consists of three main parts:
+The LHC AGM consists of three main parts:
 %
 \begin{enumerate}
-    \item \textbf{an optical front-end (OF)}, which includes~a pre-amplifier, located beneath the vacuum chamber,
-    \item \textbf{a data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area
-    \item \textbf{a control software (SW)} that retrieves, interprets, and publishes the measured data,
+    \item \textbf{an optical front-end (OF)}, which includes~a pre-amplifier, located in the LHC tunnel,
+    \item \textbf{a data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area,
+    \item \textbf{a control software (SW)} that retrieves, interprets, and publishes the measured data.
 \end{enumerate}
@@
     \includegraphics[width=\columnwidth]{bsra_chain.pdf}
-    \caption{Overview of the abort gap monitor system.}
+    \caption{Overview of an abort gap monitor system.}
     \label{fig:bsra_chain}
@@
 %
-and is installed at LHC IP4 together with other beam diagnostic, and the LHC low-level RF system.
+The AGM is installed at LHC IP4 as one of the beam diagnostics based on synchrotron radiation (SR) detection. %together with other beam diagnostic, and the LHC low-level RF system.
 %
-The LHC timing distribution (TTC) broadcasts through an optical cable - along the LHC - turn and bunch marks, together with other information, as e.g., actual beam energy.~\cite{ttc_distribution}.
+The LHC timing distribution (TTC) broadcasts through an optical cable - along the LHC - turn and bunch marks, together with other information, as e.g., actual beam energy~\cite{ttc_distribution}.
 %
@@
 %
-The particle population in the AG is measured intercepting the synchrotron radiation (SR). 
+An in-vacuum mirror intercepts  SR  emitted by protons passing through magnets located approximately 27 meters upstream.
+It then directs the radiation to a dedicated optical line installed beneath the beam pipe.
+
+%The particle population in the AG is measured intercepting the synchrotron radiation (SR). 
 %
-The AGM uses a Multi-channel photo-multiplier (PMT) to convert the SR light, into an electric signal.
+The AGM is designed to collect part of th extracted SR on  a Multi-channel photo-multiplier (PMT), which converts it  into an electric signal.
 %
-Additional Neutral Density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the PMT, thus optimize the system dynamic range.
+Neutral Density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the PMT, thus optimize the system dynamic range.
 % 
@@
 %
-The optical path, including filters, is common to both the actual version of the system, and the proposed upgrade. As well, the PMT type is the same in both systems.
+The optical path, including filters, is common to both the operational version of the system, and the proposed upgrade. As well, the PMT type is the same in both systems.
 
-The actual setup uses a digital acquisition board (DAB64x) equipped by Altera Stratix EP1S40 FPGA, used for the data processing.
+The operational setup uses a digital acquisition board (DAB64x) equipped by Altera Stratix EP1S40 FPGA, used for the data processing.
 %
@@
 %
-The amplifier used is HAMAMATSU C5594~\cite{bsra_first_operation}, featuring a static voltage gain of \SI{36}{dBV}, in the bandwidth of \SI{50}{kHz} to \SI{1.5}{GHz}.
+The amplifier used is HAMAMATSU C5594~\cite{bsra_first_operation}, featuring a fixed voltage gain of \SI{36}{dBV}, in the bandwidth of \SI{50}{kHz} to \SI{1.5}{GHz}.
 %
@@
 \section{System Upgrade}
-To address the long-term maintenance concerns, the original system described above has to be completely refurbished. 
-%
-An updated version of the AGM was installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
+To address the long-term maintenance concerns, the original system described above has to be refurbished. 
 %
@@
 Such solution eliminates completely the need for analogue integrators, as all the signal processing can be implemented in the gateware.  
+\\
+An updated version of the AGM was in 2023 installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
 
@@
 
-Figure \ref{fig:amp_schematics} illustrates the block diagram of the new amplifier.
+Figure \ref{fig:amp_schematics} depicts the block diagram of the new amplifier.
 %
@@
 %
-Tags are written into 2 LSBs of each word to indicate the position of the start of the bunch or turn.
+Tags are written into 2 unused LSBs of each word to indicate the position of the start of the bunch or turn.
 \\
 %
-The captured data are stored into a~FIFO, and integrated. 
+The tagged samples are stored into a~FIFO, and integrated. 
 %
@@
 \section{First measurements}
+
+\vspace{-5mm}
 \begin{figure}[!htb]
@@
 
+\vspace{-5mm}
 The initial measurements were conducted in November 2023 using the LHC ion beam.
@@
 %
-The operational system, using obsolete parts, has to be replaced in the near future by a new AGM to assure long-term maintainability.
+The operational system has to be replaced in the near future by a new AGM to assure long-term maintainability.
 %

### 2024-05-11 paper.tex
Update on Overleaf.

@@
 \section{Introduction}
-During its operation at flat top energy, the LHC ring stores up to \SI{350}{MJ} of beam energy, spread across 2808 bunches with an average beam transverse size under \SI{1}{mm}.
+The LHC ring stores up to \SI{350}{MJ} of beam energy, when operating at the flat top energy, spread across 2808 bunches with an average beam transverse size under \SI{1}{mm}.
 %
@@
 When the beam dump is initiated, the particles in the AG do not receive full
-extraction force, are lost on their way to the dump line and can generate damages or magnet quenches.  
+extraction force, leading to losses along the dump line that could result in damage or magnet quenching.
 %
 %That causes the particles in the AG to
-%are deflects towards the vacuum chamber, possibly causing the magnets to quench. 
+% deflect towards the vacuum chamber, possibly causing the magnets to quench. 
 %
-The purpose of the AGM \cite{particles_in_ag} is to 
-a~continuous monitoring of the AG population in order to trigger the abort gap cleaning when  necessary. 
+The purpose of the AGM is a~continuous monitoring of the AG population in order to trigger the abort gap cleaning when  necessary \cite{particles_in_ag} .
 \\
-This paper discusses the upgrade of the operational AGM installed in the LHC since 2010, detailing the system architecture and analog electronics chain, and provide a first performance comparison  of both systems.
+This paper discusses the upgrade of the operational AGM installed in the LHC since 2010, detailing the system architecture and analogue electronics chain, and provides a first performance comparison  of both systems.
 
@@
 \begin{enumerate}
-    \item \textbf{an optical front-end (OF)}, which includes~a pre-amplifier, located in the LHC tunnel,
-    \item \textbf{a data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area,
-    \item \textbf{a control software (SW)} that retrieves, interprets, and publishes the measured data.
+    \item \textbf{optical front-end (OF)}, which includes~a pre-amplifier, located in the LHC tunnel,
+    \item \textbf{data acquisition system (DAQ)} deployed on an FPGA platform located outside the radiation area,
+    \item \textbf{control software (SW)} that retrieves, interprets, and publishes the measured data.
 \end{enumerate}
@@
 %
-The AGM is designed to collect part of th extracted SR on  a Multi-channel photo-multiplier (PMT), which converts it  into an electric signal.
+The AGM collects part of the extracted SR via Multi-channel plate photo-multiplier (MCP-PMT)converting it into an electric signal.
 %
-Neutral Density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the PMT, thus optimize the system dynamic range.
+Neutral density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the MCP-PMT, thus optimizing the system dynamic range.
 % 
-Subsequently, the electric signal is amplified, and transmitted over a \SI{100}{m}-long cable to a Data Acquisition (DAQ) system.
+Subsequently, the electric signal is amplified and transmitted over a \SI{100}{m}-long cable to DAQ.
 %
@@
 %
-Each of the sixty-four \SI{100}{\nano\second} integrals is independently averaged in an Exponential Moving Averager (EMA).
+Each of the 64 \SI{100}{\nano\second} integrals is independently averaged in an Exponential Moving Averager (EMA).
 %
-The averaged result is published to the software with a repetition rate of 10~Hz, which is sufficient to react to even the fastest changes in AG population.~\cite{high_sensitivity_measurement}.
+The averaged result is published to the software with a repetition rate of \SI{10}{Hz}, which is sufficient to react to even the fastest changes in AG population.~\cite{high_sensitivity_measurement}.
 %
 \\
-The measurement period is determined by the PMT used.
+The measurement period depends on the specific MCP-PMT (HAMAMATSU R5916U-50) that features a maximum duty cycle of \SI{1}{\%}. 
+%is determined by the PMT used.
 %
-In our case, it is HAMAMATSU R5916U-50. 
+%In our case, it is HAMAMATSU R5916U-50. 
 %
-Its maximum duty cycle is \SI{1}{\%}. 
+%Its maximum duty cycle is \SI{1}{\%}. 
 %
@@
 %
-The optical path, including filters, is common to both the operational version of the system, and the proposed upgrade. As well, the PMT type is the same in both systems.
-
-The operational setup uses a digital acquisition board (DAB64x) equipped by Altera Stratix EP1S40 FPGA, used for the data processing.
+The optical path, including filters and MCP-PMT, is common to both the operational version of the system, and the proposed upgrade.
+%As well, the PMT type is the same in both systems.
+The operational setup utilizes a digital acquisition board (DAB64x) incorporating an Altera Stratix EP1S40 FPGA for data processing.
 %
-The DAB64x hosts two Individual Bunch Measurement Systems (IBMS)~\cite{ibms}, integrating the analogue input signal via the LHCb2002 ASIC~\cite{lhcb_asic}.
+The DAB64x hosts two Individual Bunch Measurement Systems (IBMS)~\cite{ibms}, integrating the analog input signal via the LHCb2002 ASIC~\cite{lhcb_asic}.
 %
-The analogue signal is provided by MCP PMT, and it is amplified before the integration to improve on the measurement SNR.
+The analog signal generated by  the MCP-PMT is amplified  prior to integration to  enhance the measurement's Signal-to-Noise Ratio  (SNR).
 %
-The amplifier used is HAMAMATSU C5594~\cite{bsra_first_operation}, featuring a fixed voltage gain of \SI{36}{dBV}, in the bandwidth of \SI{50}{kHz} to \SI{1.5}{GHz}.
+The amplifier (HAMAMATSU C5594~\cite{bsra_first_operation}) has a fixed voltage gain of \SI{36}{dBV} and the bandwidth of \SI{1.5}{GHz} with the low cutoff frequency at \SI{50}{kHz}.
 %
-The LHCb2002 in the IBMS integrates the input amplified signal in \SI{25}{\nano\second} intervals, producing a stream of analogue 'DC-like' values.
+The amplified signal is fed to the LHCb2002 in the IBMS integrating in \SI{25}{\nano\second} intervals, producing a stream of analog  'DC-like' values.
 %
-These are subsequently sampled by a 40MSPS 14-bit ADC, resulting in a digital data stream, where each value corresponds to an integral of an individual LHC bunch.
+These are subsequently sampled by a \SI{40}{MSPS} 14-bit ADC, resulting in a digital data stream, where each value corresponds to an integral of an individual LHC \SI{25}{ns} bucket.
 %
 The DAQ gateware sums four consecutive samples to compute the
-bunch charge present on a~\SI{100}{ns} interval.
+proton charge present on a~\SI{100}{ns} interval.
 %
@@
 %
-The front-end acts as a server, publishing the data upstream through FESA~\cite{fesa}.
+A dedicated  front-end  server, publishes the data stream through FESA~\cite{fesa}.
 
 \subsection{Reasons for Upgrade}
-The present AGM uses old technology to measure the beam charge. 
+
+The operational AGM primarily relies on outdated   technology, such as  the analogue integrators used in the IBMS,  which are no longer manufactured.
+%that are not produced anymore.  manufactured using obsoleted technology, rendering them impossible to get.
 %
-The analogue integrators used in IBMS are manufactured using obsoleted technology, rendering them impossible to get.
+Furthermore, each integrator is unique, with varying gain, switching characteristics, and offsets. The gateware must correct these variations.
+%Furthermore,  each integrator is unique, with varying gain, switching characteristics, and offsets. 
 %
-In addition, each integrator is unique: different gain, different switching characteristics, different offsets. 
+%The gateware must correct these variations.
+%different gain, different switching characteristics, different offsets and the 
 %
-So, the gateware must correct these effects.
+%So, the
+%gateware must correct these effects.
 %
-Further, the amplifier bandwidth (50 kHz-1,5 GHz) increases system complexity, as a correction for the missing DC component needs to be implemented.
+In addition, the amplifier bandwidth (50 kHz-1,5 GHz) %increases system complexity, as
+required a correction for the missing DC component and the amplifier gain is fixed,  for which  the overall dynamic range is limtied by the ADC. 
+%needs to be implemented.
 %
-The amplifier gain is also fixed, so the ADC cannot optimally re-use available dynamic range.
+%dynamic range is not fully exploited. cannot optimally re-use available dynamic range.
 \\
@@
 %
-A new DC-coupled amplifier was designed, allowing for dynamic change of the gain.
+A new DC-coupled amplifier was designed, thus allowing enahncing the overall dynamic range. 
 %
-Original analogue integrators were replaced by a 4-channel 500MSPS 14-bit FMC-form factor sampler.
+It was decided to change from analog to digital instegration of the PMT signal, via a DAQ based on  a 4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
 %
-FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD), featuring 2$\times 8$GBits DDR3 memories and a large Arria V FPGA.
+The FMC ADC module is installed into an in-house built FPGA carrier (VFC-HD), featuring 2$\times 8$GBits DDR3 memories and a large Arria V FPGA.
 %
-Such solution eliminates completely the need for analogue integrators, as all the signal processing can be implemented in the gateware.  
+Such a solution eliminates completely the need for the obsolete analogue integrators, as all the signal processing can be implemented in the gateware.  
 \\
-An updated version of the AGM was in 2023 installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
+In early 2023, the new AGM system was installed alongside the legacy system to facilitate an easy comparison of both systems' performance.
+%An updated version of the AGM was in 2023 installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
 
@@
 %
-The amplifier was designed to match the used PMT, while being highly configurable.
+The amplifier was designed to match the AGM MCP-PMT and to be  highly configurable.
 % A = U^2/(i^2 * R^2) => A_dB = 20*log10(U/(i*R))
 %
-A~UART interface allows for setting a transimpedance gain.
+A universal asynchronous receiver-transmitter (UART) interface allows for setting a trans-impedance gain.
 %
-The gain is selectable in a range of \SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}.
+The gain is adjustable in a range of \SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}.
 %
@@
 %
-A programmatic DC-offset compensation is implemented in the amplifier.
+A programmable DC-offset compensation is implemented in the amplifier.
 %
@@
 %
-The amplifier implements an alarm, which interlocks the PMT gate when the incident light generates a current, that is near the PMT's maximum allowable average current.
+The amplifier design incorporates an alarm. This alarm interlocks the MCP-PMT gate when the incident light produces a current nearing the MCP-PMT's maximum allowable average current.
+%The amplifier implements 
+%an alarm that interlocks the MCP-PMT gate when the incident light generates a current approachng  the MCP-PMT's maximum allowable average current.
 %
-The alarm threshold setting is stored through UART into the amplifier's non-volatile memory, so that it protects the PMT immediately at the amplifier power-up.
+The alarm threshold setting is stored through the UART into the amplifier's non-volatile memory, so that 
+%it protects 
+the MCP-PMT is protected also after a power reset. %immediately at the amplifier power-up.
 %
@@
 %
-The tagger resamples LHC timing, and generates timing masks, allowing for identification of bunch and turn starts within each individual ADC frame.
+The tagger resamples the LHC timing, and generates timing masks that  provide each individual ADC frame with %allowing for identification of 
+bunch and turn start markers. 
+%within each individual ADC frame.
 %
-Tags are written into 2 unused LSBs of each word to indicate the position of the start of the bunch or turn.
+Tags are inserted into the  2 unused least significan bits (LSBs) of each word to indicate the start of the  the bunch or turn.
 \\
 %
-The tagged samples are stored into a~FIFO, and integrated. 
+The tagged samples are stored in a~FIFO ((First In, First Out), and then integrated. 
 %
-The integrator begins summing values upon encountering the first bunch tag appearing within the acquisition window.
+The integrator is triggered %begins summing values 
+by the  the first bunch tag appearing within the acquisition window.
 %
-In parallel, it reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
+In parallel to the integral (sum of the values), the system reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
 %
-The offset is on-fly subtracted from the integrated data stream. 
+The offset is subtracted  from the integrated data stream on the fly.
 %
-Such pedestal subtraction is needed to remove systematic effects, e.g., PMT gate opening. 
+Such pedestal subtraction is needed to remove systematic effects, e.g. related to the  MCP-PMT gate opening. 
 %
-The output values are filtered by an EMA, results are kept in RAM, and read out through the VME64x bus~\cite{my_thesis}.
+The output values are filtered by an Exponential Moving Average (EMA), the results are stored  in RAM, and then read out through the VME64x bus~\cite{my_thesis}.
 
@@
 
-The new installation is depicted \textit{in retracted position} in Fig.~\ref{fig:installation}, highlighted by a~violet frame.
+The new installation, when \textit{in retracted position} is  highlighted by a~violet frame in Fig.~\ref{fig:installation}, 
 %
-Adjacent to its right is the operational AGM, while the longitudinal density monitor (LDM) occupies the left side.
+The legacy AGM  (on the right) and  the longitudinal density monitor (LDM, on the left) are also partially visible in the same figure.
+% Adjacent to its right is the operational AGM, while the longitudinal density monitor (LDM) occupies the left side.
 %
-All instruments share the same light source provided by the LHC beam synchronous light telescope (BSRT).
+All these instruments are part of the LHC beam synchronous light telescope (BSRT) and use part of the synchrotron radiation extracted by the in-vacuum extraction system sitting above the telescope.
+%  instruments share the same light source provided by the LHC beam synchronous light telescope (BSRT).
 %
@@
 %
-The light is unequally split using multiple reflective foils into their respective destinations such, that the new AGM intercepts only 10\% of luminosity of the operational AGM.
+The light is unequally split using multiple reflective foils into their respective destinations.  The new AGM receives  only 10\% of the radiation sent to the legacy AGM.
 %
-Both AGMs are equipped with LEDs installed atop of their reflective foils.
+Both AGMs are equipped with LEDs installed  on top of their reflective foils for functional and calibration tests. 
 %
-These serve to perform functional tests.
+%These serve to perform functional tests.
 %
-The new AGM amplifier is mounted on the top of the optical front-end to ease the interventions.
+It is worth noting  that the new AGM amplifier is mounted on top of the optical front-end to facilitate  interventions.
 
@@
 \vspace{-5mm}
-The initial measurements were conducted in November 2023 using the LHC ion beam.
+After few tests and few adjustements in the system layout The initial measurements were conducted in November 2023 using the LHC ion beam.
 %
@@
 %
-This is surprising, as no signal shall be present - the PMT gates are closed. 
+This is surprising, as no signal shall be present - the MCP-PMT gates are closed. 
 %
@@
 %
-This effect is systematic, and is mostly caused by analogue signal processing chain and non-ideal analogue integration.
+This effect is systematic, and is mostly caused by analog signal processing chain and non-ideal analogue integration.
 %

### 2024-05-11 paper.tex

@@
 %
-The AGM collects part of the extracted SR via Multi-channel plate photo-multiplier (MCP-PMT)converting it into an electric signal.
+The AGM collects part of the extracted SR via Multi-channel plate photo-multiplier (MCP-PMT) converting it into an electric signal.
 %
-Neutral density filters in the optical front-end (OF) allow  changing the light intensity intercepted by the MCP-PMT, thus optimizing the system dynamic range.
+Neutral density filters in the optical front-end (OF) allow  changing the light intensity, thus optimizing the system dynamic range.
 % 
@@
 %
-A new DC-coupled amplifier was designed, thus allowing enahncing the overall dynamic range. 
+A new DC-coupled amplifier was designed, thus allowing enhancing the overall dynamic range. 
 %
-It was decided to change from analog to digital instegration of the PMT signal, via a DAQ based on  a 4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
+It was decided to change from analog to digital integration of the MCP-PMT signal, via a DAQ based on  a 4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
 %
@@
 %
-The alarm status is also transmitted to the gateware.
+%The alarm status is also transmitted to the gateware.
 %
@@
 %
-Tags are inserted into the  2 unused least significan bits (LSBs) of each word to indicate the start of the  the bunch or turn.
+Tags are inserted into the  2 unused least significant bits (LSBs) of each word to indicate the start of the  the bunch or turn.
 \\
 %
-The tagged samples are stored in a~FIFO ((First In, First Out), and then integrated. 
+The tagged samples are stored in a~FIFO (First In, First Out), and then integrated. 
 %
 The integrator is triggered %begins summing values 
-by the  the first bunch tag appearing within the acquisition window.
+by the first bunch tag appearing within the acquisition window.
 %
-In parallel to the integral (sum of the values), the system reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
+In parallel the system reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
 %
@@
 %
-The output values are filtered by an Exponential Moving Average (EMA), the results are stored  in RAM, and then read out through the VME64x bus~\cite{my_thesis}.
+The output values are filtered by EMA, the results are stored  in RAM, and then read out through the VME64x bus~\cite{my_thesis}.
 
@@
 %
-The legacy AGM  (on the right) and  the longitudinal density monitor (LDM, on the left) are also partially visible in the same figure.
+The operational AGM  (on the right) and  the longitudinal density monitor (LDM, on the left) are also partially visible in the same figure. 
 % Adjacent to its right is the operational AGM, while the longitudinal density monitor (LDM) occupies the left side.
 %
-All these instruments are part of the LHC beam synchronous light telescope (BSRT) and use part of the synchrotron radiation extracted by the in-vacuum extraction system sitting above the telescope.
+All these instruments are part of the LHC beam synchrotron light telescope (BSRT) and use part of the synchrotron radiation extracted by the in-vacuum extraction system sitting above the BSRT.
 % instruments share the same light source provided by the LHC beam synchronous light telescope (BSRT).
@@
 %
-The light is unequally split using multiple reflective foils into their respective destinations.  The new AGM receives  only 10\% of the radiation sent to the legacy AGM.
+The light is unequally split using multiple reflective foils into their respective destinations.  The new AGM receives  only 10\% of the radiation sent to the operational AGM.
 %
@@
 %
-It is worth noting  that the new AGM amplifier is mounted on top of the optical front-end to facilitate  interventions.
+The new AGM amplifier is mounted on the top of the optical front-end to ease the interventions.
 
@@
 \vspace{-5mm}
-After few tests and few adjustements in the system layout The initial measurements were conducted in November 2023 using the LHC ion beam.
+Initial measurements were conducted in November 2023 using the LHC ion beam.
 %
@@
 %
-Both measurements agree to 2\% within the operational area, signals however deviate starting at $47^{\text{th}}$ bin, resulting in maximum relative error of 4\%.
+Both measurements agree to 2\% within the operational area, but deviate starting at $47^{\text{th}}$ bin, resulting in maximum relative error of 4\%.
+Despite the MCP-PMT gate is closed at that point and no signal is present, the operational AGM signal gradually decays, and extends below zero.
 %
-This is surprising, as no signal shall be present - the MCP-PMT gates are closed. 
-%
-However, the operational AGM signal gradually decays, and extends below zero.
+%Whoops, no signal shall be present - the MCP-PMT gates are closed.
+%This is surprising, as no signal shall be present - the MCP-PMT gates are closed. 
 %
@@
 \section{Summary}
-The presented text describes upgrade of the operational abort gap monitor. 
+This paper describes upgrade of the operational AGM.
 %

### 2024-05-11 paper.tex

@@
 %
-To safely extract the beam from the circulating beam lines, a series of kicker magnets belonging to the beam dump system is used. 
+To safely extract the beam from the circulating beam lines, a~series of kicker magnets belonging to the beam dump system is used. 
 %
@@
 % 
-Subsequently, the electric signal is amplified and transmitted over a \SI{100}{m}-long cable to DAQ.
+Subsequently, the electric signal is amplified and transmitted over a~\SI{100}{m}-long cable to DAQ.
 %
@@
 %
-This corresponds to a duty cycle of \SI{0.84}{\%}.
+This corresponds to a~duty cycle of \SI{0.84}{\%}.
 \\
@@
 %
-It was decided to change from analog to digital integration of the MCP-PMT signal, via a DAQ based on  a 4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
+It was decided to change from analog to digital integration of the MCP-PMT signal, via a DAQ based on  a~4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
 %
@@
 %
-A universal asynchronous receiver-transmitter (UART) interface allows for setting a trans-impedance gain.
+A universal asynchronous receiver-transmitter (UART) interface allows for setting a~trans-impedance gain.
 %
-The gain is adjustable in a range of \SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}.
+The gain is adjustable in a~range of \SI{5.8}{mV/\micro A} to \SI{1.1}{V/\micro A}.
 %

### 2024-05-11 paper.tex
Update on Overleaf.

@@
 \subsection{Operational system, used since 2010}
+The currently used system is shown in Fig.~\ref{fig:current_system_processing}.
+%
+The optical path, including filters and MCP-PMT, is common to both the operational version of the system, and the proposed upgrade.
 \begin{figure}[!tbh]
@@
 \end{figure}
-
-The currently used system is shown in Fig.~\ref{fig:current_system_processing}.
-%
-The optical path, including filters and MCP-PMT, is common to both the operational version of the system, and the proposed upgrade.
 %As well, the PMT type is the same in both systems.
@@
 \subsection{Acquisition system}
+The new DAQ (Fig.~\ref{fig:bsra_daq}) receives asynchronous data samples as a stream of four frames every~\SI{8}{\nano s}, each corresponding to one channel.
+%
 \begin{figure}[!tbh]
@@
 \end{figure}
-%
-The new DAQ (Fig.~\ref{fig:bsra_daq}) receives asynchronous data samples as a stream of four frames every~\SI{8}{\nano s}, each corresponding to one channel.
 %

### 2024-06-11 paper.tex

@@
 
+% NOTE: I (David) had to remove from abstract the proton beam info, because we did not
+% have enough time to work with protons. This article only compares ION beams so far.
+% I'll try to tweak the submitted abstract as well - if that is still possible. If not,
+% the correct abstract will be shown in the article.
 \begin{abstract}
@@
     acquisition chain, compares the characteristics of both implementations,
-    and showcases recent measurements conducted on the LHC ion and proton
-    beams.
+    and showcases recent measurements conducted on the LHC ion beams.
 \end{abstract}
@@
 %
-This defines the size of an Abort Gap (AG) in the bunch train.
+This defines the duration of an Abort Gap (AG) in the bunch train.
 %
@@
 When the beam dump is initiated, the particles in the AG do not receive full
-extraction force, leading to losses along the dump line that could result in damage or magnet quenching.
+extraction kicks, leading to losses along the dump line that could result in damage or magnet quenching.
 %
@@
 %
-The purpose of the AGM is a~continuous monitoring of the AG population in order to trigger the abort gap cleaning when  necessary \cite{particles_in_ag} .
+The purpose of the AGM is a~continuous monitoring of the AG population in order to trigger the abort gap cleaning when  necessary \cite{particles_in_ag}.
 \\
@@
 %
-The LHC timing distribution (TTC) broadcasts through an optical cable - along the LHC - turn and bunch marks, together with other information, as e.g., actual beam energy~\cite{ttc_distribution}.
+The LHC timing distribution (TTC) broadcasts along the LHC turn and bunch marks, together with other information, as e.g., actual beam energy~\cite{ttc_distribution}.
 %
@@
 %
-An in-vacuum mirror intercepts  SR  emitted by protons passing through magnets located approximately 27 meters upstream.
+An in-vacuum mirror intercepts  SR  emitted by particles passing through magnets located approximately \SI{27}{m} upstream.
 It then directs the radiation to a dedicated optical line installed beneath the beam pipe.
@@
 %
-Neutral density filters in the optical front-end (OF) allow  changing the light intensity, thus optimizing the system dynamic range.
+Neutral density filters in the optical front-end (OF) allow  changing the light intensity, thus optimize the system dynamic range.
 % 
@@
 %
-The DAQ gateware sums four consecutive samples to compute the
-proton charge present on a~\SI{100}{ns} interval.
+The DAQ gateware sums four consecutive samples to compute the charge present on a~\SI{100}{ns} interval.
 %
@@
 %
-A dedicated  front-end  server, publishes the data stream through FESA~\cite{fesa}.
+A dedicated  front-end  server publishes the data stream through FESA~\cite{fesa}.
 
@@
 In addition, the amplifier bandwidth (50 kHz-1,5 GHz) %increases system complexity, as
-required a correction for the missing DC component and the amplifier gain is fixed,  for which  the overall dynamic range is limtied by the ADC. 
-%needs to be implemented.
-%
-%dynamic range is not fully exploited. cannot optimally re-use available dynamic range.
+requires a correction for the missing DC component.
+%%%%%%%% and the amplifier gain is fixed,  for which  the overall dynamic range is limited by the ADC. 
+% To Federico: The statement above is not true. ADC dynamic range is determined solely by number of bits. 
+% What changes is the SNR, which is defined as power in signal amplitude wrt to power of noise. 
+% In ideal conditions we want our signal to be amplified such, that we use maximum available ADC 
+% analogue signal amplitude to increase signal to noise ratio. ADC dynamic range is constant.
+% I'd replace it by following:
+The amplifier gain is fixed,  so the signal amplitude cannot be adapted to optimally re-use the available ADC dynamic range. 
+% this is what happens electrically.
 \\
-The system relies on an outdated FPGA platform, and the development SW is no more compatible with the latest operating systems.
+The system also relies on an outdated FPGA platform, and the development SW is no more compatible with the latest operating systems.
 
@@
 %
-A new DC-coupled amplifier was designed, thus allowing enhancing the overall dynamic range. 
+A new DC-coupled variable gain amplifier was designed.
 %
-It was decided to change from analog to digital integration of the MCP-PMT signal, via a DAQ based on  a~4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
+It was decided to change from analog to digital integration of the MCP-PMT signal.
+%
+The signal is digitized by a DAQ based on a~4-channel \SI{500}{MSPS} 14-bit FMC-form factor sampler.
 %
@@
 %
-Such a solution eliminates completely the need for the obsolete analogue integrators, as all the signal processing can be implemented in the gateware.
+Such a solution eliminates completely the need for the analogue integrators, as all the signal processing can be implemented in the gateware.
 \\
-In early 2023, the new AGM system was installed alongside the legacy system to facilitate an easy comparison of both systems' performance.
+In early 2023, the new AGM system was installed alongside the legacy system to compare both systems' performance.
 %An updated version of the AGM was in 2023 installed \textit{in parallel to the actually running AGM}, so that we can compare behavior of both systems.
@@
 %
-A programmable DC-offset compensation is implemented in the amplifier.
+A programmable DC-offset compensation is implemented.
 %
@@
 %
-\begin{figure}[!tbh]
+\begin{figure}[!t]
     \centering
@@
 %
+% To Federico: I would personally remove definitions of UART and FIFO, as they are a 'common knowledge'. It would
+% save some space. We need to gain somewhere a half of paragraph to fit into 3 pages + refs.
 The tagged samples are stored in a~FIFO (First In, First Out), and then integrated. 
@@
 %
-In parallel the system reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
+In parallel, the system reads a stream of 64~values of a stored 'offset' from a pedestal memory (P[63:0]).
 %
@@
 \end{figure}
+\vspace{-5mm}
 
@@
 
-The new installation, when \textit{in retracted position} is  highlighted by a~violet frame in Fig.~\ref{fig:installation}, 
+The new installation, shown \textit{in retracted position}, is  highlighted by a~violet frame in Fig.~\ref{fig:installation}, 
 %
@@
         \scalebox{0.54}{\input{plots/ions.pgf}}
-        \caption{Comparison of the AGM measurements}
+        \caption{Example of a comparison between old and new  AGM measurements, binned in 100\,ns slots (\emph{output filter indices}).  The MCP-PMT gate is \emph{open} between index 17 and 47.}
         \label{fig:comparison_chart}
@@
 \vspace{-5mm}
-Initial measurements were conducted in November 2023 using the LHC ion beam.
+A first set of measurements with the new AGM system were taken during the 2023 Ion Run, 
+%Initial measurements were conducted in November 2023 using the LHC ion beam.
 %
-Figure~\ref{fig:comparison_chart} shows the very first measurements, compared to the operational AGM.
+and the comparison to the operational AGM is shown in Figure~\ref{fig:comparison_chart}.
+%shows the very first measurements, compared to the operational AGM.
 %
-Both measurements agree to 2\% within the operational area, but deviate starting at $47^{\text{th}}$ bin, resulting in maximum relative error of 4\%.
-Despite the MCP-PMT gate is closed at that point and no signal is present, the operational AGM signal gradually decays, and extends below zero.
+During the period in which the MCP-PMT gate is open (between index 17 and 47 in the plot) the agreement between old and new system is within $\pm 2\%$.  
+%Both measurements agree to 2\% within the operational area, but deviate starting at $47^{\text{th}}$ bin, resulting in maximum relative error of 4\%.
+When the MCP-PMT gate closes at index 47 the operational system exhibits a slow (several \SI{100}{ns} slots) decay to non-physical negative values. 
+%Despite the MCP-PMT gate is closed at that point and no signal is present, the operational AGM signal gradually decays, and extends below zero.
 %
@@
 %
-This effect is systematic, and is mostly caused by analog signal processing chain and non-ideal analogue integration.
+This effect was found to be  systematic, and traced back to  non-optimal analog signal processing and integration. 
+%chain and non-ideal analogue integration.
 %
-The new system effectively eliminates this.
+The new system eliminates this effect.
 
 \section{Summary}
-This paper describes upgrade of the operational AGM.
+
+The current LHC AGM system requires refurbishing to assure long-term maintainability of the DAQ.
+This paper outlines the new DAQ design, which is a fully digital solution incorporating digital integration.
+An initial prototype was installed to monitor the LHC on beam 1, working in tandem with the operational AGM.
+
+In 2023, a series of measurements with ions demonstrated exceptional performance, even with significantly less intercepted light, and showed strong alignment with the legacy system.
+
+The unit is now gathering data with protons, which will facilitate further analysis regarding its accuracy, reliability, and stability.
+Once the system is fully validated, both LHC AGMs will transition to the new version.
+
+%This paper describes upgrade of the operational AGM.
 %
-The operational system has to be replaced in the near future by a new AGM to assure long-term maintainability.
+%The operational system has to be replaced in the near future by a new AGM to assure long-term maintainability.
 %
-A fully digital solution was developed.
+%A fully digital solution was developed.
 %
-To assess its performance, it was installed in the LHC, on beam 1, in parallel with the operational AGM.
+%To assess its performance, it was installed in the LHC, on beam 1, in parallel with the operational AGM.
 %
-Very first measurements from November 2023 show exceptionally good performance even using considerably lower amount of intercepted light.
+%Very first measurements from November 2023 show exceptionally good performance even using considerably lower amount of intercepted light.
 %
-The upgraded AGM is now collecting data from the LHC 2024 proton run.
+%The upgraded AGM is now collecting data from the LHC 2024 proton run.
 %
-Further analysis in terms of accuracy, reliability, and stability has to be conducted, with the ultimate goal of replacing both operational AGMs by their new versions.
+%Further analysis in terms of accuracy, reliability, and stability has to be conducted, with the ultimate goal of replacing both operational AGMs by their new versions.
 
